### 2022-03-31 Manuscript-figures.Rmd
Add files via upload

---
title: "FireSim2019_ManuscriptFigures"
author: "Dana Johnson"
date: "9/9/2021"
output: html_document
---
```{r setup, include=FALSE}

#library(knitr)
library(ggplot2)
#library(plyr)
library(dplyr)
library(tidyr)
#library(car) # For Levene's Test
library(phyloseq)
#library(scatterplot3d)
#library(ggtree)
library(cowplot) # add-on to ggplot to assist in publication-quality figs
#library(qwraps2)
library(vegan)
library(tidyverse)
#library(psych) # scatterplot matrix (pairs, or pairs.panels)
library(ggtern) # for ternary plots
#library(devtools)
#library(DivNet)
#library(breakaway) # for richness estimates

knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width = '100%')
```

Defaults = theme_bw(), black = O, "organic"; grey40 - M, "mineral"; shapes = circle, triangle

# Metadata
```{r, include=FALSE}
df.meta <- read.csv('../data/all-sample-metadata.csv')

df.meta <- subset(df.meta, core.id != '19UW-WB-11-02' &
                         Full.id != '19UW-WB-06-08-A-SI-duplicate' &
                         Full.id != '19UW-WB-07-02-O-SI-duplicate' &
                         Full.id != '19UW-WB-11-03-O-SI-duplicate' &
                         Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                         Full.id != '19UW-WB-08-10-O-SI')

# Assign degree hours by horizon:
for (i in 1:nrow(df.meta)) {
  if (df.meta$PRE.O.hor.thickness.cm[i] == 10) {
    df.meta$hrzn.degree.hrs[i] = (df.meta$Low.degree.C.hours[i] + df.meta$Mid.degree.C.hours[i])/2
  } else if (df.meta$horizon[i] == 'A') {
    df.meta$hrzn.degree.hrs[i] = df.meta$Low.degree.C.hours[i]
  } else {
    df.meta$hrzn.degree.hrs[i] = df.meta$Mid.degree.C.hours[i]
  }
}

# Create labels and palettes for plots
HorizonLabels = c('Organic','Mineral')
names(HorizonLabels) = c('O','A')

DNALabels   = c('RNA','DNA')
names(DNALabels) = c('cDNA','gDNA')

ComparisonLabels = c('dry vs. unburned','wet vs. unburned')
names(ComparisonLabels) = c("DvC",'WvC')

# Edit names of Leading Species
VegLabels_Condensed = c("Picea spp.","Pinus banksiana","Populus \n tremuloides")
names(VegLabels_Condensed) <- c("Picea","Pinus_banksiana","Populus_tremuloides")

VegLabels_Full = c("Picea glauca","Picea mariana","Pinus banksiana","Pinus banksiana \n overstory","Populus \n tremuloides")
names(VegLabels_Full) <- c("Picea_glauca","Picea_mariana","Pinus_banksiana","Pinus_banksiana overstory piceglauc understory","Populus_tremula")

ThermoLabels = c('Organic-mineral \ninterface','Core base')
names(ThermoLabels) <- c('Mid','Low')

BurnLabels = c('Dry soil burn','Wet soil burn', 'Control')
names(BurnLabels) <- c('dry','wet', 'control')

# Edit names of Site
SiteLabels <- c("Site 01","Site 02","Site 03","Site 04","Site 05","Site 06",
               "Site 07","Site 08","Site 09","Site 10","Site 11","Site 12",
               "Site 13","Site 14","Site 15","Site 16","Site 17","Site 18",
               "Site 19")
names(SiteLabels) <- c("1","2","3","4","5","6","7","8","9","10","11",
                      "12","13","14","15","16","17","18","19")

BurnSeverityLabels = c('Wet burn','Dry burn')
names(BurnSeverityLabels) <- c("Low_Sev",'High_Sev')

IncubLabels = c('24 hours post-burn','5 weeks post-burn', '6 months post-burn', '6 months post-burn: \nAutoclaved','6 months post-burn: \nNot autoclaved')
names(IncubLabels) = c('pb','SI', 'LI', 'LIwA','LIn')

CoefsLabel = c('Slow pool (M2)', 'Fast pool (M1)', 'Slow pool decay rate (k2)','Fast pool decay rate (k1)')
names(CoefsLabel) = c('M2','M1', 'k2','k1')

# Reorder burn treatment levels
df.meta$horizon =factor(df.meta$horizon, levels = c('O','A'))
df.meta$incub.trtmt = factor(df.meta$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
df.meta$burn.trtmt = factor(df.meta$burn.trtmt, levels = c('control','wet','dry'))
```

# Load phyloseq objects
```{r, message = FALSE}
#df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
#df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
#df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
#df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')

# Starting phyloseq:
### Normalized + tree
ps.norm.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)

ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
                    sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
                    sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
                    sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                    sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)

ps.raw.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')

ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
                    sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
                    sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
                    sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                    sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)

# Reorder vegetation:
sample_data(ps.norm.full)$Veg.type = factor(sample_data(ps.norm.full)$Veg.type, levels = c('Picea','Populus_tremuloides','Pinus_banksiana'))
sample_data(ps.norm.full)$horizon = factor(sample_data(ps.norm.full)$horizon, levels = c('O','A'))
sample_data(ps.norm.full)$incub.trtmt = factor(sample_data(ps.norm.full)$incub.trtmt, levels = c('pb', 'SI','LIwA','LIn'))

#Pull out just the gDNA samples:
ps.norm.gDNA <- prune_samples(sample_data(ps.norm.full)$DNA.type == 'gDNA', ps.norm.full)
ps.raw.gDNA <- prune_samples(sample_data(ps.raw.full)$DNA.type == 'gDNA', ps.raw.full)

ps.norm.cDNA <- prune_samples(sample_data(ps.norm.full)$DNA.type == 'cDNA', ps.norm.full)
ps.raw.cDNA <- prune_samples(sample_data(ps.raw.full)$DNA.type == 'cDNA', ps.raw.full)

#ps.raw.pb <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb', ps.raw.full)
#ps.norm.pb <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb', ps.norm.full)

# ps.norm.pb
#ps.norm.pb.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb',ps.norm.gDNA)
#ps.norm.pb.cDNA <- prune_samples(sample_data(ps.norm.cDNA)$incub.trtmt == 'pb',ps.norm.cDNA)
# ps.norm.SI
#ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI',ps.norm.gDNA)
# ps.norm.LIwA
#ps.norm.LIwA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIwA',ps.norm.gDNA)
#ps.norm.LIn <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIn',ps.norm.gDNA)
#ps.norm.LI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.norm.gDNA)
#ps.raw.LI <- prune_samples(sample_data(ps.raw.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.raw.gDNA)

#ps.norm.SI<- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
```

# Figure 2 (burn temperature, pH and C:N change, respiration coefficients):
```{r}
# Temperatures ----
df.Temp <-read.csv('../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))

pTemp = ggplot(df.Temp, aes(x = time_hr, 
                          y = Temp)) + 
  geom_point(aes(color = Thermo_position), size=1) +
  theme_bw()+
  facet_grid(burn.trtmt~Thermo_position,scales = 'free_y', 
             labeller = labeller(Thermo_position = ThermoLabels,
                                 burn.trtmt = BurnLabels)) +
  labs(x = "Time (h)",
       y = expression(paste("Temperature ( ",degree ~ C, ")")),
       color = "Soil depth") + 
  scale_color_manual(values = c('black','grey40'),
                     labels = c('O horizon/mineral \n interface','9 cm'),
                     breaks = c('Mid','Low')) + 
  theme(axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        axis.text = element_text(size=16),
        strip.text.y = element_text(size=16), 
        strip.text.x = element_text(size=16), 
        legend.text = element_text(size=16),
        legend.title = element_text(size=16), 
        legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92")) 
pTemp

# pH and C:N change ----
pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = pH, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil pH',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

pChange_CN  <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = C.N.ratio, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Soil C:N',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

cowplot::plot_grid(pChange_pH, pChange_CN, ncol=2)

# Respiration coefficients ----
df.coefs <- subset(df.meta, incub.trtmt == 'LIwA' &
                     horizon == 'O' & texture != 'organic')

df.stack <- gather(df.coefs, 
                   key = 'coefs', 
                   value = value,M1,M2,k1,k2)

df.stack$coefs <- factor(df.stack$coefs, levels = c('M1', 'M2', 'k1', 'k2'))

pResp2 = ggplot(subset(df.stack, coefs %in% c('M1','M2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Fractional pool size',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=25, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

pResp1 = ggplot(subset(df.stack, coefs %in% c('k1','k2')), aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Decay rate',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  #scale_x_discrete(limits = c('O','A'), 
  #                 labels = c('Organic','Mineral'))
  facet_wrap(~coefs, ncol=1,scales = 'free_y',
             labeller = labeller(coefs = CoefsLabel))+
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical", 
       legend.position = '',
       strip.background = element_rect(colour="black", fill="grey92"))

cowplot::plot_grid(pResp2, pResp1, ncol=1)

# Stats ----
df.stats <- subset(df.meta, incub.trtmt != 'pb' & horizon == 'O')

summary(subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic' &
                 horizon == 'O' & burn.trtmt == 'wet')$k1)
sd(subset(df.stats, incub.trtmt == 'LIwA' & burn.trtmt == 'wet')$k1)

test = aov(k2 ~ burn.trtmt, subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic'))
summary(test)
TukeyHSD(test)

test = wilcox.test(M1~burn.trtmt, data = subset(df.stats, incub.trtmt == 'SI' & burn.trtmt != 'control'))
test

test = aov(M1 ~ texture, data = subset(df.meta, incub.trtmt %in% c('LIwA','LIn') & horizon == 'O'))

test

p = ggplot(df.stats, aes(x=burn.trtmt, y =k1)) + 
  geom_boxplot() + 
  facet_grid(~incub.trtmt) +
  theme_bw()

```

# Figure 3: RNA and DNA concentration (ng/g soil)
```{r}
df <- read.csv('../data/raw-data/pb-RNA-and-DNA-conc.csv')

colnames(df)[1] <- 'core.id.hor.incub'

df.sub <- df.meta %>%
  subset(incub.trtmt == 'pb') %>%
  subset(select = c(core.id.hor.incub, DNA.type, horizon, burn.trtmt))

df.DNA <- subset(df, DNA.type == 'gDNA') %>%
  mutate(Conc.DNA = Concentration_ng.uL) %>%
  subset(select = c('core.id.hor.incub', 'Conc.DNA'))
df.RNA <- subset(df, DNA.type == 'cDNA') %>%
  mutate(Conc.RNA = Concentration_ng.uL) %>%
  subset(select = c('core.id.hor.incub', 'Conc.RNA'))

df <- merge(df, df.sub)

NaLabels = c('RNA','DNA')
names(NaLabels) <- c('cDNA','gDNA')

p1 = ggplot(df) + 
  geom_boxplot(aes(x=burn.trtmt, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = horizon),alpha = 0.7, varwidth = FALSE) + 
  theme_bw()+
  facet_wrap(~DNA.type, ncol=2, labeller = labeller(DNA.type = NaLabels))+
  labs(x= 'Burn treatment',
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Concentration (ug/g soil)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                    limits = c('O','A'),
                    labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                   labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 13),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'right',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
p1

test <- aov(nucleic.acid.conc.in.soil.ng.per.g ~ burn.trtmt, data = subset(df, DNA.type == 'cDNA' & horizon == 'O' & burn.trtmt != 'wet'))
summary(test)
TukeyHSD(test)

```

Bray-Curtis dissimilarity?
```{r, message = FALSE}
# This is a possibly convoluted piece of code to first create a Bray-Curtis
#     dissimilarity matrix and then pull out the dissimilarities between dry/wet
#     burns and corresponding control cores.

# First: Calculate Bray-curtis dissimilarity matrix ----
ps.cDNA.raw <- prune_samples(sample_data(ps.raw.full)$DNA.type == 'cDNA', ps.raw.full)
ps.cDNA.raw <- prune_taxa(taxa_sums(ps.cDNA.raw) > 0, ps.cDNA.raw)

dist.bray.full <- as.matrix(distance(ps.raw.full, method = 'bray', type = 'samples'))

# Look at some figures
hist(dist.bray.full)
heatmap(dist.bray.full)

# Convert distance matrix into dataframe
df <- data.frame(dist.bray.full)

# Bring in meta data and subset for specific analysis
df.meta.sub <- subset(df.meta, select = c(Full.id, burn.trtmt,site, DNA.type,
                                          incub.trtmt,core, horizon,
                                          pH, change.pH))

# Create a dataframe with the colnames and Full.ID
x <- data.frame(str_split(colnames(df)[1:460], 'X', simplify = TRUE)[,2])

# Rename columes:
colnames(x)[1] <- 'ID.bray'

# Clean up x. 
x <- x %>%
  mutate(Full.id = ID.bray)

x$Full.id <- str_replace_all(x$Full.id, "\\.", "-")

x$X <- 'X'

x <- x %>%
  unite(Bray.ID, c('X',"ID.bray"), sep = '', remove = TRUE)

# Next, pull out the control cores from the meta data and assign them to "Control.id"
df.meta.control <- df.meta %>%
  subset(burn.trtmt == 'control') %>%
  mutate(Control.id = Full.id) %>%
  subset(select = c(Control.id, site, horizon, incub.trtmt, DNA.type))

# Combine list of control cores with full df.meta
df.meta.list <- merge(subset(df.meta.sub, select = c(Full.id, site, horizon, 
                                                     DNA.type,burn.trtmt, incub.trtmt, 
                                                     pH, change.pH)), 
                      df.meta.control, by = c('site', 'horizon', 'incub.trtmt', 'DNA.type'))

# ANd then combine the Full.id list with the control core meta data I just created.
#     df.list now contains Full.id with the corresponding control sample for each 
#     dry/wet burn and a colume ("Bray.ID") that has the sample ID formatted to 
#     match the distance matrix names.
df.list <- x %>%
  merge(df.meta.list, by = 'Full.id') %>%
  subset(burn.trtmt != 'control')

df.list$burn.trtmt <- as.character(df.list$burn.trtmt)
df.list$horizon <- as.character(df.list$horizon)
df.list$incub.trtmt <- as.character(df.list$incub.trtmt)

# Create and empty data frame to store distances
df.distances <- data.frame("Full.id" = df.list$Full.id, 
                           'control.core' = 'core',
                           #'burn.trtmt' = 'burn', 'horizon' = 'H',
                           #'DNA.type' = 'DNA.type',
                           'BC.distance.btw.burned.and.control' = 'distance'
                           #'incub.trtmt' = 'incub', 'pH' = 0
                           ) %>%
  unique()

# Now run a convoluted loop:
for (i in 1:nrow(df.list)) { # For each sample (row in df.list)
  for (j in 1:nrow(df)) { # For each row in the dissimilarity matrix
    for (k in 1:ncol(df)){ # And for each colume in the dissimilarity matrix
      if(colnames(df)[k] == df.list$Bray.ID[i] &  # If the distance matrix colume ID matches the sample ID in the list
         rownames(df)[j] == df.list$Control.id[i]) { # And the rowname ID matches the corresponding control core, then...
        df.distances$BC.distance.btw.burned.and.control[i] = df[j,k] # Pull out the distance and store it in new dataframe
        #df.distances$burn.trtmt[i] = df.list$burn.trtmt[i]
        df.distances$control.core[i] = df.list$Control.id[i]
        #df.distances$horizon[i] = df.list$horizon[i]
        #df.distances$incub.trtmt[i] = df.list$incub.trtmt[i]
        #df.distances$DNA.type[i] = df.list$DNA.type[i]
        #df.distances$pH[i] = df.list$pH[i]
        #df.distances$change.pH[i] = df.list$change.pH[i]
      }
    } 
  } 
}

df.distances$BC.distance.btw.burned.and.control <- as.numeric(df.distances$BC.distance.btw.burned.and.control)

# Save backup dataframe.
df.final <- df.distances

# -----
df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')

df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))                            
dim(df.distances)

# Plots ----
p=ggplot(subset(df.distances, DNA.type == 'cDNA')) + 
  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.burned.and.control, fill = horizon),
               alpha = 0.7) +
  theme_bw() +
  facet_wrap(~incub.trtmt, ncol=4,
             labeller = labeller(incub.trtmt = IncubLabels)) + 
  labs(x='Burn treatment',
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('wet','dry'),
                   labels = c('Wet soil \nburn','Dry soil \nburn')) +
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=18),
        legend.title = element_text(size=18),
        legend.text = element_text(size=18),
        strip.text = element_text(size=18)) + 
  ylim(0,1)

test <- aov(BC.distance.btw.burned.and.control~burn.trtmt*horizon, data = subset(df.distances, DNA.type == 'cDNA'))
summary(test)
TukeyHSD(test)

```

Richness estimates?

If the community composition data of a single sample includes few singletons, we assume that sequencing captured most of the taxa present in the sample. If the data includes many singletons, we assume that sequencing missed many rare taxa. We can use breakaway to estiamte how many taxa were missed and use this to estimate richness. 
```{r}

# Load data and calculate richness ----
df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')

head(df.pb.cDNA.OTU)

df.counts.pb.cDNA <- df.pb.cDNA.OTU %>%
  group_by(Full.id) %>%
  mutate(counts = length(unique(OTU))) %>%
  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
  unique()

df.counts.pb.gDNA <- df.pb.gDNA.OTU %>%
  group_by(Full.id) %>%
  mutate(counts = length(unique(OTU))) %>%
  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
  unique()

df.counts.SI <- df.SI.OTU %>%
  group_by(Full.id) %>%
  mutate(counts = length(unique(OTU))) %>%
  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
  unique()

df.counts.LI <- df.LI.norm %>%
  group_by(Full.id) %>%
  mutate(counts = length(unique(OTU))) %>%
  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
  unique()

df.counts <- rbind(df.counts.pb.cDNA, df.counts.pb.gDNA,
                   df.counts.SI, df.counts.LI)

df.counts$burn.trtmt <-  factor(df.counts$burn.trtmt, levels = c('control','wet','dry'))
df.counts$horizon <-  factor(df.counts$horizon, levels = c('O', 'A'))

df.counts.pb <- subset(df.counts, incub.trtmt == 'pb')

# Plots ----
p = ggplot(df.counts.pb, aes(x=burn.trtmt, y=counts)) +
  geom_boxplot(aes(fill = burn.trtmt), alpha = 0.7) + 
  geom_point(color = 'black', alpha = 0.4) + 
  theme_bw() + 
  facet_grid(horizon~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels,
                                                               horizon = HorizonLabels, 
                                                               DNA.type = DNALabels)) + 
  labs(y = 'unique non-zero OTU count')

test <- aov(counts ~ burn.trtmt, data = subset(df.counts.pb.gDNA, horizon =='O'))
summary(test)
TukeyHSD(test)

# Plot richness using "plot_richness" function in phyloseq: ----
ps <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb',
                    ps.raw.full)

sample_data(ps)$burn.trtmt <- factor(sample_data(ps)$burn.trtmt, levels = c('control','wet','dry'))
sample_data(ps)$horizon <- factor(sample_data(ps)$horizon, levels = c('O','A'))

p = plot_richness(ps, x = "burn.trtmt", measures = 'Shannon') +
  theme_bw() + 
  geom_boxplot(aes(fill = horizon), alpha = 0.6) + 
  facet_grid(horizon~DNA.type+incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels,
                                                   DNA.type = DNALabels,
                                                      horizon = HorizonLabels))
```

RNA:DNA ratios?
```{r}
df.norm.ratios <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/RNA_DNA_norm_ratios.csv')
# RNA:DNA ratios were calculated by (RNA rel. abundance)/(DNA rel. abundance)
#     In instances of DNA rel. abundance = 0, I set DNA abundance = 0.0000038, which
#     is equal to the lowest measured rel. abundance of DNA across the dataset.
#     In instances of RNA re. abundance = 0, I set ratio = 0.

df.norm.ratios$horizon <- factor(df.norm.ratios$horizon, levels = c('O','A'))
df.norm.ratios$burn.trtmt <- factor(df.norm.ratios$burn.trtmt, levels = c('control','wet','dry'))

# Plot 
p = ggplot(data = subset(df.norm.ratios, DNA.abundance > 0.001), aes(x=burn.trtmt, y = RNA.DNA.ratio, fill = horizon)) + 
  geom_boxplot()+ 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  #facet_wrap(~horizon, ncol=1,scale = 'free')+
  theme_bw() + 
  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')

# What fraction of total reads for each sample fall below 0.001 relative abundance threshold? -----
df.DNA.tally <- df.norm.ratios %>%
  subset(RNA.abundance + DNA.abundance > 0) %>%
  #subset(DNA.abundance > 0) %>%
  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
  mutate(counts = length(OTU)) %>%
  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
  tally(DNA.abundance > 0.001) %>%
  #mutate(DNA.fraction.above.cutoff = n/counts)
  mutate(non.zero.DNA.fraction = n/counts)
head(df.DNA.tally)

df.RNA.tally <- df.norm.ratios %>%
  subset(RNA.abundance + DNA.abundance > 0) %>%
  #subset(RNA.abundance > 0) %>%
  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
  mutate(counts = length(OTU)) %>%
  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
  tally(RNA.abundance > 0.001)%>%
  mutate(non.zero.RNA.fraction = n/counts)
  #mutate(RNA.fraction.above.cutoff = n/counts)
head(df.RNA.tally)

df.DNA.tally$burn.trtmt <- factor(df.DNA.tally$burn.trtmt, levels = c('control','wet','dry'))
df.RNA.tally$burn.trtmt <- factor(df.RNA.tally$burn.trtmt, levels = c('control','wet','dry'))

p = ggplot(df.DNA.tally, aes(x=burn.trtmt, y =DNA.fraction.above.cutoff, fill = horizon)) + 
  geom_boxplot() + theme_bw()

test <- aov(DNA.fraction.above.cutoff ~ burn.trtmt*horizon, data = df.DNA.tally)
summary(test)
TukeyHSD(test)

test <- aov(non.zero.RNA.fraction ~ burn.trtmt*horizon, data = df.RNA.tally)
summary(test)
TukeyHSD(test)

# Re-calculate ratio including only taxa present in both burned and unburned cores: ----
df.burned <- subset(df.norm.ratios, burn.trtmt == 'dry') %>%
  subset(DNA.abundance > 0) %>%
  mutate(burned.DNA.abundance = DNA.abundance) %>%
  subset(select = c(site, horizon, OTU, burned.DNA.abundance))

df.control <- subset(df.norm.ratios, burn.trtmt == 'control') %>%
  subset(DNA.abundance > 0) %>%
  mutate(unburned.DNA.abundance = DNA.abundance) %>%
  subset(select = c(site, horizon, OTU, unburned.DNA.abundance))

df.shared.OTUs <- merge(df.burned, df.control)

df.common.taxa <- subset(df.norm.ratios, burn.trtmt != 'wet') %>%
  merge(df.shared.OTUs) %>%
  mutate(ratio = RNA.abundance/DNA.abundance) %>%
  group_by(core.id.hor.incub) %>%
  mutate(mean.ratio = mean(ratio))

df.counts <- df.common.taxa %>%
  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
  tally(DNA.abundance > 0)

dim(df.common.taxa)

# Plot 
p = ggplot(data = df.common.taxa, aes(x=burn.trtmt, y = ratio, fill = horizon)) + 
  geom_boxplot()+ 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  #facet_wrap(~horizon, ncol=1,scale = 'free')+
  theme_bw() + 
  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')

test <- aov(ratio ~ burn.trtmt*horizon, data = df.common.taxa)
summary(test)
TukeyHSD(test)

# Recalculating ratios using raw reads: -----
ps.raw.gDNA <- prune_samples(sample_data(ps.raw.pb)$DNA.type == 'gDNA', ps.raw.pb)
ps.raw.gDNA
ps.raw.gDNA <- prune_taxa(taxa_sums(ps.raw.gDNA)>0, ps.raw.gDNA)
ps.raw.gDNA

ps.raw.cDNA <- prune_taxa(taxa_sums(ps.raw.cDNA)>0, ps.raw.cDNA)

df.raw.pb.cDNA <- psmelt(ps.raw.cDNA)
df.raw.pb.gDNA <- psmelt(ps.raw.gDNA)

df.RNA <- df.raw.pb.cDNA %>%
  mutate(RNA.abundance = Abundance) %>%
  subset(select = c(core.id.hor.incub, OTU, RNA.abundance))

df.DNA <- df.raw.pb.gDNA %>%
  mutate(DNA.abundance = Abundance) %>%
  subset(select = c(core.id.hor.incub, OTU, DNA.abundance, horizon, site, pH, hrzn.degree.hrs,burn.trtmt))

rownames(df.RNA) <- NULL
rownames(df.DNA) <- NULL

df.merge <- merge(df.RNA, df.DNA, by = c("core.id.hor.incub", "OTU"), all = TRUE)

df.pb <- df.merge %>%
  group_by(site, OTU) %>%
  mutate(min = min(DNA.abundance)) %>%
  subset(min > 0)

df.pb[is.na(df.pb$RNA.abundance),3] <- 0

df.pb <- df.pb %>%
  mutate(ratio = RNA.abundance/DNA.abundance)

# Plot
df.pb$burn.trtmt <- factor(df.pb$burn.trtmt, levels = c('control','wet','dry'))

p = ggplot(data = subset(df.pb,horizon =='O'), aes(x=burn.trtmt, y = (ratio), color = burn.trtmt)) + 
  geom_boxplot()+ 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  facet_wrap(~horizon, ncol=1,scale = 'free')+
  theme_bw() + 
  labs(title = 'RNA:DNA \nonly taxa present across all trtmts')

test <- aov((ratio) ~ burn.trtmt, data = subset(df.pb, horizon == 'O'))
summary(test)
TukeyHSD(test)

# Alternative calculations for RNA:DNA ratios: ----

### Set ratio = 100 if DNA rel. abundance = 0 (Bowsher et al. 2019)
for (i in 1:nrow(df.norm.ratios)) {
  if(df.norm.ratios$DNA.abundance[i] == 0) {
    df.norm.ratios$RNA.DNA.ratio[i] = 100
  } else {
    df.norm.ratios$RNA.DNA.ratio[i] = df.norm.ratios$RNA.DNA.ratio[i]
  }
}

### If DNA abundance = 0, change it to 1.  (Bowsher et al. 2019)
#     But this would only work for raw count data.
for (i in 1:nrow(df.norm.ratios)) {
  if(df.norm.ratios$DNA.abundance[i] == 0) {
    df.norm.ratios$DNA.abundance[i] = 0.000038
  } else {
    df.norm.ratios$DNA.abundance[i] = df.norm.ratios$DNA.abundance[i]
  }
}
df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance

### Add 1 to all DNA and RNA abundances (Bowsher et al. 2019)
df.norm.ratios$DNA.abundance = df.norm.ratios$DNA.abundance + 0.000038

#df.norm.ratios$RNA.abundance = df.norm.ratios$RNA.abundance + 0.000038

df.norm.ratios <- subset(df.norm.ratios, DNA.abundance > 0.0001 || RNA.abundance >0.0001 )

df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance
```

# Figure 4 - weighted mean gene copy number
Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
```{r}
df.WMCN.pb <- read.csv('../data/WtMeanCopyNum_pb_gDNA.csv')
df.WMCN.SI <- read.csv('../data/WtMeanCopyNum_SI.csv')
df.WMCN.LIwA <- read.csv('../data/WtMeanCopyNum_LIwA.csv')

df.WMCN.SI <- subset(df.WMCN.SI, core.id != '19UW-WB-11-02' & 
                    Full.id != '19UW-WB-06-08-A-SI-duplicate' &
                    Full.id != '19UW-WB-07-02-O-SI-duplicate' &
                    Full.id != '19UW-WB-11-03-O-SI-duplicate'&
                    Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                    Full.id != '19UW-WB-08-10-O-SI' )

summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)
sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)

test = aov(WtMeanCopyNum~ burn.trtmt*horizon, data = df.WMCN.SI)
summary(test)
TukeyHSD(test)

df.WMCN <- rbind(df.WMCN.SI, df.WMCN.LIwA, df.WMCN.pb)

df.WMCN <- df.WMCN %>%
  unite(core.id.hor, c(core.id, horizon), sep = '-', remove=FALSE)

df.WMCN <- merge(df.WMCN, df.meta)

# CHeck for normality:
p.QQ = qqplot(df.WMCN$hrzn.degree.hrs, df.WMCN$WtMeanCopyNum)

# Plot ----
df.WMCN$burn.trtmt <- factor(df.WMCN$burn.trtmt, levels = c('control','wet','dry'))
df.WMCN$horizon <- factor(df.WMCN$horizon, levels = c('O','A'))
df.WMCN$incub.trtmt <- factor(df.WMCN$incub.trtmt, levels = c('pb','SI','LIwA'))

p1 = ggplot(data = subset(df.WMCN, incub.trtmt != 'LIwA')) + 
  geom_boxplot(aes(x=burn.trtmt, y=WtMeanCopyNum, fill=horizon),alpha=0.7)+
  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels))+
  theme_bw() + 
  scale_fill_manual(values = c('black','grey50'),
                     labels = c('Organic','Mineral'),
                     limits = c('O','A'))+
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  labs(x='Burn treatment',
       y='Weighted mean predicted \n16S rRNA gene copy number',
       fill = 'Soil horizon') +
  theme(axis.text.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14),
        strip.text = element_text(size=14),
        legend.position = 'right',
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10))) +
  ylim(1,NA)

# Stats
df.WMCN.O <- subset(df.WMCN, horizon == 'O')
df.WMCN.A <- subset(df.WMCN, horizon == 'A')

fit.df.WMCN.O <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.O)
fit.df.WMCN.A <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.A)

summary(fit.df.WMCN.O)
# p = 2*10^-16, R^2 adj = 0.6081
summary(fit.df.WMCN.A)
# p = 2*10^-16, R^2 adj = 0.7883

# Weighted mean copy number STATS:
test <- aov(WtMeanCopyNum ~ burn.trtmt*horizon, data = subset(df.WMCN, incub.trtmt == 'SI'))
summary(test)
TukeyHSD(test)

test.sum <- df.WMCN %>%
  group_by(burn.trtmt, horizon) %>%
  summarize(mean.WMCN = mean(WtMeanCopyNum))

# Calculate WMCN change from pb to SI: ----
df.WMCN.initial <- subset(df.WMCN, incub.trtmt == 'pb') %>%
  mutate(WMCN.pb = WtMeanCopyNum) %>%
  subset(select = c(core.id, horizon, burn.trtmt, WMCN.pb))

df.WMCN.SI <- df.WMCN.SI %>%
  merge(df.WMCN.initial, all = TRUE) %>%
  mutate(change.WMCN = WtMeanCopyNum - WMCN.pb)

df.WMCN.SI$burn.trtmt <- factor(df.WMCN.SI$burn.trtmt, levels = c('control','wet','dry'))

p = ggplot(df.WMCN.SI, aes(x=burn.trtmt, y = change.WMCN, fill = horizon)) + 
  geom_boxplot() + 
  geom_hline(yintercept = 0)+
  theme_bw() + 
  labs(x = 'Comparison between samples 24 h and 5 wk post-burn',
       y = 'Change in predicted wt. mean gene copy number')

test <- aov(change.WMCN ~ burn.trtmt*horizon, data = df.WMCN.SI)
summary(test)
TukeyHSD(test)

# Compare copy number of positive/negative responders: ----
df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
RDP <- read.csv('../data/All-OTUs-CopyNum.csv')

df.fast <- subset(df.full, Experiment == 'fast growth' &
                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
  mutate(fast.est = Estimate)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.Estimate = max(Estimate)) %>%
  subset(Estimate == max.Estimate) %>%
  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, Experiment,
                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
                    Species, DNA.type, fast.est)) %>%
  unique()

ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI', ps.norm.full)
ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)

df.not.responders <- data.frame(taxa_names(ps.norm.SI))

df.not.responders <- subset(df.not.responders, !(taxa_names.ps.norm.SI. %in% df.responders$OTU))

df.not.responders$Responders = 'no'
df.responders <- subset(df.fast, select = c(OTU)) %>%
  mutate(Responders = 'yes')
colnames(df.not.responders)[1] = 'OTU'

df.responders <- rbind(df.responders, df.not.responders) %>%
  merge(RDP)

p = ggplot(df.responders, aes(x=Responders, y = CopyNum)) + 
  geom_boxplot() + 
  theme_bw()

df.SI.responders <- df.full.OTU %>%
  subset(Experiment == 'fast growth') %>%
  merge(RDP)

dim(df.SI.responders)

df.SI.positive = subset(df.SI.responders, Estimate > 0 ) %>%
  group_by(OTU) %>%
  mutate(Estimate = max(Estimate)) %>%
  mutate(Response = 'positive') %>%
  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
  unique()

df.SI.negative = subset(df.SI.responders, Estimate < 0 ) %>%
  group_by(OTU) %>%
  mutate(Estimate = min(Estimate)) %>%
  mutate(Response = 'negative') %>%
  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
  unique()

df.SI.responders <- rbind(df.SI.positive, df.SI.negative)

p = ggplot(df.SI.responders, aes(x=Estimate, y = Class, color = Phylum)) + 
  geom_point() + 
  theme_bw() + 
  facet_wrap(~Comparison) +
  geom_vline(xintercept = 0)

df.SI.dry.responders <- subset(df.SI.responders, Comparison == 'pb.dry.v.SI.dry') %>%
  subset(!(OTU %in% subset(df.SI.responders, Comparison %in% c('pb.wet.v.SI.wet', 'pb.control.v.SI.control')))) %>%
  subset(select = c(OTU, CopyNum, Response, horizon,Estimate)) %>%
  unique()

p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Response, y = CopyNum, fill = horizon)) + 
  geom_boxplot() + 
  theme_bw() + 
  facet_wrap(~horizon)

test = aov(CopyNum ~ Response+horizon, data = df.SI.dry.responders)
summary(test)
TukeyHSD(test)

p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Estimate, y = CopyNum)) + 
  geom_point()+
  facet_grid(Response~horizon) + 
  stat_smooth(method=lm,se = FALSE,color='black') +
  theme_bw() 
```

# Figure 5 - Calculate bray-curtis dissimilarity for autoclaving
```{r, message = FALSE}
df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')

df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))

df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
df.distances$horizon <- factor(df.distances$horizon, levels = c('O','A'))

# plot: Dry soil burns
p3=ggplot(subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry'),
         aes(x=change.pH, y = BC.distance.btw.burned.and.control, color = horizon, shape = horizon)) + 
  geom_point(size=3, alpha = 0.8) +
  theme_bw() +
  facet_wrap(~horizon,ncol=2,
             labeller = labeller(horizon = HorizonLabels),
             scales = 'fixed') + 
  labs(x = expression(Delta~'pH with burning'),
       y = 'Bray-Curtis dissimilarity \ncompared to control', 
       color = 'Soil horizon',
       shape = 'Soil horizon') + 
  scale_color_manual(values = c('black', 'grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title.x = element_text(size=14, margin = margin(t=10)),
        axis.title.y = element_text(size=14, margin = margin(r=10)),
        axis.text = element_text(size=12),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14),
        strip.text = element_text(size=14),
        panel.spacing.x = unit(2, "lines"),
       legend.position = 'right') +
  stat_smooth(data = subset(df.distances, incub.trtmt == 'LIwA' & burn.trtmt == 'dry' & horizon == 'O'),
              method=lm,se = FALSE,color='black') +
    ylim(0,1)

test = lm(BC.distance.btw.burned.and.control~change.pH, data=subset(df.distances, incub.trtmt == 'LIwA' & horizon == 'A' & burn.trtmt == 'dry'))

test
summary(test)

# Hrzn.degree.hrs vs. Bray-Curtis dissimilarities for -pb RNA and DNA -----
p = ggplot(subset(df.meta.combined, burn.trtmt =='dry' & 
                    incub.trtmt == 'pb'),
           aes(x=hrzn.degree.hrs, y = BC.distance.btw.burned.and.control,fill = horizon)) +
  geom_point(shape='circle filled',
             stroke=1,
             alpha = 0.8,
             size=3) +
  theme_bw() +
  facet_grid(DNA.type~horizon, scales = 'free',
             labeller = labeller(incub.trtmt = IncubLabels,
                                 burn.trtmt = BurnLabels, 
                                 DNA.type = DNALabels)) + 
  labs(y = 'Bray-Curtis dissimilarity compared to control', 
       title = 'Bray-Curtis dissimilarities') + 
  scale_fill_manual(values = c('black','grey70'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12),
        legend.title = element_text(size=12),
        legend.text = element_text(size=12)) + 
    stat_smooth(method=lm,se = FALSE,color='black')

# Stats -----
test <- aov(BC.distance.btw.burned.and.control ~ hrzn.degree.hrs, 
            data = subset(df.meta.combined,incub.trtmt == 'pb' & DNA.type == 'cDNA' &burn.trtmt == 'wet'))
summary(test) 
```

# Figure 6: Trade offs
```{r}
df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
df.L2FC <- read.csv('../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')

# Checking to make sure that L2FC calculations didn't drop any OTUs. 
df.survival <- df %>%
  subset(Experiment == 'survival'&
           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') & 
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.survival.L2FC <- df.L2FC %>%
  subset(Experiment == 'survival'  &
           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique()

df.survival.merge <- merge(df.survival, df.survival.L2FC)
#write.csv(df.survival,'../tables/survivors.csv', row.names=FALSE)

dim(df.survival)
dim(df.survival.L2FC)

df.fast <- df %>%
  subset(Experiment == 'fast growth'&
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.fast)

df.fast.L2FC  <- df.L2FC %>%
  subset(Experiment == 'fast growth'  &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.fast.L2FC)
df.fast.merge <- merge(df.fast.L2FC, df.fast)

df.affinity <- df %>%
  subset(Experiment == 'affinity'&
           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') &
           Estimate > 0) %>%
  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
dim(df.affinity)

df.affinity.L2FC  <- df.L2FC %>%
  subset(Experiment == 'affinity'  &
           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
           mu > 0) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  subset(select = c(OTU)) %>%
  unique() 
dim(df.affinity.L2FC)

df.affinity.merge <- merge(df.affinity.L2FC, df.affinity)

df.full <- df.L2FC

# Filter u ----
# First pull out enriched taxa:
df <-  subset(df.full, mu > 0)

# Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
#   the mean of the estimate. Remove duplicate taxa. 
df.survival <- subset(df, Experiment == 'survival' &
                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(survival.L2FC = L2FC) %>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()%>%
  mutate(survivor = 'yes')

# Create dataframe for fast growers filtering for 1 sd from the mean: -----
df.fast <- subset(df, Experiment == 'fast growth') %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(fast.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique() %>%
  mutate(fast = 'yes')

# Create data frame for affinity taxa filtering for temperature cutoff and 1
#   sd from the mean:
df.affinity <- subset(df, Experiment == 'affinity' &
                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
  subset(mu > (mean(mu)-1*sd(mu))) %>%
  mutate(affinity.L2FC = L2FC)%>%
  dplyr::group_by(OTU) %>%
  dplyr::mutate(max.mu = max(mu)) %>%
  subset(mu == max.mu) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()%>%
  mutate(affinity = 'yes')

# Combine the three dataframes:
df.index <- merge(df.survival, df.fast, all = TRUE) %>%
  merge(df.affinity, all = TRUE) %>%
  subset(select = c(OTU, survivor, fast, affinity))

df.ids <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv') %>%
  subset(select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()
df.ids <- merge(df.index,df.ids, all = FALSE)
write.csv(df.ids, '../tables/all-responding-otus.csv', row.names = FALSE)

# Next take the full responder dataset and filter out any duplicate taxa

x.1 <- df.full %>%
  subset(Experiment == 'survival') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(survival.L2FC = L2FC) %>%
  subset(select = c(OTU, survival.L2FC)) %>%
  unique()

x.2 <- df.full %>%
  subset(Experiment == 'fast growth') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(fast.L2FC = L2FC) %>%
  subset(select = c(OTU, fast.L2FC)) %>%
  unique()

x.3 <- df.full %>%
  subset(Experiment == 'affinity') %>%
  subset(select = c(OTU, mu, Experiment,horizon,
                    fold.change, L2FC)) %>%
  dplyr::group_by(OTU, Experiment) %>%
  dplyr::mutate(max.mu = max(abs(mu))) %>%
  subset(max.mu == abs(mu)) %>%
  dplyr::mutate(affinity.L2FC = L2FC) %>%
  subset(select = c(OTU, affinity.L2FC)) %>%
  unique()

x <- merge(x.1, x.2, all = TRUE) %>%
  merge(x.3, all = TRUE)

# Create list of responding taxa:
responding.OTU.list = unique(df.index$OTU)

# Then filter this to include only taxa identified as responders (i.e. meeting
#   the respective cutoffs for at least one of the three trait experiments)
df.traits <- filter(x, OTU %in% responding.OTU.list) %>% 
  unique()

df.traits <- merge(df.index, df.traits)

#df.traits <- test %>%
#  merge(unique(subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species))))

df.traits$trait = 'null'

for (i in 1:nrow(df.traits)) {
  if (df.traits$survivor[i] == 'yes' &
      df.traits$survival.L2FC[i] > 0 &
      is.na(df.traits$fast[i]) == TRUE &
      is.na(df.traits$affinity[i]) == TRUE) {
    df.traits$trait[i] = 'survival'
      } else if (df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE &
                 is.na(df.traits$affinity[i]) == TRUE) {
        df.traits$trait[i] = 'fast growth'
      } else if (df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE &
                 is.na(df.traits$fast[i]) == TRUE) {
        df.traits$trait[i] = 'affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 is.na(df.traits$affinity[i]) == TRUE) {
        df.traits$trait[i] = 'survival and fast growth'
      } else if (df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$survivor[i]) == TRUE) {
        df.traits$trait[i] = 'fast growth and affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0 &
                 is.na(df.traits$fast[i]) == TRUE) {
        df.traits$trait[i] = 'survival and affinity'
      } else if (df.traits$survivor[i] == 'yes' &
                 df.traits$survival.L2FC[i] > 0 &
                 df.traits$fast[i] == 'yes' &
                 df.traits$fast.L2FC[i] > 0 &
                 df.traits$affinity[i] == 'yes' &
                 df.traits$affinity.L2FC[i] > 0) {
        df.traits$trait[i] = 'survival, fast growth, \nand affinity'
      } else {
        df.traits$trait[i] = 'none'
      } 
}

unique(df.traits$trait)

head(df.traits)

library(RColorBrewer)
old.trait.colors = c('gold','green','royalblue3','purple','darkred','orange','black')
trait.colors = c(brewer.pal(n=10, name = 'Spectral'), 'black')

trait.colors = c('#E6AB02','#33A02C','#386CB0','#762A83','#D73027','#F46D43','black')

# Finally build trait trade-off plots:
p1 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=survival.L2FC, y=fast.L2FC, color = trait, fill = trait), shape = 21,size=4, alpha=1) + 
  theme_bw() +
  labs(x= expression(Survival~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Fast~growth~(log[2]-fold~change))) + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=10),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=10),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")+
  stat_smooth(aes(x=survival.L2FC, y=fast.L2FC),method=lm, se=FALSE, color = 'grey40',
              geom = 'smooth')

p2 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=fast.L2FC, y=affinity.L2FC, color = trait, fill=trait), shape = 21,  size=4,alpha=1) + 
  theme_bw() +
  labs(x= expression(Fast~growth~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Post~fire~envir.~affinity~(log[2]-fold~change))) + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=10),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=10),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

p3 = ggplot(df.traits) + 
  geom_hline(yintercept = 0) + 
  geom_vline(xintercept = 0)+ 
  geom_point(aes(x=affinity.L2FC, y=survival.L2FC, color = trait, fill = trait), 
             shape = 21,size=4,alpha=1) + 
  theme_bw() +
  labs(x=expression(Post~fire~envir.~affinity~(log[2]-fold~change)),
       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = expression(Survival~(log[2]-fold~change)),
       color = 'Bacterial strategy:',
       fill = 'Bacterial strategy:') + 
  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
                     values = trait.colors) + 
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'none',
        # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
cowplot::plot_grid(p1, p2,p3, ncol=3)

test <- lm(fast.L2FC ~ affinity.L2FC, data = df.traits)
summary(test)
test
#

x <- grDevices::rainbow(n=6)

df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
df <- subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
  unique()

df.traits <- merge(df.traits,df)
dim(df.traits)
```

```{r}
# How much of total community do affinity taxa account for?
ps.norm.LI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIwA', ps.norm.gDNA)
ps.norm.LI <- prune_taxa(taxa_names(ps.norm.LI) %in% df.affinity.L2FC$OTU, ps.norm.LI)

df.norm.LI <- psmelt(ps.norm.LI)
df.norm.LI$burn.trtmt = factor(df.norm.LI$burn.trtmt, levels = c('control','wet','dry'))

df.norm.LI <- df.norm.LI %>%
  group_by(core.id.hor.incub, horizon, burn.trtmt) %>%
  summarize(sum.Abundance = sum(Abundance))

p = ggplot(df.norm.LI, aes(x=burn.trtmt, y = sum.Abundance, color = horizon)) + 
  geom_point() + 
  facet_grid(~horizon) + 
  theme_bw()
```

# PERMANOVAs:
```{r}
ps.E1 <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb' &
                         sample_data(ps.norm.full)$DNA.type == 'cDNA', ps.norm.full)
ps.E1 <- prune_taxa(taxa_sums(ps.E1)>0, ps.E1)
ps.E1

ps.E1.DNA <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb' &
                         sample_data(ps.norm.full)$DNA.type == 'gDNA', ps.norm.full)
ps.E1.DNA <- prune_taxa(taxa_sums(ps.E1.DNA)>0, ps.E1.DNA)
ps.E1.DNA

ps.E2 <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI' &
                         sample_data(ps.norm.full)$DNA.type == 'gDNA', ps.norm.full)
ps.E2 <- prune_taxa(taxa_sums(ps.E2)>0, ps.E2)
ps.E2

ps.E3  <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'LIwA' &
                         sample_data(ps.norm.full)$DNA.type == 'gDNA', ps.norm.full)
ps.E3 <- prune_taxa(taxa_sums(ps.E3)>0, ps.E3)
ps.E3

MyWunifrac_E1 <- distance(ps.E1, method = 'wunifrac')
MyWunifrac_E1.DNA <- distance(ps.E1.DNA, method = 'wunifrac')
MyWunifrac_E2 <- distance(ps.E2, method = 'wunifrac')
MyWunifrac_E3 <- distance(ps.E3, method = 'wunifrac')

SamDat_E1 = data.frame(sample_data(ps.E1))
SamDat_E1.DNA = data.frame(sample_data(ps.E1.DNA))
SamDat_E2 = data.frame(sample_data(ps.E2))
SamDat_E3 = data.frame(sample_data(ps.E3))

test_E1 <- adonis(MyWunifrac_E1 ~ Veg.type+PRE.hor.thickness.cm+pH+percent.total.C+
                    percent.total.N+texture+burn.trtmt+horizon, data = SamDat_E1)
test_E1.DNA <- adonis(MyWunifrac_E1.DNA ~ Veg.type+PRE.hor.thickness.cm+pH+percent.total.C+
                    percent.total.N+texture+burn.trtmt+horizon, data = SamDat_E1.DNA)
test_E2 <- adonis(MyWunifrac_E2 ~ Veg.type+PRE.hor.thickness.cm+pH+percent.total.C+
                    percent.total.N+texture+burn.trtmt+horizon, data = SamDat_E2)
test_E3 <- adonis(MyWunifrac_E3 ~ Veg.type+PRE.hor.thickness.cm+pH+percent.total.C+
                    percent.total.N+texture+burn.trtmt+horizon, data = SamDat_E3)
test_E1
test_E1.DNA
test_E2
test_E3

test_E1_sub <- adonis(MyWunifrac_E1.DNA ~ percent.total.N, data = SamDat_E1.DNA)
test_E1_sub

# Fire survival
adonis(MyWunifrac_E1 ~ Veg.type, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ PRE.hor.thickness.cm, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ pH, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ percent.total.C, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ percent.total.N, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ texture, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ burn.trtmt, data = SamDat_E1)
adonis(MyWunifrac_E1 ~ horizon, data = SamDat_E1)

adonis(MyWunifrac_E1.DNA ~ Veg.type, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ PRE.hor.thickness.cm, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ pH, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ percent.total.C, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ percent.total.N, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ texture, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ burn.trtmt, data = SamDat_E1.DNA)
adonis(MyWunifrac_E1.DNA ~ horizon, data = SamDat_E1.DNA)

# Fast growth
adonis(MyWunifrac_E2 ~ Veg.type, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ PRE.hor.thickness.cm, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ pH, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ percent.total.C, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ percent.total.N, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ texture, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ burn.trtmt, data = SamDat_E2)
adonis(MyWunifrac_E2 ~ horizon, data = SamDat_E2)

# Test of autoclaving
ps.E3.autoclave  <- prune_samples(sample_data(ps.norm.full)$incub.trtmt %in% c('LIwA','LIn'), ps.norm.full)
ps.E3.autoclave <- prune_taxa(taxa_sums(ps.E3.autoclave)>0, ps.E3.autoclave)
ps.E3.autoclave
SamDat <- data.frame(sample_data(ps.E3.autoclave))
head(SamDat,5)

MyWunifrac_E3.autoclave <- distance(ps.E3.autoclave, method = 'wunifrac')

SamDat_E3.autoclaving = data.frame(sample_data(ps.E3.autoclave))

adonis(MyWunifrac_E3.autoclave ~ Veg.type+PRE.hor.thickness.cm+pH+percent.total.C+
                    percent.total.N+texture+burn.trtmt+horizon + incub.trtmt, data = SamDat_E3.autoclaving)

adonis(MyWunifrac_E3.autoclave ~ Veg.type, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ PRE.hor.thickness.cm, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ pH, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ percent.total.C, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ percent.total.N, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ texture, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ burn.trtmt, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ horizon, data = SamDat_E3.autoclaving)
adonis(MyWunifrac_E3.autoclave ~ incub.trtmt, data = SamDat_E3.autoclaving)

```

# Figure 7:
Ordinations
```{r}
# Full ordination
ps.full.dataset <- readRDS('../../CombinedFireSim1519/ps.1519FireSim.merged')
tree <- ape::read.tree('../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')

tree <- phy_tree(tree)
tax <- tax_table(ps.full.dataset)
otu <- otu_table(ps.full.dataset)
sam <- sample_data(ps.full.dataset)

ps.full.dataset = phyloseq::phyloseq(otu,tax, sam,tree)
ps.full.dataset

# Setting some plot parameters
year.labs = c("One year post-fire","Five years post-fire")
names(year.labs) = c(1,5)
horizon.labs = c("Mineral","Organic")

# Playing with new datasets
ps = ps.full.dataset

# Add column with pairs info
sample_data(ps)$Pairs = paste(sample_data(ps)$Site_ID,sample_data(ps)$Org_or_Min,sep="_")
head(sample_data(ps)$Pairs)

# Normalize sample counts
ps.norm = transform_sample_counts(ps,function(x) x/sum(x))
sample_data(ps.norm)$Study = sample_data(ps.norm)$Years_Since_Fire
sample_data(ps.norm)$Study[is.na(sample_data(ps.norm)$Study)]="Lab"

ord.nmds = ordinate(ps.norm,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)

plot_ordination(ps.norm,ord.pcoa,color="burn.trtmt",shape="incub.trtmt")
plot_ordination(ps.norm,ord.nmds,color="pH",shape="Study")
# Neat, they all fall out on top of each other. That's nice.
colnames(sample_data(ps.norm))

ps.norm.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('pb','SI','LIwA'), ps.norm.gDNA)
ps.norm.gDNA <- prune_taxa(taxa_sums(ps.norm.gDNA)>0,ps.norm.gDNA)

MyNMDS.full.gDNA <- ordinate(ps.norm.gDNA, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)

# Ordination plot with horizons and deg.hrs
p1 = plot_ordination(ps.norm.gDNA, MyNMDS.full.gDNA, axes = c(1,2), 
                      color = "burn.trtmt",
                      shape = 'incub.trtmt') + 
  facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels,
                                                   DNA.type = DNALabels,
                                                   incub.trtmt = IncubLabels))+
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  #geom_line(aes(group = core.id.hor)) +
  labs(color = 'Burn treatment',
       #color = expression("Degree ("*degree*C*") hours"), 
       shape = 'Experiment') +
  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  scale_color_manual(values = c('black','orange','red'),
                     labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
                     breaks = c('control','wet','dry'))+
  scale_shape_manual(values = c('circle','square','triangle'),
                     labels = c('Fire survival', 'Fast growth','Post-fire envir. affinity'),
                     breaks = c('pb','SI','LIwA')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(face = 'italic',size = 16),
        axis.title = element_text(size=16),
        axis.text = element_text(size=16),
        legend.title = element_text(size=16)) + 
  theme_bw()

p1
```

# Supplementary
```{r}
# Carbon and nitrogen loss
pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Total C (%)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey90'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

pChange_N <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
  geom_boxplot(aes(x=burn.trtmt, y = percent.total.N, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
    theme_bw()+
  labs(x= 'Burn treatment',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Total N (%)',
       fill = 'Soil horizon') + 
  scale_fill_manual(values = c('black','grey90'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

cowplot::plot_grid(pChange_C, pChange_N, ncol=2)

test <- aov(percent.total.N ~ burn.trtmt, data = subset(df.meta, incub.trtmt == 'SI' & horizon == 'O'))
summary(test)
TukeyHSD(test)

# Traits
df.resp.taxa <- merge(df.survival.L2FC, df.fast.L2FC, all = TRUE) %>% merge(df.affinity.L2FC, all = TRUE)

ps.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.resp.taxa$OTU, ps.norm.full)
ps.taxa
df.taxa <- psmelt(ps.taxa)

# survival
ps.survival.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.survival.L2FC$OTU, ps.norm.full)
ps.survival.taxa

df.survival.taxa <- psmelt(ps.survival.taxa)

df.survival.taxa$burn.trtmt <- factor(df.survival.taxa$burn.trtmt, levels = c('control','wet','dry'))

p = ggplot(subset(df.survival.taxa, incub.trtmt == 'pb' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
  theme_bw()+
  facet_wrap(~horizon,ncol=1) + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil'))+
  labs(fill = 'Burn treatment',
       x = 'site',
       y='Total abundance (%)') + 
 theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

# fast
ps.fast.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.fast.L2FC$OTU, ps.norm.full)
ps.fast.taxa

df.fast.taxa <- psmelt(ps.fast.taxa)

p = ggplot(subset(df.survival.taxa, incub.trtmt == 'SI' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
  theme_bw()+
  facet_wrap(~horizon,ncol=1) + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil'))+
  labs(fill = 'Burn treatment',
       x = 'site',
       y='Total abundance (%)') + 
 theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = '',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

# affinity
ps.affinity.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.affinity.L2FC$OTU, ps.norm.full)
ps.affinity.taxa

df.affinity.taxa <- psmelt(ps.affinity.taxa)

p = ggplot(subset(df.survival.taxa, incub.trtmt == 'LIwA' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
  theme_bw()+
  facet_wrap(~horizon,ncol=1) + 
  scale_fill_manual(values = c('black','slategray3','tan3'),
                     limits = c('control','wet','dry'),
                     labels = c('control','wet soil','dry soil'))+
  labs(fill = 'Burn treatment',
       x = 'site',
       y='Total abundance (%)') + 
 theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'right',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

```

FIN --------------------------------

EXTRAS:

# figuring out corncob + trait assignments
```{r}
df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')

unique(subset(df, select = c(Experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))

df.LI <- read.csv('../data/sequence-data/LibCombined/corncob-output/Ex3 Affinity/all-responders.csv')

df$horizon <- factor(df$horizon, levels = c('O','A'))
df$Experiment <- factor(df$Experiment, levels = c('survival','fast growth','affinity'))

for (i in 1:nrow(df)) {
  if (abs(df$Estimate[i]) > 2) {
    df$trimmed.Estimate[i] = df$Estimate[i]
  } else {
    df$trimmed.Estimate[i] = NA
  }
}

p = ggplot(df) + 
  geom_histogram(aes(Estimate),fill = 'red', binwidth=1) + 
  #geom_histogram(aes(trimmed.Estimate), fill = 'blue', binwidth=1) + 
  theme_bw() + 
  facet_grid(Experiment+DNA.type~horizon, scales = 'free')

length(unique(subset(df, Temp.cutoff == 'Low thermo greater than 50 C' &
                       Experiment == 'survival')$OTU))

p1 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

p2 = ggplot(subset(df, Experiment == 'fast growth'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~pH.cutoff, scales = 'free')

p3 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
  geom_histogram() + 
  theme_bw() + 
  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')

length(unique(subset(df, Estimate > 0 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate < 0 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate > 1 & Experiment == 'affinity')$OTU))
length(unique(subset(df, Estimate < -1 & Experiment == 'affinity')$OTU))

dim(subset(df, Experiment == 'fast growth' &
             horizon == 'O' &
             Comparison == 'pb.dry.v.SI.dry' &
             pH.cutoff != 'null'))
             #Temp.cutoff != 'null'))

```

# PLotting rel. abundance of responders:
Reallying interesting data. We're seeing interesting trends with positive responders.
The relative abundance of positive responders increases across the dry soil post-burn
pH range, but decreases across the control soil pH range. 
```{r}
df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-resopnders.csv')
df.full3 <- read.csv('../data/sequence-data/LibCombined/corncob-output/Ex3 Affinity/all-responders.csv')
df.LI.norm$burn.trtmt <- factor(df.LI.norm$burn.trtmt, levels = c('control','wet','dry'))

for (i in 1:nrow(df.full3)) {
  if (df.full3$Estimate[i] > 0) {
    df.full3$Response[i] = 'positive'
  } else if (df.full3$Estimate[i] < 0) {
    df.full3$Response[i] = 'negative'
  }
}

df.full3.LIn <-  subset(df.full3, Comparison %in% c('LIn.dry.v.LIn.control'))$OTU
df.full3.LIwA <- subset(df.full3, Comparison %in% c('LIwA.dry.v.LIwA.control'))$OTU

df.count <- df.full3 %>%
  group_by(Comparison, Controlling.for) %>%
  count(Response)

# PUll out a subset of the corncob analyses:
df.affinity <- subset(df.full3, Comparison %in% c('LIwA.dry.v.LIwA.control') &
                        Controlling.for == 'pH category: low, mid, high' ) %>%
  subset(select = c(OTU, horizon, Response))

# OR just pull out positive responding OTUs:
df.affinity <- df.full3 %>%
  subset(Estimate > 0) %>%
  subset(Comparison %in% c('LIwA.dry.v.LIwA.control') & Controlling.for =='control pH') %>%
  subset(select = c(OTU, horizon, Response))

# Create a list of positive/negative responding OTUs
df.affinity.positive = subset(df.affinity, Response == 'positive')
df.affinity.negative = subset(df.affinity, Response == 'negative')

# Match these lists to the full community data.
df.LI.positive.responders <- subset(df.LI.norm, OTU %in% df.affinity.positive$OTU)
df.LI.negative.responders <- subset(df.LI.norm, OTU %in% df.affinity.negative$OTU)
df.LI.not.responders <- subset(df.LI.norm, !OTU %in% df.affinity$OTU)

# Create response categories to use in ggplot
df.LI.positive.responders$Response = 'positive'
df.LI.negative.responders$Response = 'negative'
df.LI.not.responders$Response = 'none'

# Combine the dataframe
df.LI.responders <- rbind(df.LI.positive.responders,df.LI.negative.responders,df.LI.not.responders)

# Convert pH to a character for the purpose of plotting
df.LI.responders$pH <- as.character(df.LI.responders$pH)
df.LI.responders$cntl.pH <- as.character(df.LI.responders$cntl.pH)

p1 = ggplot(subset(df.LI.responders, horizon == 'O' & site != 19), aes(x=cntl.pH, y=Abundance, fill=Response))+
  geom_bar(stat = 'identity') +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
  scale_fill_manual(values = c('forestgreen','grey50','red'),
                     limits = c('positive','none', 'negative'),
                     labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'Experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
       y = 'Relative abundance') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))

df.LI.sum <- df.LI.responders %>%
  group_by(Full.id, Response) %>%
  mutate(sum.abun = sum(Abundance)) %>%
  subset(select = c(Full.id, pH, cntl.pH, horizon, burn.trtmt, incub.trtmt, Response,site, sum.abun)) %>%
  unique()

df.LI.sum$burn.trtmt <- factor(df.LI.sum$burn.trtmt, levels = c('control','wet','dry'))
df.LI.sum$site <- as.character(df.LI.sum$site)

p2 = ggplot(subset(df.LI.sum, horizon == 'O' & Response != 'none' & burn.trtmt == 'dry'), aes(x=pH, y=(sum.abun), color = site))+
  geom_point(size=3) +
  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
             labeller = labeller(incub.trtmt = IncubLabels, 
                                 horizon = HorizonLabels,
                                 burn.trtmt = BurnLabels)) +
        stat_smooth(method=lm,se = FALSE,color='black') +
  #scale_color_manual(values = c('forestgreen','grey50','red'),
   #                  limits = c('positive','none', 'negative'),
    #                 labels = c('Positive','No Response', 'Negative')) +
  labs(title = 'Experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
       y = 'Relative abundance',
       x = 'post-burn pH') + 
  theme(legend.position = 'bottom',
        axis.text.x = element_text(size=8), 
        legend.text = element_text(size=8))+
  ylim(0,0.2)

```

# Mapping relative abundance of responding taxa across experiments:
```{r}
df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-resopnders.csv')

df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')

p = ggplot(data = df.pb.gDNA.OTU, aes(x=site, y = Abundance, fill = Phylum)) + 
  geom_bar(stat = 'identity') + 
  facet_grid(burn.trtmt~horizon) + 
  theme_bw()

df <- df.full.OTU %>%
  subset(Estimate > 0) %>%
  group_by(OTU) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(abs(Estimate) > 1) %>%
  merge(df.LI.norm) %>%
  subset(incub.trtmt == 'LIwA')

df$site <- as.character(df$site)
df$change.pH <- as.character(df$change.pH)
df$burn.trtmt <- factor(df$burn.trtmt, levels = c('control','wet','dry'))

p <- ggplot(data = subset(df, burn.trtmt == 'dry' & horizon == 'O'), 
            aes(x=site, y = Abundance, Fill = Experiment)) + 
  theme_bw()+
  #geom_point()+
  geom_bar(stat = 'identity') +
  facet_wrap(~Experiment, scale = 'free') + 
  #stat_smooth(method=lm,se = FALSE,color='black') +
  theme(axis.text.x = element_text(angle = 90))
```

# Exploring composition data for 24-hours post-burn:
```{r}
#df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
#df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')

p = ggplot(data = df.pb.gDNA.OTU, aes(x=site, y = Abundance, fill = Phylum)) + 
  geom_bar(stat='identity')+
  facet_grid(horizon~burn.trtmt, labeller = labeller(horizon = HorizonLabels,
                                                     burn.trtmt = BurnLabels)) + 
  theme_bw() +
  theme(legend.position = 'bottom')

# Most abundant taxa; most abundant responders:
df <- df.pb.gDNA.OTU %>%
  group_by(Family) %>%
  mutate(sum.Abundance = sum(Abundance))

p = ggplot(data = subset(df, sum.Abundance > 2.08), aes(x=site, y = Abundance, fill = Class)) + 
  geom_bar(stat='identity')+
  facet_grid(horizon~burn.trtmt, labeller = labeller(horizon = HorizonLabels,
                                                     burn.trtmt = BurnLabels)) + 
  theme_bw() +
  theme(legend.position = 'bottom')

```

# Calculate bray-curtis dissimilarity for LIwA vs. SI
```{r, message = FALSE}
# This is a possibly convoluted piece of code to first create a Bray-Curtis
#     dissimilarity matrix and then pull out the dissimilarities between SI and
#     LIwA cores.
ps.bray <- prune_samples(sample_data(ps.raw.gDNA)$DNA.type == 'gDNA' &
                           sample_data(ps.raw.gDNA)$incub.trtmt %in% c('SI','LIwA')&
                           sample_data(ps.raw.gDNA)$Full.id %in% df.meta$Full.id, ps.raw.gDNA)

ps.bray <- prune_taxa(taxa_sums(ps.bray) > 0, ps.bray)

dist.bray.SIvLIwA <- as.matrix(distance(ps.bray, method = 'bray', type = 'samples'))

# Convert distance matrix into dataframe
df <- data.frame(dist.bray.SIvLIwA)

# Bring in meta data and subset for specific analysis
df.meta.sub <- subset(df.meta, select = c(Full.id, burn.trtmt,site, core.id.hor,
                                          incub.trtmt,core, horizon)) %>%
  subset(incub.trtmt %in% c('SI','LIwA')) %>%
  unique()

# Combine metadata and distances so we can use burn treatment to sort
#df <- merge(df, df.meta.pb.cDNA)

# Create a dataframe with the colnames and Full.ID
x <- data.frame(str_split(colnames(df)[1:276], 'X', simplify = TRUE)[,2])

# Rename columes:
colnames(x)[1] <- 'ID.bray'

# Clean up x. 
x <- x %>%
  mutate(Full.id = ID.bray)

x$Full.id <- str_replace_all(x$Full.id, "\\.", "-")

x$X <- 'X'

x <- x %>%
  unite(Bray.ID, c('X',"ID.bray"), sep = '', remove = TRUE) %>%
  unique()

# Create row with LIwA id, SI id, and core.id.hor:
df.LIwA <- subset(df.meta, incub.trtmt == 'LIwA') %>%
  mutate(LIwA.full.id = Full.id) %>%
  subset(select = c(core.id.hor, LIwA.full.id))

df.SI <- subset(df.meta, incub.trtmt == 'SI') %>%
  mutate(SI.full.id = Full.id) %>%
  subset(select = c(core.id.hor, SI.full.id)) %>%
  unique()

#df.list <- merge(df.LIwA, df.SI, by = 'core.id.hor')

# ANd then combine the Full.id list with the control core meta data I just created.
#     df.list now contains Full.id with the corresponding control sample for each 
#     dry/wet burn and a column ("Bray.ID") that has the sample ID formatted to 
#     match the distance matrix names.
df.list <- df.SI %>%
  merge(df.meta.sub, by = 'core.id.hor') %>%
  merge(x, by = 'Full.id') %>%
  subset(incub.trtmt == 'LIwA') %>%
  unique()

df.list$burn.trtmt <- as.character(df.list$burn.trtmt)
df.list$horizon <- as.character(df.list$horizon)
df.list$incub.trtmt <- as.character(df.list$incub.trtmt)

head(df.meta.sub)
# Create and empty data frame to store distances
df.distances <- data.frame("Full.id" = df.list$Full.id, 'core.id.hor' = 'core.id.hor',
                           'burn.trtmt' = 'burn', 'SI.full.id' = 'SI.full.id',
                           'horizon' = 'H',
                           'BC.distance.btw.SI.and.LIwA' = 'distance',
                           'incub.trtmt' = 'incub') %>%
  unique()

# Now run a convoluted loop:
for (i in 1:nrow(df.list)) { # For each sample (row in df.list)
  for (j in 1:nrow(df)) { # For each row in the dissimilarity matrix
    for (k in 1:ncol(df)){ # And for each colume in the dissimilarity matrix
      if(colnames(df)[k] == df.list$Bray.ID[i] &  # If the distance matrix colume ID matches the sample ID in the list
         rownames(df)[j] == df.list$SI.full.id[i]) { # And the rowname ID matches the corresponding control core, then...
        df.distances$BC.distance.btw.SI.and.LIwA[i] = df[j,k] # Pull out the distance and store it in new dataframe
        df.distances$burn.trtmt[i] = df.list$burn.trtmt[i]
        df.distances$horizon[i] = df.list$horizon[i]
        df.distances$incub.trtmt[i] = df.list$incub.trtmt[i]
        df.distances$SI.full.id[i] = df.list$SI.full.id[i]
      }
    } 
  } 
}

# Remove any samples that didn't have duplicates between LIwA and SI
df.distances <- subset(df.distances, horizon != 'H')

df.distances$BC.distance.btw.SI.and.LIwA <- as.numeric(df.distances$BC.distance.btw.SI.and.LIwA)

df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))

p=ggplot(subset(df.distances,horizon=='O')) + 
  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.SI.and.LIwA, fill = horizon),
               alpha = 0.5) +
  theme_bw() +
  facet_wrap(~horizon, ncol=3,
             labeller = labeller(horizon = HorizonLabels)) + 
  labs(x='Burn treatment',
       #y = 'Bray-Curtis dissimilarity between \nsoil 5 weeks post-burn vs. inoculated soil 6 months post-burn',
       y='Bray-Curtis dissimilarity',
       fill = 'Soil horizon',
       title = 'Bray-Curtis dissimilarities for gDNA') + 
  scale_fill_manual(values = c('black','grey80'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  scale_x_discrete(limits = c('control','wet','dry'),
                   labels = c('Unburned \ncontrol', 'Wet soil \nburn','Dry soil \nburn')) +
  theme(axis.title = element_text(size=18),
        axis.text = element_text(size=18),
        legend.title = element_text(size=18),
        legend.text = element_text(size=18),
        strip.text = element_text(size=18))+
  ylim(0,1)

test <- aov(BC.distance.btw.SI.and.LIwA~burn.trtmt, data = subset(df.distances,horizon=='O'))
summary(test)
TukeyHSD(test)

df.meta.combined <- merge(df.meta, df.distances, by = c('Full.id', 'burn.trtmt', 'horizon', 'incub.trtmt'))

p = ggplot(subset(df.meta.combined, horizon == 'A'),aes(x=Thermo.mid.max, y = BC.distance.btw.burned.and.control, fill = horizon)) +
  geom_point(shape='circle filled',
             stroke=1,
             alpha = 0.8,
             size=3) +
  theme_bw() +
  facet_wrap(burn.trtmt~incub.trtmt, scales = 'free',
             labeller = labeller(incub.trtmt = IncubLabels,
                                 burn.trtmt = BurnLabels)) + 
  labs(x='Max temp, mid-point',
       y = 'Bray-Curtis dissimilarity compared to control; A horizon', 
       fill = 'Soil horizon',
       title = 'Bray-Curtis dissimilarities for gDNA') + 
  scale_fill_manual(values = c('black','grey40'),
                     limits = c('O','A'),
                     labels = c('Organic','Mineral')) +
  theme(axis.title = element_text(size=12),
        axis.text = element_text(size=12),
        legend.title = element_text(size=12),
        legend.text = element_text(size=12)) + 
    stat_smooth(method=lm,se = FALSE,color='black')

```

# Control pH vs. Delta pH:
```{r}
pChange_pH <- ggplot(subset(df.meta, burn.trtmt != 'control'),aes(x=cntl.pH, y = change.pH, color = Thermo.mid.max)) + 
  geom_point(aes(x=cntl.pH, y = change.pH, color = Thermo.mid.max), alpha = 0.4,size=3)  + 
      stat_smooth(method=lm,se = FALSE,color='black')+ 
    theme_bw()+
  labs(x= 'pre-burn (control) pH',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Change in post-burn pH') + 
  facet_grid(burn.trtmt~horizon, scales = 'free_y',
             labeller = labeller(horizon = HorizonLabels,
                                                     burn.trtmt = BurnLabels))+
  #scale_color_manual(values = c('black','slategray','tan3'),
   #                  limits = c('control','wet','dry'),
    #                 labels = c('control','wet soil','dry soil')) +
  theme(axis.text.y = element_text(size = 14),
        legend.title = element_text(size=14),
        axis.text.x = element_text(face="italic",size = 14),
        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
        strip.text = element_text(size=14),
        legend.text = element_text(size=14),
        legend.position = 'right',
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

pChange_pH

df.meta.dry.O <- subset(df.meta, burn.trtmt == 'dry' & horizon == 'A')

model <- lm(change.pH~cntl.pH, data = df.meta.dry.O)
model
summary(model)

```

# Scatterplot matrices to explore "severity"
```{r}
colnames(df.meta)

my_colors <- c('red','orange','black')

df1 <- df.meta %>%
  subset(DNA.type =='gDNA' & incub.trtmt == 'pb') %>%
  mutate(Frac.O.loss = (PRE.O.hor.thickness.cm - POST.O.hor.thickness.cm)/PRE.O.hor.thickness.cm) %>%
  subset(select = c(burn.trtmt, 
                    PRE.O.hor.thickness.cm,
                    avg.sand,
                    Thermo.mid.max,
                    Thermo.low.max, 
                    change.pH, 
                    change.C.N.ratio,
                    Mid.degree.C.hours,
                    Low.degree.C.hours,
                    Frac.core.dry.mass.loss,
                    Frac.core.wet.mass.loss,
                    hrzn.degree.hrs,
                    Frac.O.loss))

pairs.panels(df1[,c(2:3,8:10)], 
      method = 'pearson',
      hist.col = 'blue',
      density = TRUE,
      ellipses = TRUE,
      col = my_colors[df1$burn.trtmt],
      pch=19)

pairs.panels(df1[,c(10,11,8,9)], 
      method = 'pearson',
      hist.col = 'blue',
      density = TRUE,
      ellipses = TRUE,
      col = my_colors[df1$burn.trtmt],
      pch=19)

pairs(df1[,c(2,3,4,6,7,8,12,13)],
      method = 'pearson',
      col = my_colors[df1$burn.trtmt],
      pch=19)

df.meta <- df.meta %>%
  mutate(Frac.O.loss = (PRE.O.hor.thickness.cm - POST.O.hor.thickness.cm)/PRE.O.hor.thickness.cm)

p3 = ggplot(df.meta, aes(x=hrzn.degree.hrs,y=Frac.O.loss, color=burn.trtmt)) +
  theme_bw()+
  geom_point(size=3) + 
  stat_smooth(method=lm,color='black') +
  facet_grid(~Veg.type)

```

# Comparing autoclave v. not decay model data:
```{r}
df.coefs <- subset(df.meta, incub.trtmt != 'SI' &
                     incub.trtmt != 'pb')

p1 = ggplot(df.coefs, aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=(M1), fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(x= 'Dominant vegetation',
     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
       y = 'Fractional size of fast C pool \n(M1)',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  facet_wrap(~Veg.type) +
  theme(axis.text.y = element_text(size = 16),
        legend.title = element_text(size=16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
        strip.text = element_text(size=16),
        legend.text = element_text(size=16),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
p1

df.rsquared.5weeks <- read.csv('../data/2-pool-decay-model-output-5-weeks.csv')
df.5weeks <- subset(df.rsquared.5weeks, t == 3)

df.5weeks$incub.trtmt <- factor(df.5weeks$incub.trtmt, levels = c('SI','LIwA','LIn'))
df.5weeks$burn.trtmt <- factor(df.5weeks$burn.trtmt, levels = c('control','wet','dry'))

p1 = ggplot(df.5weeks, aes(x=burn.trtmt)) + 
  geom_boxplot(aes(y=(M1), fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
  theme_bw()+
  labs(y = 'Fractional size of fast C pool \n(M1)',
       fill = 'Burn treatment',
       color = 'Burn treatment') + 
  theme(axis.text.y = element_text(size = 16),
        legend.title = element_text(size=16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
        strip.text = element_text(size=16),
        legend.text = element_text(size=16),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")
p1

# Look at fractional C remaining at end of incubation:
df.fracC <- read.csv("../data/fractional-c-remaining.csv", row.names = 1)

df.veg <- subset(df.meta, select = c(site, Veg.type)) %>%
  unique()

df.fracC <- subset(df.fracC, DayFactor == 34) %>%
  merge(df.veg, all = TRUE)

df.fracC$incub.trtmt <- factor(df.fracC$incub.trtmt, levels = c('SI','LIwA','LIn'))
df.fracC$burn.trtmt <- factor(df.fracC$burn.trtmt, levels = c('control','wet','dry'))

p = ggplot(df.fracC, aes(x = burn.trtmt)) + 
    geom_boxplot(aes(y=fractional.C.remaining, fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
  theme_bw()+
  facet_wrap(~Veg.type)+
  labs(fill = 'Burn treatment',
       color = 'Burn treatment') + 
  theme(axis.text.y = element_text(size = 16),
        legend.title = element_text(size=16),
        axis.text.x = element_text(size = 16),
        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
        strip.text = element_text(size=16),
        legend.text = element_text(size=16),
       # legend.background = element_rect(fill = "darkgray"),
        legend.box = "vertical")

```

# ORDINATIONS - Comparing to unburned
```{r}
MyNMDS.pb.gDNA <- ordinate(ps.norm.pb.gDNA, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
MyNMDS.pb.cDNA <- ordinate(ps.norm.pb.cDNA, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
MyNMDS.SI <- ordinate(ps.norm.SI, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)

MyNMDS.LI <- ordinate(ps.norm.LI, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
MyNMDS.LI

ps.norm.LI.control <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('control'),ps.norm.LI)
ps.norm.LI.control<- prune_taxa(taxa_sums(ps.norm.LI.control)>0, ps.norm.LI.control)

ps.norm.LI.wet <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('wet'),ps.norm.LI)
ps.norm.LI.wet<- prune_taxa(taxa_sums(ps.norm.LI.wet)>0, ps.norm.LI.wet)

ps.norm.LI.dry <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('dry'),ps.norm.LI)
ps.norm.LI.dry<- prune_taxa(taxa_sums(ps.norm.LI.dry)>0, ps.norm.LI.dry)

MyNMDS.LI.control <- ordinate(ps.norm.LI.control, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
MyNMDS.LI.wet <- ordinate(ps.norm.LI.wet, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
MyNMDS.LI.dry <- ordinate(ps.norm.LI.dry, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)

MyNMDS.LI.control
MyNMDS.LI.wet
MyNMDS.LI.dry

p.LI.control = plot_ordination(ps.norm.LI.control, MyNMDS.LI.control,
                               axes=c(1,3),shape = "incub.trtmt", color = 'horizon') +
  geom_line(aes(group = core.id.hor)) +
  theme_bw() +
  geom_point(size=3)

p.LI.wet = plot_ordination(ps.norm.LI.wet, MyNMDS.LI.wet, 
                           axes = c(1,3),shape = "incub.trtmt", color = 'horizon') +  
  geom_line(aes(group = core.id.hor)) +

  theme_bw() +
  geom_point(size=3)

p.LI.dry = plot_ordination(ps.norm.LI.dry, MyNMDS.LI.dry, 
                           axes=c(1,3),shape = "incub.trtmt", color = 'horizon') +
    geom_line(aes(group = core.id.hor)) +
  theme_bw() +
  geom_point(size=3)

cowplot::plot_grid(p.LI.control,p.LI.wet,p.LI.dry, ncol=3, labels = c('Control','Wet','Dry'))

p.LI.axis1.2 = plot_ordination(ps.norm.LI, MyNMDS.LI, 
                           axes=c(1,2),shape = "horizon", color = 'burn.trtmt') +
    geom_line(aes(group = core.id.hor)) +
  theme_bw() +
  geom_point(size=3)
p.LI.axis1.3 = plot_ordination(ps.norm.LI, MyNMDS.LI, 
                           axes=c(1,3),shape = "horizon", color = 'burn.trtmt') +
    geom_line(aes(group = core.id.hor)) +
  theme_bw() +
  geom_point(size=3)
cowplot::plot_grid(p.LI.axis1.2,p.LI.axis1.3, ncol=2)

p1 = plot_ordination(ps.norm.pb.gDNA, MyNMDS.pb.gDNA, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)
p2 = plot_ordination(ps.norm.pb.gDNA, MyNMDS.pb.gDNA, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)
p3 = plot_ordination(ps.norm.SI, MyNMDS.SI, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)
p4 = plot_ordination(ps.norm.SI, MyNMDS.SI, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)
p5 = plot_ordination(ps.norm.LIwA, MyNMDS.LIwA, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)
p6 = plot_ordination(ps.norm.LIwA, MyNMDS.LIwA, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
  facet_wrap(~incub.trtmt) + theme_bw() +
  geom_point(size=3)

# using cowplot to combine multiple figures.
plot_grid(p1,p2,p3,p4,p5,p6,ncol=2)

# Full ordination
MyNMDS.full <- ordinate(ps.norm.gDNA, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)

ps.norm.pb <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb', ps.norm.full)
ps.norm.pb <- prune_taxa(taxa_sums(ps.norm.pb)>0, ps.norm.pb)
MyNMDS.pb <- ordinate(ps.norm.pb, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)

sample_data(ps.norm.pb)$horizon = factor(sample_data(ps.norm.pb)$horizon, levels = c('O','A'))

# Ordination plot with horizons and deg.hrs
p1 = plot_ordination(ps.norm.pb, MyNMDS.pb, axes = c(1,2), 
                      color = "burn.trtmt",
                      shape = 'burn.trtmt') + 
  facet_grid(horizon~DNA.type, labeller = labeller(horizon = HorizonLabels,
                                                   DNA.type = DNALabels,
                                                   incub.trtmt = IncubLabels))+
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  labs(color = 'Burn treatment',
       #color = expression("Degree ("*degree*C*") hours"), 
       shape = 'Burn treatment') +
  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  scale_color_manual(values = c('black','orange','red'),
                     labels = c('control', 'wet soil burn','dry soil burn'),
                     breaks = c('control','wet','dry'))+
  scale_shape_manual(values = c('circle','square','triangle'),
                     labels = c('control', 'wet soil burn','dry soil burn'),
                     breaks = c('control','wet','dry')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(face = 'italic',size = 16),
        axis.title = element_text(size=16),
        axis.text = element_text(size=16),
        legend.title = element_text(size=16)) + 
  theme_bw()

p1

p2 = plot_ordination(ps.norm.gDNA, MyNMDS.full, axes = c(2,3), 
                      color = "pH",
                      shape = 'burn.trtmt') + 
  facet_grid(horizon~incub.trtmt, labeller = labeller(horizon = HorizonLabels))+
  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
  geom_point(size=3, alpha=0.8) +
  labs(color = 'post-burn pH',
       #color = expression("Degree ("*degree*C*") hours"), 
       shape = 'Burn treatment',
       title = "Ch 4, p2: NMDS ordination on weighted unifrac dissimilarities \n All DNA samples; all timepoints") +
  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
  #scale_shape_manual(values = c('circle','square','triangle'),
   #                  labels = c('control', 'wet soil burn','dry soil burn'),
    #                 breaks = c('control','wet','dry')) +
  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
  #scale_shape_manual(values = c('circle','triangle'),
   #                  labels = c('O horizon','Mineral'),
    #                 breaks = c('O','A')) + 
  theme(legend.text = element_text(face = 'italic',size = 16),
        axis.title = element_text(size=16),
        axis.text = element_text(size=16),
        legend.title = element_text(size=16)) + 
  theme_bw()

p2
```

# ORDINATIONS - Comparing SI to LIwA - inoculated burned soils look more like uninoculated burned 5-week samples
```{r}
ps.norm.SI.v.LIwA <- prune_samples(sample_data(ps.norm.full)$incub.trtmt %in% c('SI','LIwA'), ps.norm.full)

ps.subset <- prune_samples(sample_data(ps.norm.SI.v.LIwA)$horizon == 'O' &
                             sample_data(ps.norm.SI.v.LIwA)$burn.trtmt != 'wet',ps.norm.SI.v.LIwA)

MyNMDS.inoculation <- ordinate(ps.subset, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)

IncubLabels = c('5 weeks post-burn', 'Inoculated soils \n6 months post-burn')
names(IncubLabels) = c('SI', 'LIwA')

p.inoc = plot_ordination(ps.subset, MyNMDS.inoculation,
                               axes=c(1,2),shape = "burn.trtmt", color='burn.trtmt') +
  geom_point(size=2)+
  geom_line(aes(group = site), color = 'grey60') +
  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt=IncubLabels))+
  scale_color_manual(values = c('black','tan3'),
                     limits = c('control','dry'),
                     labels = c('Unburned \ncontrol','Dry soil')) +
  scale_shape_manual(values = c('circle','triangle'),
                     limits = c('control','dry'),
                     labels = c('Unburned \ncontrol','Dry soil')) +
  labs(shape = 'Burn treatment',
       color = 'Burn treatment')+
  theme_bw() +
  geom_point(size=3)

p.inoc
```

# Phylogenetic tree:
```{r, message = FALSE}
ps.traits <- phyloseq::prune_taxa(df.trait$OTU, ps.raw.full)

AbunTaxa = taxa_names(filter_taxa(ps.norm.gDNA, function(x) mean(x) > 0.001, TRUE))

length(AbunTaxa)
ps.prune = prune_taxa(AbunTaxa, ps.raw.full)
ps.prune

ps.prune <- ps.raw.full %>%
  subset_samples(burn.trtmt %in% c('dry'))

ps.prune <- prune_taxa(AbunTaxa, ps.prune)

p = ggtree(ps.prune, aes(color=Phylum), 
           branch.length = 'none',
           layout = 'circular') + 
  geom_treescale() + 
  geom_tiplab2(size=2, aes(angle=angle))

tree <- read.tree(file = '../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')
tree <- phy_tree(ps.prune)

plot(tree, type = 'cladogram')

# using cowplot to combine multiple figures.
cowplot::plot_grid(p,p1, ncol=2, labels = c('A','B'))

```

# Number of responding OTUs for each experiment:
```{r}
df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
head(df.full.OTU)

# Filter responders:
df.full <- df.full.OTU %>%
  subset(abs(Estimate) > 1) # removes 1500 non-unique OTUs
dim(df.full)

df.PB.pos.rspd <- subset(df.full, Experiment == 'survival' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%  
  mutate(Response = 'positive') %>%
  unique()

df.PB.neg.rspd <- subset(df.full, Experiment == 'survival' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique()

summary(df.PB.pos.rspd$Estimate)
length(unique(df.PB.pos.rspd$OTU))
length(unique(df.PB.neg.rspd$OTU))

df.SI.cntl.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  unique()
df.SI.cntl.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
  subset(Comparison == 'pb.control.v.SI.control') %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique()

df.SI.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() %>% 
  subset(!(OTU %in% df.SI.cntl.pos.rspd$OTU))
length(unique(df.SI.pos.rspd$OTU))

df.SI.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  unique() %>%
  mutate(Response = 'negative') %>%
  subset(!(OTU %in% df.SI.cntl.neg.rspd$OTU))

length(unique(df.SI.neg.rspd$OTU))

# LIwA:
df.LIwA <- subset(df.full, Experiment == 'affinity')

df.LIwA.pos.rspd <- subset(df.full, Experiment == 'affinity' & Estimate > 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU, horizon) %>%
  mutate(max.Estimate = max(Estimate)) %>%
  subset(max.Estimate == Estimate) %>%
  mutate(Response = 'positive') %>%
  unique() 
length(unique(df.LIwA.pos.rspd$OTU))

df.LIwA.neg.rspd <- subset(df.full, Experiment == 'affinity' & Estimate < 0) %>%
  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
                            'Mid thermo greater than 50 C')) %>%
  group_by(OTU,horizon) %>%
  mutate(min.Estimate = min(Estimate)) %>%
  subset(min.Estimate == Estimate) %>%
  mutate(Response = 'negative') %>%
  unique() 
length(unique(df.LIwA.neg.rspd$OTU))

df.responders <- rbind(df.PB.pos.rspd, df.PB.neg.rspd,
                       df.SI.pos.rspd, df.SI.neg.rspd,
                       df.LIwA.pos.rspd, df.LIwA.neg.rspd)
head(df.responders)

p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = Experiment)) + 
  geom_point(size=2) + 
  theme_bw() + 
  facet_grid(horizon~Experiment) + 
  geom_vline(xintercept = 0)

# Are fire survivors likely to be fast growing?
length(df.PB.pos.rspd$OTU)
dim(subset(df.PB.pos.rspd, OTU %in% df.SI.pos.rspd$OTU))
# --> No not really. Of 19 fire survivors, only 2 are fast growing.

# Are fast growing taxa also survivors?
length(unique(df.SI.pos.rspd$OTU))
dim(subset(df.SI.pos.rspd, OTU %in% df.PB.pos.rspd$OTU)) 
# --> No, of 98 OTUs identified as fast growing, only 2 were also identified as fire surviving.

# Do fast growing taxa show post-fire affinity?
length(unique(df.SI.pos.rspd$OTU))
length(unique(subset(df.SI.pos.rspd, OTU %in% df.LIwA.pos.rspd$OTU))$OTU)
length(unique(subset(df.SI.pos.rspd, OTU %in% df.LIwA.neg.rspd$OTU))$OTU)
# --> 8 of 98 are positive+positive, 
# --> 5 of 98 are positive+negative

# Are positive affinity taxa also fire susceptible?
length(df.LIwA.pos.rspd$OTU)
dim(subset(df.LIwA.pos.rspd, OTU %in% df.PB.neg.rspd$OTU))
# --> Nope. Only 1 of the positive affinity taxa was identified as fire susceptible.

# Are positive affinity taxa also fast growers?
length(df.LIwA.pos.rspd$OTU)
dim(subset(df.LIwA.pos.rspd, OTU %in% df.SI.pos.rspd$OTU))
# --> Not really, 7 of 53 positive affinity taxa identified as fast growing.

# Are negative affinity taxa the same as slow growing taxa?
length(df.LIwA.neg.rspd$OTU) 
dim(subset(df.LIwA.neg.rspd, OTU %in% df.SI.neg.rspd$OTU))
# Not really, 12 of 199 (10%) of negative affinity taxa were identified as slow growing.

# DO fire survivors appear to have an affinity for post-fire environment?
length(df.PB.pos.rspd$OTU)
dim(subset(df.PB.pos.rspd, OTU %in% df.LIwA.pos.rspd$OTU))
# --> Nope. 1 of 19

# What about an anti-affinity?
dim(subset(df.PB.pos.rspd, OTU %in% df.LIwA.neg.rspd$OTU))
# --> Nop3. 2 of 19.
```

# Attempt at 3D plot
```{r}
# GRoup by Order
ps.norm.gDNA <- ps.norm.gDNA %>%
  tax_glom('Phylum')

df.norm.gDNA.Phylum <- psmelt(ps.norm.gDNA)

df.Phylum.pb <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'pb') %>%
  group_by(Phylum, core.id.hor) %>%
  mutate(mean.Abun.pb = mean(Abundance)) %>%
  subset(select = c(Domain, Phylum, mean.Abun.pb, core.id.hor, burn.trtmt))

df.Phylum.SI <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'SI') %>%
  group_by(Phylum, core.id.hor) %>%
  mutate(mean.Abun.SI = mean(Abundance)) %>%
  subset(select = c(Domain, Phylum, mean.Abun.SI, core.id.hor, burn.trtmt))

df.Phylum.LIn <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'LIn') %>%
  group_by(Phylum, core.id.hor) %>%
  mutate(mean.Abun.LIn = mean(Abundance)) %>%
  subset(select = c(Domain, Phylum, mean.Abun.LIn, core.id.hor, burn.trtmt))

df.Phylum.LIwA <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'LIwA') %>%
  group_by(Phylum, core.id.hor) %>%
  mutate(mean.Abun.LIwA = mean(Abundance)) %>%
  subset(select = c(Domain, Phylum, mean.Abun.LIwA, core.id.hor, burn.trtmt))

df <- merge(df.Phylum.pb, df.Phylum.SI) %>%
  merge(df.Phylum.LIn) %>%
  merge(df.Phylum.LIwA) %>%
  subset(mean.Abun.pb > 0.1 |
           mean.Abun.SI > 0.1 |
           mean.Abun.LIn > 0.1)

# Plot
p = ggplot(df, aes(x=mean.Abun.pb, 
                   y=mean.Abun.SI, 
                   color=Phylum, 
                   shape = burn.trtmt,
                   size = mean.Abun.LIn))+
  geom_point() + 
  #facet_wrap(~Phylum, scales = 'fixed') + 
  ylim(0,1) + 
  xlim(0,1)
p

cols <- c('red','orange','yellow','green','blue','purple','pink','black','grey10','grey20', 'forestgreen')

df$color <- mycolors[as.numeric(df$Phylum)]

# 3D plot with scatterplot3d - problems with coloring by variable
with(df,
     scatterplot3d(x = mean.Abun.pb, 
                  y = mean.Abun.SI,
                  z = mean.Abun.LIn))

# 3D plot with rgl
plot3d(
  x=df$mean.Abun.pb, y=df$mean.Abun.SI, z=df$mean.Abun.LIn,
  type = 's',
  raidus = 0.1)
```

### 2022-03-31 OTU-counts.R

@@ -1,0 +1,211 @@
+ps.cDNA.wet <- prune_samples(sample_data(ps.cDNA.raw)$burn.trtmt == 'wet', ps.cDNA.raw)
+
+ps.cDNA.wet <- prune_taxa(taxa_sums(ps.cDNA.wet)>0, ps.cDNA.wet)
+
+df.cDNA.wet <- psmelt(ps.cDNA.wet)
+
+
+df.control.counts <- df.cDNA.control %>%
+  subset(Abundance > 0) %>%
+  mutate(Frequence = 1) %>%
+  group_by(site) %>%
+  summarize(OTUnum = sum(Frequence))
+
+df.dry.site.counts <- df.cDNA.dry %>%
+  subset(Abundance > 0) %>%
+  subset(select = c(site, OTU))
+
+
+df.wet.site.counts <- df.cDNA.wet %>%
+  subset(Abundance > 0) %>%
+  subset(select = c(site, OTU))
+
+
+df.counts <- df.cDNA.control %>%
+  subset(Abundance > 0) %>%
+  merge(df.dry.site.counts) %>%
+  mutate(Frequency = 1) %>%
+  group_by(site) %>%
+  summarize(OTUnum = sum(Frequency))
+
+
+
+ps.gDNA.dry <- prune_samples(sample_data(ps.gDNA.raw)$burn.trtmt == 'dry', ps.gDNA.raw)
+
+ps.gDNA.dry <- prune_taxa(taxa_sums(ps.gDNA.dry)>0, ps.gDNA.dry)
+
+df.gDNA.dry <- psmelt(ps.gDNA.dry)
+
+ps.gDNA.control <- prune_samples(sample_data(ps.gDNA.raw)$burn.trtmt == 'control', ps.gDNA.raw)
+
+ps.gDNA.control <- prune_taxa(taxa_sums(ps.gDNA.control)>0, ps.gDNA.control)
+
+df.gDNA.control <- psmelt(ps.gDNA.control)
+
+ps.gDNA.wet <- prune_samples(sample_data(ps.gDNA.raw)$burn.trtmt == 'wet', ps.gDNA.raw)
+
+ps.gDNA.wet <- prune_taxa(taxa_sums(ps.gDNA.wet)>0, ps.gDNA.wet)
+
+df.gDNA.wet <- psmelt(ps.gDNA.wet)
+
+
+df.control.counts <- df.gDNA.control %>%
+  subset(Abundance > 0) %>%
+  mutate(Frequence = 1) %>%
[…]

### 2022-03-31 OTU-trait-list.R

@@ -1,0 +1,651 @@
+# Today's goal (21.Oct.2021) - for each experiment, create a dataframe with the
+#    positive responders and a composite mu value. I can calculate this mu value
+#    in different ways - max, min, mean - and create a weighted mu value.
+#    So the resulting dataframe will have a mu.survival.max (or mu.mean or mu.min) and a 
+#    mu.survival.weighted
+
+library(ggplot2)
+library(dplyr)
+library(phyloseq)
+library(tidyr)
+
+setwd('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data')
+# Experiment 1: -----
+#     Import data
+df.1.low <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/low-thermo-cutoff-50C.csv')
+df.1.mid <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/Mid-thermo-cutoff.csv')
+
+df.1 <- rbind(df.1.low,df.1.mid)
+
+head(df.1)
+dim(df.1) # total of 951 responders
+length(unique(df.1$OTU)) # 388 unique OTU responders
+
+# Create dataframe with unique OTU identifies
+y <- data.frame(unique(df.1$OTU))
+colnames(y)[1] = 'OTU'
+y$Responder.in.n.analyses = 0
+y$Pos.count = 0
+y$Neg.count = 0
+
+# Calculate the number of times that each OTU was identified as a pos/neg fire responder
+for (i in 1:nrow(y)) {
+  for (j in 1:nrow(df.1)) {
+    if (df.1$OTU[j] == y$OTU[i]) {
+      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]+1
+    } else {
+      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]
+    }
+  }
+}
+
+for (i in 1:nrow(y)) {
+  for(j in 1:nrow(df.1)) {
+    if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] > 0) {
+      y$Pos.count[i] = y$Pos.count[i] + 1
+    } else if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] < 0) {
+      y$Neg.count[i] = y$Neg.count[i] + 1
+    } else {
[…]

### 2022-03-31 compile_thermocouple_data_all_burns.R

@@ -1,0 +1,54 @@
+# --------------------
+# 
+# Title: compile_thermocouple_data_all_burns
+# Author: Dana Johnson
+# Date: 2020-Feb-03
+#
+# Purpose: This is code to compile all thermocouple data from simulated burns at FPL
+# into a single data file "Temp-all-burns"
+#
+# --------------------
+
+setwd("C:/Users/danab/Box Sync/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data/FireSim2019_Temp/")
+
+# Import packages
+# library(dplyr)
+# library(ggplot2)
+
+# library(plyr)
+# library(readr)
+
+library(tidyverse)
+library(stringr)
+
+## Import all .csv files from location (mydir) 
+myfiles = list.files(pattern="*.csv", full.names=TRUE)
+
+
+# Combine all the raw temp .csv files into one (df) and add column with site ID
+df <- myfiles %>%
+  setNames(nm = .) %>%
+  map_df(~read_csv(.x,col_types = cols(), col_names = FALSE), .id = "File_name")
+
+# Rename colums
+col.names <- c('Site_ID','time_s','Thermo_mid','Thermo_low')
+names(df) <- col.names
+
+class(df$time_s)
+
+# Removing rows in column time_s 
+df <- subset(df, time_s != 'time_s')
+
+df$time_s = as.numeric(df$time_s)
+
+# Use only first couple hours of burn time
+df <- subset(df, time_s < 18000)
+
+# Get rid of lower temperatures
+df <- subset(df, Thermo_mid >20 | Thermo_low >20)
+
+# export new .csv file with compiled temp data
+write.csv(df,"C:/Users/danab/Box Sync/WhitmanLab/Projects/WoodBuffalo/WB2019/data/FireSim2019_Temp\\Temp-all-burns.csv")
+
+
+

### 2022-03-31 compiling-log2FC-all-experiments.R

@@ -1,0 +1,497 @@
+library(dplyr)
+library(corncob)
+library(ggplot2)
+getwd()
+setwd('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/code')
+
+df <- read.csv('../data/sequence-data/LibCombined/corncob-output/raw-df_L2FC.csv')
+df.fast <- read.csv('../data/sequence-data/LibCombined/corncob-output/fast-Mid-and-low-thermo-L2FC.csv')
+
+
+head(df,2)
+head(df.fast,2)
+unique(df$test)
+unique(df.fast$test)
+
+summary(df$cntl.pH)
+
+
+df <- rbind(df, df.fast) %>%
+  subset(!(test %in% c("dt.DvD.O.gt50","dt.DvD.A.gt50","dt.DvD.O.lt50","dt.DvD.A.lt50",
+                       "dt.WvW.O.lt50" ,"dt.WvW.A.lt50","dt.CvC.O.lt50","dt.CvC.A.lt50")))
+
+unique(df$test)
+
+head(df)
+dim(df)
+unique(df$test)
+
+df <- df %>% subset(test != 'test')
+dim(df)
+
+df$experiment = 'x'
+df$burn.comparison = 'x'
+df$horizon = 'x'
+df$Temp.cutoff = 'x'
+df$pH.cutoff = 'x'
+df$controlling.for = 'x'
+
+for (i in 1:nrow(df)) {
+# Experiment 1, low thermo. 
+  if (df$test[i] == 'dt.RNA.dryBurn.O.gt50') {
+    df$test[i] = 'dt.low.RNA.dryBurn.O.gt50'
+    df$experiment[i] = 'survival'
+    df$burn.comparison[i] ='dry.v.control'
+    df$horizon[i] = 'O'
+    df$Temp.cutoff[i] = 'low thermo greater than 50 C'
+    df$pH.cutoff[i] = 'null'
+    df$controlling.for[i] = 'cntl.pH'
+  }   else if (df$test[i] == 'dt.RNA.dryBurn.A.gt50') {
+    df$test[i] = 'dt.low.RNA.dryBurn.A.gt50'
+    df$experiment[i] = 'survival'
+    df$burn.comparison[i] ='dry.v.control'
+    df$horizon[i] = 'A'
+    df$Temp.cutoff[i] = 'low thermo greater than 50 C'
+    df$pH.cutoff[i] = 'null'
+    df$controlling.for[i] = 'cntl.pH'
[…]

### 2022-03-31 corncob-experiment1.R

@@ -1,0 +1,591 @@
+# --------------------
+# Title: FireSim2019 Experiment 1 corncob analysis
+# Author: Dana Johnson
+# Date: 2021-Oct-13
+#
+
+# set-up -----
+
+library(corncob)
+library(phyloseq)
+library(magrittr)
+library(dplyr)
+
+#setwd("C:/Users/danab/Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/")
+
+
+# Corncob analysis for Manuscript: 
+# Input data -----
+#      Input to corncob is raw count data!
+
+ps.raw.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
+ps.raw.full
+
+ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
+ps.norm.full
+
+
+ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
+
+
+ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
+
+
+ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)
+ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
+
+# Abundance cut off and Phylum level prep -----
[…]

### 2022-03-31 corncob-experiment2-TempCutoff.R

@@ -1,0 +1,834 @@
+# --------------------
+# Title: FireSim2019 Experiment 2 corncob analysis, temperature cutoff
+# Author: Dana Johnson
+# Date: 2021-Oct-13
+#
+# set-up -----
+
+library(corncob)
+library(phyloseq)
+library(magrittr)
+library(dplyr)
+
+# Input data -----
+#      Input to corncob is raw count data!
+
+ps.raw.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
+ps.raw.full
+
+ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
+#ps.norm.full
+
+
+ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
+
+
+ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
+
+
+ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)
+ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
+
+# Create phylum dataset:
+#ps.raw.phylum <- tax_glom(ps.raw.full, taxrank = 'Phylum')
+#ps.raw.phylum
+
+
[…]

### 2022-03-31 corncob-experiment2-pHclasses.R

@@ -1,0 +1,1112 @@
+# --------------------
+# Title: FireSim2019 Experiment 2: sliding pH categories x 3
+# Author: Dana Johnson
+# Date: 2021-Oct-13
+#
+# set-up -----
+
+library(corncob)
+library(phyloseq)
+library(magrittr)
+library(dplyr)
+
+
+# Input data -----
+#      Input to corncob is raw count data!
+
+ps.raw.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
+ps.raw.full
+
+ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
+#ps.norm.full
+
+
+ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
+
+
+ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                               sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                              sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                             sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                            sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
+
+
+ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)
+ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
+
+# Create phylum dataset:
+#ps.raw.phylum <- tax_glom(ps.raw.full, taxrank = 'Phylum')
+#ps.raw.phylum
+
+
+
[…]

### 2022-03-31 corncob-experiment3.R

@@ -1,0 +1,564 @@
+# --------------------
+# Title: FireSim2019 Experiment 3 corncob analysis
+# Author: Dana Johnson
+# Date: 2021-Oct-13
+#
+
+# set-up -----
+
+library(corncob)
+library(phyloseq)
+library(magrittr)
+library(dplyr)
+
+# Corncob analysis for Manuscript: 
+# Input data -----
+#      Input to corncob is raw count data!
+
+ps.raw.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
+ps.raw.full
+
+ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
+ps.norm.full
+
+
+ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
+
+
+ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                                sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
+
+
+ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)
+ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
+
+
+### EXPERIMENT 1 -----
+
+ps.raw.LIwA <- ps.raw.full %>%
+  phyloseq::subset_samples(incub.trtmt %in% c('LIwA'))
+
+
+# DRY BURNS -----
[…]

### 2022-03-31 create-phyloseq.R

@@ -1,0 +1,480 @@
+# --------------------
+# Title: Creating phyloseq object
+# Author: Dana Johnson
+# Date: 2021-April-6
+#
+# Purpose: Make figures from seq data 
+
+# Libraries -----
+library(phyloseq)
+library(ggplot2)
+library(tidyverse)
+library(corncob)
+
+
+# OBJECTIVE: Combine reads from Lanes 1 and 2 ----- 
+
+# Create master sample list:
+### Lib1:
+SamList <- read.csv('../data/sequence-data/Lib1-CombinedLanes/Seq-IDs-by-lane-lib1.csv',fileEncoding="UTF-8-BOM")
+### Lib2:
+SamList <- read.csv('../data/sequence-data/Lib2-CombinedLanes/Seq-IDs-by-lane-lib2.csv', fileEncoding = "UTF-8-BOM")
+### Combined Libs:
+SamList <- read.csv('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data/sequence-data/LibCombined/Seq-IDs-combined-libs.csv', fileEncoding = "UTF-8-BOM")
+
+SamList <- read.csv('data-exploration/data/LibCombined/Seq-IDs-combined-libs.csv')
+head(SamList)
+
+# End of Lane 1-specific code; skip to line 33
+
+# Converge ID list to phyloseq object
+SamList <- sample_data(SamList)
+
+# Assign the sample names to match the samples' IDs
+sample_names(SamList) = SamList$Lane.IDs
+
+# Import necessary seq data
+### Lib1:
+ps <- import_biom('../data/sequence-data/Lib1-CombinedLanes/full-diversity_OTU_table/feature-table-metaD-tax.biom')
+### Lib2: 
+ps <- import_biom('../data/sequence-data/Lib2-CombinedLanes/full-diversity_OTU_table/feature-table-metaD-tax.biom')
+ps
+### Combined Libs:
+ps <- import_biom('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data/sequence-data/LibCombined/full-diversity_OTU_table/feature-table-metaD-tax.biom')
+
+ps <- import_biom('data-exploration/data/LibCombined/full-diversity_OTU_table/feature-table-metaD-tax.biom')
+
[…]

### 2022-03-31 creating_burn_temp_profiles.R

@@ -1,0 +1,341 @@
+# --------------------
+# 
+# Title: creating-burn-temp-profiles
+# Author: Dana Johnson
+# Date: 2020-Feb-3
+#
+# Purpose: This is code to plot the temperature profiles during simulated burns.
+# Can I add this to Git?
+# --------------------
+# Import packages
+library(tidyverse)
+library(stringr)
+library(ggplot2)
+# --------------------
+
+# Read temperature data
+df <-read.csv('../Temp-all-burns-clean.csv')
+
+
+# Quick look at maximum temperatures across vegetation type and burn severity
+X <- df %>%
+  subset(Leading_species == 'Picea_mariana') %>%
+  subset(Thermo_position == 'Mid') %>%
+  subset(Burn_severity == 'High_Sev') %>%
+  group_by(Site) %>%
+  mutate(max.Temp = max(Temp))
+range(X$max.Temp)
+
+
+# Fix column name
+names(df)[1] <- 'core.id'
+
+# Remove core that fell on ground
+df <- subset(df, core.id != '19UW-WB-11-02')
+
+# Change time to numeric
+class(df$time_s)
+df$time_s = as.numeric(df$time_s)
+
+
+# Integrate area under the curve for "cumulative temperature" (terminology?)
+df.full <- read.csv('../Temp-all-burns.csv')
+
+# Calculate cumulative temperature above a baseline of 21 degrees C and convert 
+#   to "degrees * hours"
+# 
+df.full <- df.full %>%
+  subset(Thermo_mid >0) %>%
+  subset(Thermo_low > 0) %>%
+  group_by(Site_ID) %>%
+  mutate(cumul.T.s.mid = sum(Thermo_mid-18)) %>%
+  mutate(cumul.T.s.low = sum(Thermo_low-18)) %>%
+  mutate(cumul.T.hr.mid = cumul.T.s.mid /3600) %>%
+  mutate(cumul.T.hr.low = cumul.T.s.low/3600) %>%
+# Subset this dataframe to include just the site ID and the cumulative temp data.
+  subset(time_s == 501) %>%
+  subset(select = c(Site_ID,
+                    cumul.T.hr.mid,
+                    cumul.T.hr.low))
+# Save as .csv file
+# write.csv(df.area, '../Cumulative-temp-above-18-degrees.csv')
+
+
+
+# Create names vector 
+names.vec <- seq(1,19, by=1)
+
+# Create output dataframe
+output.df <- data.frame("core.id" = NULL, 
+                            "Site" = NULL, 
[…]

### 2023-02-03 README.rmd
Add annotations to scripts and add README

Scripts for analyzing data associated with "Experimentally-determined traits shape bacterial community composition one and five years following wildfire"

corncob-experiment1.R: tests for differentially abundant OTUs in unburned soil vs. soil 24 hrs post-burn using the corncob package (Martin et al. 2020)

corncob-experiment2-pHclasses.R: tests for differentially abundant OTUs in unburned/burned soils after a 24 hr vs. 5 week incubation using corncob

corncob-experiment3.R: tests for differentially abundant OTUs in burned vs. unburned soils following autoclaving, inoculation with unburned soil, and a 6 month incubation

create-phyloseq.R: takes seq data in form of BIOM table and list of sequence IDs and cleans up samples by removing blanks, lab standard, duplicated samples. Output is a phyloseq object with sample ID, taxonomic table, OTU table, and phylogenetic tree.

decay-model-two-pool.R: Fits two pool decay model to CO2 respiration data

Manuscript-figrues.Rmd: Script to create figures in the manuscript and SI

OTU-trait-list.R - compiles list of OTUs identified as differentially enriched from each experiment

rrndb-SI.R: Assigns mean predicted 16S copy numbers to OTUs based on taxonomy

### 2023-02-03 OTU-trait-list.R

@@ -8,644 +8,893 @@ library(ggplot2)
 library(dplyr)
 library(phyloseq)
 library(tidyr)
+library(phyloseq)
 
-setwd('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data')
-# Experiment 1: -----
-#     Import data
-df.1.low <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/low-thermo-cutoff-50C.csv')
-df.1.mid <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/Mid-thermo-cutoff.csv')
-
-df.1 <- rbind(df.1.low,df.1.mid)
-
-head(df.1)
-dim(df.1) # total of 951 responders
-length(unique(df.1$OTU)) # 388 unique OTU responders
-
-# Create dataframe with unique OTU identifies
-y <- data.frame(unique(df.1$OTU))
-colnames(y)[1] = 'OTU'
-y$Responder.in.n.analyses = 0
-y$Pos.count = 0
-y$Neg.count = 0
-
-# Calculate the number of times that each OTU was identified as a pos/neg fire responder
-for (i in 1:nrow(y)) {
-  for (j in 1:nrow(df.1)) {
-    if (df.1$OTU[j] == y$OTU[i]) {
-      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]+1
-    } else {
-      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]
-    }
-  }
-}
-
-for (i in 1:nrow(y)) {
-  for(j in 1:nrow(df.1)) {
-    if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] > 0) {
-      y$Pos.count[i] = y$Pos.count[i] + 1
-    } else if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] < 0) {
-      y$Neg.count[i] = y$Neg.count[i] + 1
-    } else {
-      y$Pos.count[i] = y$Pos.count[i]
-      y$Neg.count[i] = y$Neg.count[i]
-    }
-  }
-}
-
-# Combine this data with the full corncob output:
-z <- merge(df.1, y)
-hist(z$Responder.in.n.analyses)
-
-Problem.OTUs <- subset(y, Pos.count > 0 & Neg.count > 0) 
-
-df.problem <- subset(df.1, OTU %in% Problem.OTUs$OTU) %>%
-  merge(Problem.OTUs)
[…]

### 2023-02-03 corncob-experiment2-pHclasses.R

@@ -10,7 +10,6 @@ library(phyloseq)
 library(magrittr)
 library(dplyr)
 
-
 #setwd("C:/Users/danab/Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/")
 
 ### CORNCOB TAKES RAW SEQ DATA AS INPUT ###
@@ -37,7 +36,7 @@ ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-0
                              sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                             sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
 
-# Remove taxa with 0 abundance:
+# Remove taxa with 0 abundance and filter for only genomic DNA:
 ps.raw.prune <-  prune_samples(sample_data(ps.raw.full)$incub.trtmt %in% c('pb','SI') &
                                 sample_data(ps.raw.full)$DNA.type == 'gDNA', ps.raw.full) 
 ps.raw.prune <- prune_taxa(taxa_sums(ps.raw.prune)>0, ps.raw.prune) 
@@ -55,7 +54,7 @@ ps.norm.prune <- prune_taxa(taxa_sums(ps.norm.prune)>0, ps.norm.prune)
 #ps.raw.prune <- ps.raw.phylum
 
 
-### Step 4. Create sliding pH categories -----
+### Step 3. Create sliding pH categories -----
 
 df <- data.frame(sample_data(ps.raw.prune))
 
@@ -99,17 +98,19 @@ sample_names(ps.df) = df$Full.id
 sample_data(ps.raw.prune) <- ps.df
 
 
-### Step 4 XXX, dry burns ----
 
+
+### Step 4: Subset phyloseq by burn.trtmt and run corncob ----
 ps.DvD <- prune_samples(sample_data(ps.raw.prune)$burn.trtmt == 'dry', ps.raw.prune)
+ps.WvW <- prune_samples(sample_data(ps.raw.prune)$burn.trtmt == 'wet', ps.raw.prune)
+ps.CvC <- prune_samples(sample_data(ps.raw.prune)$burn.trtmt == 'control', ps.raw.prune)
 
-### pH 3 to 7, Dry burns, O horizon -----
-ps.corncob.DvD.O.pH3to7 <-  prune_samples(sample_data(ps.DvD)$horizon == 'O' & 
+### pH 3 to 7, Dry burns, O horizon
[…]

### 2023-02-06 Manuscript-figures.Rmd
Include README file and finalize corncob scripts

@@
 knitr::opts_chunk$set(out.width = '100%')
+
 ```
@@
 
-df.fast <- subset(df.full, Experiment == 'fast growth' &
+df.fast <- subset(df.full, experiment == 'fast growth' &
                         Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
@@
   subset(Estimate == max.Estimate) %>%
-  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, Experiment,
+  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
                     horizon, Domain, Phylum, Class, Order, Family, Genus, 
@@
 df.SI.responders <- df.full.OTU %>%
-  subset(Experiment == 'fast growth') %>%
+  subset(experiment == 'fast growth') %>%
   merge(RDP)
@@
 ```{r}
-df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
-df.L2FC <- read.csv('../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')
+
+df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/all-responders.csv')
+df.L2FC <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')
 
@@
 df.survival <- df %>%
-  subset(Experiment == 'survival'&
-           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') & 
-           Estimate > 0) %>%
-  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
+  subset(experiment == 'survival'&
+           T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C') & 
+           intercept > 0) %>%
+  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
   subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
@@
 df.survival.L2FC <- df.L2FC %>%
-  subset(Experiment == 'survival'  &
-           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
+  subset(experiment == 'survival'  &
+           T.cutoff %in% c('low thermo > 50C','Mid thermo > 50C') &
            mu > 0) %>%
@@
 df.fast <- df %>%
-  subset(Experiment == 'fast growth'&
-           Estimate > 0) %>%
-  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
+  subset(experiment == 'fast growth'&
+           intercept > 0) %>%
+  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
   subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
@@
 df.fast.L2FC  <- df.L2FC %>%
-  subset(Experiment == 'fast growth'  &
+  subset(experiment == 'fast growth'  &
            mu > 0) %>%
@@
 df.affinity <- df %>%
-  subset(Experiment == 'affinity'&
-           Temp.cutoff %in% c('Low thermo greater than 50 C','Mid thermo greater than 50 C') &
-           Estimate > 0) %>%
-  subset(Estimate > (mean(Estimate)-1*sd(Estimate)) ) %>% 
+  subset(experiment == 'affinity'&
+           T.cutoff %in% c('Low thermo > 50','Mid thermo > 50') &
+           intercept > 0) %>%
+  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
   subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
@@
 df.affinity.L2FC  <- df.L2FC %>%
-  subset(Experiment == 'affinity'  &
-           Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C') &
+  subset(experiment == 'affinity'  &
+           T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C') &
            mu > 0) %>%
@@
 # Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
-#   the mean of the estimate. Remove duplicate taxa. 
-df.survival <- subset(df, Experiment == 'survival' &
-                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
+#   the mean of the intercept. Remove duplicate taxa. 
+df.survival <- subset(df, experiment == 'survival' &
+                        T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C')) %>%
   subset(mu > (mean(mu)-1*sd(mu))) %>%
@@
 # Create dataframe for fast growers filtering for 1 sd from the mean: -----
-df.fast <- subset(df, Experiment == 'fast growth') %>%
+df.fast <- subset(df, experiment == 'fast growth') %>%
   subset(mu > (mean(mu)-1*sd(mu))) %>%
@@
 #   sd from the mean:
-df.affinity <- subset(df, Experiment == 'affinity' &
-                        Temp.cutoff %in% c('low thermo greater than 50 C','mid thermo greater than 50 C')) %>%
+df.affinity <- subset(df, experiment == 'affinity' &
+                        T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C')) %>%
   subset(mu > (mean(mu)-1*sd(mu))) %>%
@@
 x.1 <- df.full %>%
-  subset(Experiment == 'survival') %>%
-  subset(select = c(OTU, mu, Experiment,horizon,
+  subset(experiment == 'survival') %>%
+  subset(select = c(OTU, mu, experiment,horizon,
                     fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, Experiment) %>%
+  dplyr::group_by(OTU, experiment) %>%
   dplyr::mutate(max.mu = max(abs(mu))) %>%
@@
 x.2 <- df.full %>%
-  subset(Experiment == 'fast growth') %>%
-  subset(select = c(OTU, mu, Experiment,horizon,
+  subset(experiment == 'fast growth') %>%
+  subset(select = c(OTU, mu, experiment,horizon,
                     fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, Experiment) %>%
+  dplyr::group_by(OTU, experiment) %>%
   dplyr::mutate(max.mu = max(abs(mu))) %>%
@@
 x.3 <- df.full %>%
-  subset(Experiment == 'affinity') %>%
-  subset(select = c(OTU, mu, Experiment,horizon,
+  subset(experiment == 'affinity') %>%
+  subset(select = c(OTU, mu, experiment,horizon,
                     fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, Experiment) %>%
+  dplyr::group_by(OTU, experiment) %>%
   dplyr::mutate(max.mu = max(abs(mu))) %>%
@@
        #color = expression("Degree ("*degree*C*") hours"), 
-       shape = 'Experiment') +
+       shape = 'experiment') +
   #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
@@
 
-unique(subset(df, select = c(Experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))
+unique(subset(df, select = c(experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))
 
@@
 df$horizon <- factor(df$horizon, levels = c('O','A'))
-df$Experiment <- factor(df$Experiment, levels = c('survival','fast growth','affinity'))
+df$experiment <- factor(df$experiment, levels = c('survival','fast growth','affinity'))
 
 for (i in 1:nrow(df)) {
-  if (abs(df$Estimate[i]) > 2) {
-    df$trimmed.Estimate[i] = df$Estimate[i]
+  if (abs(df$intercept[i]) > 2) {
+    df$trimmed.intercept[i] = df$intercept[i]
   } else {
-    df$trimmed.Estimate[i] = NA
+    df$trimmed.intercept[i] = NA
   }
@@
 p = ggplot(df) + 
-  geom_histogram(aes(Estimate),fill = 'red', binwidth=1) + 
-  #geom_histogram(aes(trimmed.Estimate), fill = 'blue', binwidth=1) + 
-  theme_bw() + 
-  facet_grid(Experiment+DNA.type~horizon, scales = 'free')
+  geom_histogram(aes(intercept),fill = 'red', binwidth=1) + 
+  #geom_histogram(aes(trimmed.intercept), fill = 'blue', binwidth=1) + 
+  theme_bw() + 
+  facet_grid(experiment+DNA.type~horizon, scales = 'free')
 
 length(unique(subset(df, Temp.cutoff == 'Low thermo greater than 50 C' &
-                       Experiment == 'survival')$OTU))
-
-p1 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
+                       experiment == 'survival')$OTU))
+
+p1 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
   geom_histogram() + 
@@
 
-p2 = ggplot(subset(df, Experiment == 'fast growth'), aes(Estimate)) +
+p2 = ggplot(subset(df, experiment == 'fast growth'), aes(intercept)) +
   geom_histogram() + 
@@
 
-p3 = ggplot(subset(df, Experiment == 'survival'), aes(Estimate)) +
+p3 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
   geom_histogram() + 
@@
 
-length(unique(subset(df, Estimate > 0 & Experiment == 'affinity')$OTU))
-length(unique(subset(df, Estimate < 0 & Experiment == 'affinity')$OTU))
-length(unique(subset(df, Estimate > 1 & Experiment == 'affinity')$OTU))
-length(unique(subset(df, Estimate < -1 & Experiment == 'affinity')$OTU))
-
-dim(subset(df, Experiment == 'fast growth' &
+length(unique(subset(df, intercept > 0 & experiment == 'affinity')$OTU))
+length(unique(subset(df, intercept < 0 & experiment == 'affinity')$OTU))
+length(unique(subset(df, intercept > 1 & experiment == 'affinity')$OTU))
+length(unique(subset(df, intercept < -1 & experiment == 'affinity')$OTU))
+
+dim(subset(df, experiment == 'fast growth' &
              horizon == 'O' &
@@
                      labels = c('Positive','No Response', 'Negative')) +
-  labs(title = 'Experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
+  labs(title = 'experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
        y = 'Relative abundance') + 
@@
     #                 labels = c('Positive','No Response', 'Negative')) +
-  labs(title = 'Experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
+  labs(title = 'experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
        y = 'Relative abundance',
@@
 p <- ggplot(data = subset(df, burn.trtmt == 'dry' & horizon == 'O'), 
-            aes(x=site, y = Abundance, Fill = Experiment)) + 
+            aes(x=site, y = Abundance, Fill = experiment)) + 
   theme_bw()+
@@
   geom_bar(stat = 'identity') +
-  facet_wrap(~Experiment, scale = 'free') + 
+  facet_wrap(~experiment, scale = 'free') + 
   #stat_smooth(method=lm,se = FALSE,color='black') +
@@
 
-df.PB.pos.rspd <- subset(df.full, Experiment == 'survival' & Estimate > 0) %>%
+df.PB.pos.rspd <- subset(df.full, experiment == 'survival' & Estimate > 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 
-df.PB.neg.rspd <- subset(df.full, Experiment == 'survival' & Estimate < 0) %>%
+df.PB.neg.rspd <- subset(df.full, experiment == 'survival' & Estimate < 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 
-df.SI.cntl.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
+df.SI.cntl.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
   subset(Comparison == 'pb.control.v.SI.control') %>%
@@
   unique()
-df.SI.cntl.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
+df.SI.cntl.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
   subset(Comparison == 'pb.control.v.SI.control') %>%
@@
 
-df.SI.pos.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate > 0) %>%
+df.SI.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 
-df.SI.neg.rspd <- subset(df.full, Experiment == 'fast growth' & Estimate < 0) %>%
+df.SI.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 # LIwA:
-df.LIwA <- subset(df.full, Experiment == 'affinity')
-
-df.LIwA.pos.rspd <- subset(df.full, Experiment == 'affinity' & Estimate > 0) %>%
+df.LIwA <- subset(df.full, experiment == 'affinity')
+
+df.LIwA.pos.rspd <- subset(df.full, experiment == 'affinity' & Estimate > 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 
-df.LIwA.neg.rspd <- subset(df.full, Experiment == 'affinity' & Estimate < 0) %>%
+df.LIwA.neg.rspd <- subset(df.full, experiment == 'affinity' & Estimate < 0) %>%
   subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
@@
 
-p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = Experiment)) + 
+p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = experiment)) + 
   geom_point(size=2) + 
   theme_bw() + 
-  facet_grid(horizon~Experiment) + 
+  facet_grid(horizon~experiment) + 
   geom_vline(xintercept = 0)

### 2023-02-06 OTU-trait-list.R

@@ -8,644 +8,897 @@ library(ggplot2)
 library(dplyr)
 library(phyloseq)
 library(tidyr)
+library(phyloseq)
 
-setwd('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data')
-# Experiment 1: -----
-#     Import data
-df.1.low <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/low-thermo-cutoff-50C.csv')
-df.1.mid <- read.csv('sequence-data/LibCombined/corncob-output/Ex1 Fire survival/Mid-thermo-cutoff.csv')
-
-df.1 <- rbind(df.1.low,df.1.mid)
-
-head(df.1)
-dim(df.1) # total of 951 responders
-length(unique(df.1$OTU)) # 388 unique OTU responders
-
-# Create dataframe with unique OTU identifies
-y <- data.frame(unique(df.1$OTU))
-colnames(y)[1] = 'OTU'
-y$Responder.in.n.analyses = 0
-y$Pos.count = 0
-y$Neg.count = 0
-
-# Calculate the number of times that each OTU was identified as a pos/neg fire responder
-for (i in 1:nrow(y)) {
-  for (j in 1:nrow(df.1)) {
-    if (df.1$OTU[j] == y$OTU[i]) {
-      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]+1
-    } else {
-      y$Responder.in.n.analyses[i] = y$Responder.in.n.analyses[i]
-    }
-  }
-}
-
-for (i in 1:nrow(y)) {
-  for(j in 1:nrow(df.1)) {
-    if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] > 0) {
-      y$Pos.count[i] = y$Pos.count[i] + 1
-    } else if (df.1$OTU[j] == y$OTU[i] & df.1$Estimate[j] < 0) {
-      y$Neg.count[i] = y$Neg.count[i] + 1
-    } else {
-      y$Pos.count[i] = y$Pos.count[i]
-      y$Neg.count[i] = y$Neg.count[i]
-    }
-  }
-}
-
-# Combine this data with the full corncob output:
-z <- merge(df.1, y)
-hist(z$Responder.in.n.analyses)
-
-Problem.OTUs <- subset(y, Pos.count > 0 & Neg.count > 0) 
-
-df.problem <- subset(df.1, OTU %in% Problem.OTUs$OTU) %>%
-  merge(Problem.OTUs)
[…]

### 2023-02-06 corncob-experiment1.R

@@ -23,65 +23,77 @@ ps.raw.full
 ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
 ps.norm.full
 
-
-ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
-ps.raw.full <- prune_taxa(taxa_sums(ps.raw.full)>0, ps.raw.full)
-
-# normalize abundance seq data
-ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
-                                sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
-                                sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
-                                sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
-                                sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
-ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
+# NOT RELEVANT TO 24 HR POST-BURN SAMPLES:
+# ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+#                                sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+#                                sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+#                                sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
[…]

### 2023-02-06 corncob-experiment2-pHclasses.R

@@ -10,7 +10,6 @@ library(phyloseq)
 library(magrittr)
 library(dplyr)
 
-
 #setwd("C:/Users/danab/Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/")
 
 ### CORNCOB TAKES RAW SEQ DATA AS INPUT ###
@@ -37,7 +36,7 @@ ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-0
                              sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
                             sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
 
-# Remove taxa with 0 abundance:
+# Remove taxa with 0 abundance and filter for only genomic DNA:
 ps.raw.prune <-  prune_samples(sample_data(ps.raw.full)$incub.trtmt %in% c('pb','SI') &
                                 sample_data(ps.raw.full)$DNA.type == 'gDNA', ps.raw.full) 
 ps.raw.prune <- prune_taxa(taxa_sums(ps.raw.prune)>0, ps.raw.prune) 
@@ -55,7 +54,7 @@ ps.norm.prune <- prune_taxa(taxa_sums(ps.norm.prune)>0, ps.norm.prune)
 #ps.raw.prune <- ps.raw.phylum
 
 
-### Step 4. Create sliding pH categories -----
+### Step 3. Create sliding pH categories -----
 
 df <- data.frame(sample_data(ps.raw.prune))
 
@@ -99,17 +98,45 @@ sample_names(ps.df) = df$Full.id
 sample_data(ps.raw.prune) <- ps.df
 
 
-### Step 4 XXX, dry burns ----
 
+
+### OPTIONAL. Set temperature cutoff for burns -----
+# # Focus on dry soil burns: 
+# ps.DNA.dry <-  prune_samples(sample_data(ps.raw.prune)$burn.trtmt != 'wet', ps.raw.prune)
+# 
+# # Create dataframe ps.DNA.dry sample_data.
+# df.dry <- data.frame(sample_data(ps.DNA.dry))
+# 
+# # Want to pull out pairs (dry burn and control) of cores in which the dry burn
+# #   core reached temps greater than some T cutoff. To do this, we need to assign
[…]

### 2023-02-06 corncob-experiment3.R

@@ -23,7 +23,7 @@ ps.raw.full
 ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
 ps.norm.full
 
-# Exclude all but 6 month incubation samples and emove taxa with 0 abundance:
+# Exclude all but 6 month incubation samples and remove taxa with 0 abundance:
 ps.raw.prune <-  prune_samples(sample_data(ps.raw.full)$incub.trtmt %in% c('LIwA') &
                                  sample_data(ps.raw.full)$DNA.type == 'gDNA', ps.raw.full) 
 ps.raw.prune <- prune_taxa(taxa_sums(ps.raw.prune)>0, ps.raw.prune) 
@@ -33,26 +33,27 @@ ps.norm.prune <-  prune_samples(sample_data(ps.norm.full)$incub.trtmt %in% c('LI
                                   sample_data(ps.norm.full)$DNA.type == 'gDNA', ps.norm.full) 
 ps.norm.prune <- prune_taxa(taxa_sums(ps.norm.prune)>0, ps.norm.prune)
 
-
 # Create phylum dataset:
 #ps.raw.phylum <- tax_glom(ps.raw.prune, taxrank = 'Phylum')
 #ps.raw.prune <- ps.raw.phylum
 
-### EXPERIMENT 1 -----
 
-# DRY BURNS -----
-#     Create Temp cutoff 
+
+
+
+### Step 2. Create temp categories -----
+
+# Subset dry burns
 ps.LIwA.dry <-  prune_samples(sample_data(ps.raw.prune)$burn.trtmt != 'wet', ps.raw.prune)
 
-#    Create dataframe from ps.LIwA.dry sample_data.
-df.dry <- data.frame(sample_data(ps.LIwA.dry))
-
-#    Create temperature categories:
-df.dry <- df.dry %>%
+# Want to pull out pairs (dry burn and control) of cores in which the dry burn
+#   core reached temps greater than some T cutoff. To do this, we need to assign
+#   a "max temp" of the core pair to both the dry burn and the control core. 
+df.dry <- data.frame(sample_data(ps.LIwA.dry)) %>%
   group_by(site) %>%
   mutate(Dry.burn.max = max(Thermo.mid.max)) 
 
-#     Now combine the new sample data with the original phyloseq object:
+# Now combine the new sample data with the original phyloseq object:
 ps.df <- sample_data(df.dry)
 
 sample_names(ps.df) = df.dry$Full.id
[…]

### 2023-03-16 Manuscript-figures.Rmd
Updating scripts used in manuscript

@@
 ```{r, include=FALSE}
-df.meta <- read.csv('../data/all-sample-metadata.csv')
+df.meta <- read.csv('../../data/all-sample-metadata.csv')
 
@@
 ### Normalized + tree
-ps.norm.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
+ps.norm.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
 ps.norm.full <- prune_taxa(taxa_sums(ps.norm.full)>0, ps.norm.full)
@@
 
-ps.raw.full <- readRDS('../data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
+ps.raw.full <- readRDS('../../data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
 
@@
 # Temperatures ----
-df.Temp <-read.csv('../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
+df.Temp <-read.csv('../../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
 df.Temp$Thermo_position <- factor(df.Temp$Thermo_position, levels = c('Mid','Low'))
@@
                           y = Temp)) + 
-  geom_point(aes(color = Thermo_position), size=1) +
+  geom_point(aes(color = burn.trtmt), size=1) +
   theme_bw()+
-  facet_grid(burn.trtmt~Thermo_position,scales = 'free_y', 
+  facet_wrap(~Thermo_position,scales = 'free_y', ncol=1,
              labeller = labeller(Thermo_position = ThermoLabels,
@@
   labs(x = "Time (h)",
-       y = expression(paste("Temperature ( ",degree ~ C, ")")),
-       color = "Soil depth") + 
-  scale_color_manual(values = c('black','grey40'),
-                     labels = c('O horizon/mineral \n interface','9 cm'),
-                     breaks = c('Mid','Low')) + 
-  theme(axis.title.x = element_text(size = 16),
-        axis.title.y = element_text(size = 16),
-        axis.text = element_text(size=16),
-        strip.text.y = element_text(size=16), 
-        strip.text.x = element_text(size=16), 
-        legend.text = element_text(size=16),
-        legend.title = element_text(size=16), 
-        legend.position = '',
-       strip.background = element_rect(colour="black", fill="grey92")) 
+       y = expression(paste("Thermocouple temperature ( ",degree ~ C, ")")),
+       color = "Burn treatment") + 
+  #scale_color_manual(values = c("black","grey70"),
+   #                  labels = c('O horizon/mineral \n interface','9 cm'),
+    #                 breaks = c('wet','dry')) + 
+  scale_color_manual(values = c('orange','red'),
+                     limits = c('wet','dry'),
+                     labels = c('Moist soil burn','Dry soil burn')) +
+  theme(axis.title.x = element_text(size = 14),
+        axis.title.y = element_text(size = 14),
+        axis.text = element_text(size=14),
+        strip.text.y = element_text(size=14), 
+        strip.text.x = element_text(size=14), 
+        legend.text = element_text(size=12),
+        legend.title = element_text(size=12), 
+        legend.position = 'right',
+       strip.background = element_rect(colour="black", fill="grey92")) +
+  geom_hline(yintercept=100)
 pTemp
@@
 pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = pH, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
+  geom_boxplot(aes(x=horizon, y = pH, fill = burn.trtmt), varwidth = FALSE) + 
     theme_bw()+
-  labs(x= 'Burn treatment',
+  labs(x= 'Soil horizon',
      #  y = 'Decay rate constant for fast C pool \nlog(k1)',
        y = 'Soil pH',
-       fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey40'),
-                     limits = c('O','A'),
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('O','A'),
                      labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
+  # scale_fill_manual(values = c("slateblue4","palegreen3"),
+  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
+  #                    limits = c('O','A'),
+  #                    labels = c('Organic','Mineral')) +
+  # scale_x_discrete(limits = c('control','wet','dry'),
+  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
   theme(axis.text.y = element_text(size = 14),
@@
 
-pChange_CN  <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = C.N.ratio, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
+pChange_CN  <- ggplot(subset(df.meta, incub.trtmt == 'SI' &site !=10)) + 
+  geom_boxplot(aes(x=horizon, y = C.N.ratio, fill = burn.trtmt), varwidth = FALSE) + 
+    theme_bw()+
+  labs(x= 'Soil horizon',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Soil C:N',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('O','A'),
+                     labels = c('Organic','Mineral')) +
+  #scale_fill_manual(values = c("deepskyblue3","saddlebrown"),
+  # scale_fill_manual(values = c("slateblue4","palegreen3"),
+  # #scale_fill_manual(values = c("darkgreen","saddlebrown"),
+  #                    limits = c('O','A'),
+  #                    labels = c('Organic','Mineral')) +
+  # scale_x_discrete(limits = c('control','wet','dry'),
+  #                    labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=12),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=12),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+cowplot::plot_grid(pChange_pH, pChange_CN, ncol=2)
+
+# Stats ----
+df.stats <- subset(df.meta, incub.trtmt == 'SI' )
+
+test = aov(C.N.ratio ~ burn.trtmt*horizon, subset(df.stats))
+summary(test)
+TukeyHSD(test)
+
+# Respiration coefficients ----
+#   Decay model coefficients at end of 5 week incubation (Days=34)
+#   after adjusting for total C
+df.coefs <- read.csv('../../data/2-pool-decay-model-output-SI-adjusted-for-total-C.csv') %>%
+  subset(t==34) 
+# df.coefs <- read.csv('../../data/2-pool-decay-model-output-LIwA-adjusted-for-total-C.csv') %>%
+#   subset(t==180)
+
+df.stack <- gather(df.coefs, 
+                   key = 'coefs', 
+                   value = value,M1,M2,k1,k2)
+
+df.stack$coefs <- factor(df.stack$coefs, levels = c('M1', 'M2', 'k1', 'k2'))
+
+pResp2 = ggplot(subset(df.stack, coefs %in% c('M1','M2')), aes(x=burn.trtmt)) + 
+  geom_boxplot(aes(y=value, fill=burn.trtmt),varwidth = FALSE)+
+  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
   theme_bw()+
@@
      #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Soil C:N',
-       fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey40'),
-                     limits = c('O','A'),
+       y = 'Fractional pool size',
+       fill = 'Burn treatment',
+       color = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet burn','dry burn'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('control','wet burn','dry burn'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  #scale_x_discrete(limits = c('O','A'), 
+  #                 labels = c('Organic','Mineral'))
+  facet_wrap(~coefs, ncol=1,scales = 'free_y',
+             labeller = labeller(coefs = CoefsLabel))+
+  theme(axis.text.y = element_text(size = 12),
+        legend.title = element_text(size=12),
+        axis.text.x = element_text(size = 12),
+        axis.title.x = element_text(size = 12, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=25, l=10)),
+        strip.text = element_text(size=12),
+        legend.text = element_text(size=12),
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical", 
+       legend.position = '',
+       strip.background = element_rect(colour="black", fill="grey92"))
+
+pResp1 = ggplot(subset(df.stack, coefs %in% c('k1','k2')), aes(x=burn.trtmt)) + 
+  geom_boxplot(aes(y=value, fill=burn.trtmt),varwidth = FALSE)+
+  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
+  theme_bw()+
+  labs(x= 'Burn treatment',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Decay rate',
+       fill = 'Burn treatment',
+       color = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet burn','dry burn'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('control','wet burn','dry burn'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  #scale_x_discrete(limits = c('O','A'), 
+  #                 labels = c('Organic','Mineral'))
+  facet_wrap(~coefs, ncol=1,scales = 'free_y',
+             labeller = labeller(coefs = CoefsLabel))+
+  theme(axis.text.y = element_text(size = 12),
+        legend.title = element_text(size=12),
+        axis.text.x = element_text(size = 12),
+        axis.title.x = element_text(size = 12, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=12),
+        legend.text = element_text(size=14),
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical", 
+       legend.position = '',
+       strip.background = element_rect(colour="black", fill="grey92"))
+
+cowplot::plot_grid(pResp2, pResp1, ncol=2)
+
+# Stats ----
+df.stats <- subset(df.meta, incub.trtmt != 'pb' & horizon == 'O')
+
+summary(subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic' &
+                 horizon == 'O' & burn.trtmt == 'wet')$k1)
+sd(subset(df.stats, incub.trtmt == 'LIwA' & burn.trtmt == 'wet')$k1)
+
+test = aov(k2 ~ burn.trtmt, subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic'))
+summary(test)
+TukeyHSD(test)
+
+test = wilcox.test(M1~burn.trtmt, data = subset(df.stats, incub.trtmt == 'SI' & burn.trtmt != 'control'))
+test
+
+test = aov(M1 ~ texture, data = subset(df.meta, incub.trtmt %in% c('LIwA','LIn') & horizon == 'O'))
+
+test
+
+p = ggplot(df.stats, aes(x=burn.trtmt, y =k1)) + 
+  geom_boxplot() + 
+  facet_grid(~incub.trtmt) +
+  theme_bw()
+
+```
+
+# Figure 3: RNA and DNA concentration (ng/g soil)
+```{r}
+df <- read.csv('../../data/raw-data/pb-RNA-and-DNA-conc.csv')
+
+colnames(df)[1] <- 'core.id.hor.incub'
+
+df.sub <- df.meta %>%
+  subset(incub.trtmt == 'pb') %>%
+  subset(select = c(core.id.hor.incub, DNA.type, horizon, burn.trtmt))
+
+df.DNA <- subset(df, DNA.type == 'gDNA') %>%
+  mutate(Conc.DNA = Concentration_ng.uL) %>%
+  subset(select = c('core.id.hor.incub', 'Conc.DNA'))
+df.RNA <- subset(df, DNA.type == 'cDNA') %>%
+  mutate(Conc.RNA = Concentration_ng.uL) %>%
+  subset(select = c('core.id.hor.incub', 'Conc.RNA'))
+
+df <- merge(df, df.sub)
+
+NaLabels = c('RNA','DNA')
+names(NaLabels) <- c('cDNA','gDNA')
+
+p1 = ggplot(df) + 
+  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
+  theme_bw()+
+  facet_wrap(~DNA.type, ncol=2, labeller = labeller(DNA.type = NaLabels))+
+  labs(x= 'Soil horizon',
+       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Concentration\n(ug/g soil)',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('O','A'),
                      labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  # scale_fill_manual(values = c("darkgreen","grey70"),
+  #                   limits = c('O','A'),
+  #                   labels = c('Organic','Mineral')) +
+  # scale_x_discrete(limits = c('control','wet','dry'),
+  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
   theme(axis.text.y = element_text(size = 14),
         legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
+        axis.text.x = element_text(size = 13),
         axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
@@
         legend.box = "vertical")
-
-cowplot::plot_grid(pChange_pH, pChange_CN, ncol=2)
-
-# Respiration coefficients ----
-df.coefs <- subset(df.meta, incub.trtmt == 'LIwA' &
-                     horizon == 'O' & texture != 'organic')
-
-df.stack <- gather(df.coefs, 
-                   key = 'coefs', 
-                   value = value,M1,M2,k1,k2)
-
-df.stack$coefs <- factor(df.stack$coefs, levels = c('M1', 'M2', 'k1', 'k2'))
-
-pResp2 = ggplot(subset(df.stack, coefs %in% c('M1','M2')), aes(x=burn.trtmt)) + 
-  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
-  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
+p1
+
+p_DNA = ggplot(subset(df, DNA.type == 'gDNA')) + 
+  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
   theme_bw()+
-  labs(x= 'Burn treatment',
+  labs(x= 'Soil horizon',
        #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Fractional pool size',
-       fill = 'Burn treatment',
-       color = 'Burn treatment') + 
-  scale_fill_manual(values = c('black','slategray3','tan3'),
+       y = 'DNA concentration\n(ug/g soil)',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
                      limits = c('control','wet','dry'),
-                     labels = c('control','wet soil','dry soil')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
-  #scale_x_discrete(limits = c('O','A'), 
-  #                 labels = c('Organic','Mineral'))
-  facet_wrap(~coefs, ncol=1,scales = 'free_y',
-             labeller = labeller(coefs = CoefsLabel))+
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=25, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical", 
-       legend.position = '',
-       strip.background = element_rect(colour="black", fill="grey92"))
-
-pResp1 = ggplot(subset(df.stack, coefs %in% c('k1','k2')), aes(x=burn.trtmt)) + 
-  geom_boxplot(aes(y=value), fill='grey70', alpha=0.7,varwidth = FALSE)+
-  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
-  theme_bw()+
-  labs(x= 'Burn treatment',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Decay rate',
-       fill = 'Burn treatment',
-       color = 'Burn treatment') + 
-  scale_fill_manual(values = c('black','slategray3','tan3'),
-                     limits = c('control','wet','dry'),
-                     labels = c('control','wet soil','dry soil')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
-  #scale_x_discrete(limits = c('O','A'), 
-  #                 labels = c('Organic','Mineral'))
-  facet_wrap(~coefs, ncol=1,scales = 'free_y',
-             labeller = labeller(coefs = CoefsLabel))+
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical", 
-       legend.position = '',
-       strip.background = element_rect(colour="black", fill="grey92"))
-
-cowplot::plot_grid(pResp2, pResp1, ncol=1)
-
-# Stats ----
-df.stats <- subset(df.meta, incub.trtmt != 'pb' & horizon == 'O')
-
-summary(subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic' &
-                 horizon == 'O' & burn.trtmt == 'wet')$k1)
-sd(subset(df.stats, incub.trtmt == 'LIwA' & burn.trtmt == 'wet')$k1)
-
-test = aov(k2 ~ burn.trtmt, subset(df.stats, incub.trtmt == 'LIwA' & texture != 'organic'))
-summary(test)
-TukeyHSD(test)
-
-test = wilcox.test(M1~burn.trtmt, data = subset(df.stats, incub.trtmt == 'SI' & burn.trtmt != 'control'))
-test
-
-test = aov(M1 ~ texture, data = subset(df.meta, incub.trtmt %in% c('LIwA','LIn') & horizon == 'O'))
-
-test
-
-p = ggplot(df.stats, aes(x=burn.trtmt, y =k1)) + 
-  geom_boxplot() + 
-  facet_grid(~incub.trtmt) +
-  theme_bw()
-
-```
-
-# Figure 3: RNA and DNA concentration (ng/g soil)
-```{r}
-df <- read.csv('../data/raw-data/pb-RNA-and-DNA-conc.csv')
-
-colnames(df)[1] <- 'core.id.hor.incub'
-
-df.sub <- df.meta %>%
-  subset(incub.trtmt == 'pb') %>%
-  subset(select = c(core.id.hor.incub, DNA.type, horizon, burn.trtmt))
-
-df.DNA <- subset(df, DNA.type == 'gDNA') %>%
-  mutate(Conc.DNA = Concentration_ng.uL) %>%
-  subset(select = c('core.id.hor.incub', 'Conc.DNA'))
-df.RNA <- subset(df, DNA.type == 'cDNA') %>%
-  mutate(Conc.RNA = Concentration_ng.uL) %>%
-  subset(select = c('core.id.hor.incub', 'Conc.RNA'))
-
-df <- merge(df, df.sub)
-
-NaLabels = c('RNA','DNA')
-names(NaLabels) <- c('cDNA','gDNA')
-
-p1 = ggplot(df) + 
-  geom_boxplot(aes(x=burn.trtmt, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = horizon),alpha = 0.7, varwidth = FALSE) + 
-  theme_bw()+
-  facet_wrap(~DNA.type, ncol=2, labeller = labeller(DNA.type = NaLabels))+
-  labs(x= 'Burn treatment',
-       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Concentration (ug/g soil)',
-       fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey40'),
-                    limits = c('O','A'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  scale_x_discrete(limits = c('O','A'),
                      labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                   labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  # scale_fill_manual(values = c("darkgreen","grey70"),
+  #                   limits = c('O','A'),
+  #                   labels = c('Organic','Mineral')) +
+  # scale_x_discrete(limits = c('control','wet','dry'),
+  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
   theme(axis.text.y = element_text(size = 14),
@@
         legend.text = element_text(size=14),
-        legend.position = 'right',
+        legend.position = '',
         # legend.background = element_rect(fill = "darkgray"),
         legend.box = "vertical")
-p1
-
-test <- aov(nucleic.acid.conc.in.soil.ng.per.g ~ burn.trtmt, data = subset(df, DNA.type == 'cDNA' & horizon == 'O' & burn.trtmt != 'wet'))
+
+p_RNA = ggplot(subset(df, DNA.type == 'cDNA')) + 
+  geom_boxplot(aes(x=horizon, y = nucleic.acid.conc.in.soil.ng.per.g/1000, fill = burn.trtmt),varwidth = FALSE) + 
+  theme_bw()+
+  labs(x= 'Soil horizon',
+       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'RNA concentration\n(ug/g soil)',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned control','Moist soil burn','Dry soil burn')) +
+  scale_x_discrete(limits = c('O','A'),
+                     labels = c('Organic','Mineral')) +
+  # scale_fill_manual(values = c("darkgreen","grey70"),
+  #                   limits = c('O','A'),
+  #                   labels = c('Organic','Mineral')) +
+  # scale_x_discrete(limits = c('control','wet','dry'),
+  #                  labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 13),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+        # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+cowplot::plot_grid(p_DNA, p_RNA, ncol=2)
+
+test <- aov(nucleic.acid.conc.in.soil.ng.per.g ~ burn.trtmt*horizon, data = subset(df, DNA.type == 'gDNA'))
 summary(test)
@@
   scale_x_discrete(limits = c('wet','dry'),
-                   labels = c('Wet soil \nburn','Dry soil \nburn')) +
+                   labels = c('Moist soil \nburn','Dry soil \nburn')) +
   theme(axis.title = element_text(size=18),
@@
 ```{r}
-df.WMCN.pb <- read.csv('../data/WtMeanCopyNum_pb_gDNA.csv')
-df.WMCN.SI <- read.csv('../data/WtMeanCopyNum_SI.csv')
-df.WMCN.LIwA <- read.csv('../data/WtMeanCopyNum_LIwA.csv')
+df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
+df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
+df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')
 
@@
   theme_bw() + 
-  scale_fill_manual(values = c('black','grey50'),
+  scale_fill_manual(values = c("darkgreen","grey70"),
                      labels = c('Organic','Mineral'),
@@
   scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
   labs(x='Burn treatment',
@@
 # Compare copy number of positive/negative responders: ----
-df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
-RDP <- read.csv('../data/All-OTUs-CopyNum.csv')
-
-df.fast <- subset(df.full, experiment == 'fast growth' &
+df.full.OTU <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+RDP <- read.csv('../../data/All-OTUs-CopyNum.csv')
+
+df.fast <- subset(df.full.OTU, experiment == 'fast growth' &
                         Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
@@
 ```{r, message = FALSE}
-df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')
+df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')
 
@@
        shape = 'Soil horizon') + 
-  scale_color_manual(values = c('black', 'grey40'),
+  scale_color_manual(values = c("darkgreen","grey70"),
                      limits = c('O','A'),
@@
 summary(test) 
+```
+
+# Responders as fraction of total reads
+```{r}
+df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+
+ps.responders <- prune_taxa(taxa_names(ps.norm.full) %in% df$OTU, ps.norm.full)
+
+df.melt <- psmelt(ps.responders)
+
+responders <- df.melt %>% group_by(Sample) %>% summarize(Abundance) 
+max(responders$Abundance)
+mean(responders$Abundance)
+
+dry <- subset(df.melt, burn.trtmt == 'dry') %>% subset(select = c(Sample, horizon, burn.trtmt, Abundance, incub.trtmt, Thermo.mid.max)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
+
+summary(dry)
+
+# Total gDNA reads in lab experiments: 39115
+# Total reads in lab experiments: 43450
+# Number responders = 117
+# max abundance in lab data = 60%
+# mean abundance, dry burns = 0.15% +/- 14%
+
+df.frac.of.total <- df.melt %>% subset(select = c(Sample, horizon, burn.trtmt, Veg.type, Abundance, DNA.type, incub.trtmt, Thermo.mid.max, site)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
+
+p_FractionTotal <- ggplot(subset(df.frac.of.total, DNA.type == 'cDNA'), aes(x=site, y=total.Abun, fill=burn.trtmt)) +
+  geom_bar(stat='identity',  position='dodge') + 
+  facet_wrap(~horizon+incub.trtmt, labeller = labeller(horizon = HorizonLabels)) + 
+  theme_bw()+
+  labs(x= 'Sampling site ID',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Fraction of total reads',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+df.frac.of.total$burn.trtmt <- factor(df.frac.of.total$burn.trtmt, levels = c('control','wet','dry'))
+
+p_FractionTotal <- ggplot(subset(df.frac.of.total,incub.trtmt!='LIn'), aes(x=horizon, y=total.Abun, fill=burn.trtmt)) +
+  geom_boxplot()+
+  facet_wrap(~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels, DNA.type = DNALabels)) + 
+  theme_bw()+
+  labs(x= 'Soil horizon',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Fraction of total reads',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+    scale_x_discrete(limits = c('O','A'),
+                     labels = c('Organic','Mineral')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+# Table summarize composition of responders by phylum:
+df.phylum <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Phylum)) %>% unique()
+
+df.phylum %>% mutate(Phylum = as.factor(Phylum)) %>% subset(mu.affinity.max>0) %>%subset(select = c(Phylum)) %>% View()
+
+df.Class <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Class)) %>% unique()
+
+df.Class %>% mutate(Class = as.factor(Class)) %>% subset(mu.fast.max>0) %>%subset(select = c(Class)) %>% summary()
+
+# Count number of taxa by sample:
+# Create a factor corresponding to the Genera
+genfac = factor(tax_table(ps.norm.cDNA)[, "Genus"])
+# Tabulate the counts for each genera in each sample
+gentab = apply(otu_table(ps.norm.cDNA), MARGIN = 2, function(x) {
+    tapply(x, INDEX = genfac, FUN = sum, na.rm = TRUE, simplify = TRUE)
+})
+head(gentab)[, 1:10]
+
+x <- as.data.frame(gentab)
+```
+
+# New figures: 
+```{r}
+### BC dissim of burned vs. unburned on the x axis with a respiration metric on the y axis
+
+# Import BC dissimilarity data
+df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')
+
+# Combine this with metadata
+df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))
+
+# Organize
+df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
+df.distances$horizon <- factor(df.distances$horizon, levels = c('O','A'))
+
+# Import respiration data:
+df.resp <- read.csv("../../data/fractional-c-remaining.csv")
+
+df.merge <- merge(df.distances, df.resp, by = c('core.id','incub.trtmt')) %>%
+  subset(incub.trtmt == 'SI') %>%
+  subset(DayFactor == 34) %>%
+  mutate(mass.C.respired = mass.C.remaining.g * (1-fractional.C.remaining))
+
+pBC = ggplot(df.merge, aes(x=BC.distance.btw.burned.and.control, y=k1, color = horizon)) + 
+  geom_point() + 
+  scale_color_manual(values = c('darkgreen','grey70'))+
+  stat_smooth(method=lm,se = FALSE,color='black') +
+  theme_bw() + 
+  #facet_wrap(~horizon, ncol=2,scales = 'fixed',
+   #          labeller = labeller(horizon = HorizonLabels))+
+  labs(y = 'Decay rate constant for \nfast C pool (k1)',
+       x = 'Bray-Curtis dissimilarity \ncompared to unburned control')
+
+summary(lm(data=df.merge,k1~BC.distance.btw.burned.and.control))
+
+### Ordination colored by respiration metric:
+# Full ordination
+ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt =='SI', ps.norm.full)
+ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
+
+ord.nmds = ordinate(ps.norm.SI,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)
+
+# quick look at results:
+plot_ordination(ps.norm.SI,ord.nmds,color="burn.trtmt",shape="incub.trtmt")
+colnames(sample_data(ps.norm))
+
+# Ordination plot with horizons and deg.hrs
+p1 = plot_ordination(ps.norm.SI, ord.nmds, axes = c(1,2), color = "",
+                      shape = 'burn.trtmt') + 
+  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
+  geom_point(size=3, alpha=0.8) +
+  # scale_color_gradientn(colours = c('gold2','red','red4','black')) +
+  # scale_color_manual(values = c('black','orange','red'),
+  #                    labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
+  #                    breaks = c('control','wet','dry'))+
+  scale_shape_manual(values = c('circle','square','triangle'),
+                     labels = c('Unburned control', 'Moist soil','Dry soil'),
+                     breaks = c('control','wet','dry')) +
+  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
+  #scale_shape_manual(values = c('circle','triangle'),
+   #                  labels = c('O horizon','Mineral'),
+    #                 breaks = c('O','A')) + 
+  theme(legend.text = element_text(size = 12),
+        axis.title = element_text(size=12),
+        axis.text = element_text(size=12),
+        legend.title = element_text(size=12)) + 
+  labs(shape = 'Burn treatment',
+       color = 'Fractional size\nof fast C pool') +
+  theme_bw()
+
+p1
+
+## What fraction of total reads in dry soil burns 24 hr post burn were bacillus?
+#  Bacillus fire surviving taxa = 8f0e2646c1389192d5a822f62bd295cf, 8adb5559e135233565acfea1287280bf
+df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+
+df.bac <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv') %>%
+  subset(mu.survival.max>0) %>%
+  subset(Genus=='Bacillus')
+
+ps.norm.bac <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb', ps.norm.gDNA) 
+ps.norm.bac <- prune_taxa(taxa_names(ps.norm.bac) %in% df.bac$OTU, ps.norm.bac)
+
+bac <- psmelt(ps.norm.bac)
+# Answer 9% (8f0e2646c1389192d5a822f62bd295cf) and 4% (8adb5559e135233565acfea1287280bf) of total reads in dry soil burns
+
+### What percentage of all OTUs were identified as fast growers?
+df.fast <- df %>%
+  subset(mu.fast.max>0)
+
+ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI', ps.norm.gDNA) 
+ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
+ps.norm.SI
+# Answer: IN the 5 week incubation, 0.4%
+
+### Max relative abundance of responding taxa in lab samples?
+ps.responders <- prune_taxa(taxa_names(ps.norm.gDNA) %in% df$OTU, ps.norm.gDNA)
+df.responders <- psmelt(ps.responders)
+
+df.responders <- df.responders %>%
+  subset(select = c(Sample, Abundance, Full.id,burn.trtmt))
+
+Num.responders <- df.responders %>% group_by(Full.id) %>% mutate(abun = sum(Abundance))
+max(Num.responders$abun) # = 0.604
+
+Num.responders.in.dry <- df.responders %>%
+  subset(burn.trtmt == 'dry') %>% 
+  group_by(Full.id) %>% 
+  mutate(combined.abun = sum(Abundance))
+
+mean(Num.responders.in.dry$combined.abun) # = 15
+sd(Num.responders.in.dry$combined.abun) # =
+
 ```
@@
 MyWunifrac_E3 <- distance(ps.E3, method = 'wunifrac')
+MyWunifrac_All <- distance(ps.norm.gDNA, method = 'wunifrac')
 
@@
 SamDat_E3 = data.frame(sample_data(ps.E3))
+SamDat_All = data.frame(sample_data(ps.norm.gDNA))
 
@@
                     percent.total.N+texture+burn.trtmt+horizon, data = SamDat_E3)
+test_All <- adonis(MyWunifrac_All ~ incub.trtmt+burn.trtmt+pH+horizon+Veg.type, data = SamDat_All)
+
 test_E1
@@
 test_E3
+test_All
 
@@
 
+# All
+adonis(MyWunifrac_All ~ Veg.type, data = SamDat_All)
+adonis(MyWunifrac_All ~ pH, data = SamDat_All)
+adonis(MyWunifrac_All ~ incub.trtmt, data = SamDat_All)
+adonis(MyWunifrac_All ~ burn.trtmt, data = SamDat_All)
+adonis(MyWunifrac_All ~ horizon, data = SamDat_All)
 ```
@@
 
+# SI: plot responders as fraction of total comm. vs. total C mineralized over 5 week incub.
+```{r}
+### Goal plot with fraction of total comm by trait category vs. total C-CO2 respired after 5 weeks
+
+# 1. import trait data
+df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+head(df)
+
+df$trait = 'TBD'
+
+# assign traits:
+for (i in 1:nrow(df)) {
+  if (is.na(df$mu.fast.max[i]) & is.na(df$mu.affinity.max[i])) {
+    df$trait[i] = 'Survivor' 
+  } else if (is.na(df$mu.survival.max[i]) & is.na(df$mu.affinity.max[i])) {
+    df$trait[i] = 'Fast grower' 
+  } else if (is.na(df$mu.survival.max[i]) & is.na(df$mu.fast.max[i])) {
+    df$trait[i] = 'Affinity taxa' 
+  } else if (is.na(df$mu.survival.max[i])) {
+    df$trait[i] = 'Fast grower and affinity taxa'
+  } else if (is.na(df$mu.affinity.max[i])) {
+    df$trait[i] = 'Survivor and fast grower'
+  } else if (is.na(df$mu.fast.max[i])) {
+    df$trait[i] = 'Survivor and affinity taxa' 
+  } else {
+    df$trait[i] = 'ALL'
+  }
+}
+
+# 2. import full comm data at end of SI incubation
+ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI', ps.norm.full)
+
+# 3. Assign traits to OTUs in the SI comm data
+ps.norm.SI <- prune_taxa(taxa_names(ps.norm.SI) %in% df$OTU, ps.norm.SI)
+ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
+
+df.norm.SI <- psmelt(ps.norm.SI)
+
+df.norm.SI <- merge(df.norm.SI, subset(df, select = c(OTU, trait)))
+
+p = ggplot(df.norm.SI, aes(x=burn.trtmt, y=Abundance)) + 
+  geom_bar(aes(fill=trait), stat='identity', position='stack')
+
+# 4. Import respiration data
+#df.resp <- read.csv("../../data/fractional-c-remaining.csv")
+# df.resp <- df (imported from "incubations_microbial_respiration_TLWcheck.R")
+
+# 5. sum total respiration at end of 5 weeks
+df.resp.SI <- subset(df.resp, Incubation.trtmt == 'SI')
+
+# 6. merge trait and respiration dataframes
+df.sum <- df.norm.SI %>%
+  group_by(Full.id, trait) %>%
+  mutate(trait.abun = sum(Abundance)) %>%
+  subset(select = c(core.id,trait,trait.abun)) %>%
+  unique() %>%
+  merge(df.resp.SI, by = 'core.id')
+
+# 7. plot fraction of total comm vs. total C-CO2 respired
+p = ggplot(subset(df.sum, Day==34), aes(x=trait.abun, y = C.CO2.absorbed.per.g.C)) + 
+  geom_point(aes(color=trait)) + 
+  facet_wrap(~burn.trtmt)+
+  theme_bw()
+
+p = ggplot(df.sum, aes(x=(1-fractional.C.remaining),y=trait.abun)) + 
+  geom_bar(aes(fill=trait), stat='identity', position='stack') + 
+  theme_bw()
+
+# Initial mineralization after 2-7 days
+
+```
+
 # figuring out corncob + trait assignments

### 2023-03-16 OTU-trait-list.R

@@ -23,7 +23,7 @@ colnames(df.exp1)[7] <- 'experiment'
 
 
 # Experiment 2
-df.exp2 <- read.csv('data/sequence-data/LibCombined/corncob-output/Manuscript/Ex2_signOTUs_3sliding_pH_categories_byBurnTrtmt.csv')
+df.exp2 <- read.csv('data/sequence-data/LibCombined/corncob-output/Manuscript/Ex2_signOTUs_MidThermoCutoff_50C.csv') # DvD, WvW, CvC
 
 # Experiment 3
 df.exp3 <- read.csv('data/sequence-data/LibCombined/corncob-output/Manuscript/Ex3_signOTUs_MidThermoCutoff_50C.csv')
@@ -43,7 +43,7 @@ df.exp2 <- df.exp2 %>%
          mu.cntl.pH = NA)
 
 df.raw.combined <- rbind(df.exp13,df.exp2)
-write.csv(df.raw.combined, 'data/sequence-data/LibCombined/corncob-output/Manuscript/All-responders.csv')
+#write.csv(df.raw.combined, 'data/sequence-data/LibCombined/corncob-output/Manuscript/All-responders.csv')
 
 
 
@@ -90,23 +90,25 @@ df.ratio <- merge(df.DNA.prune, df.RNA.prune, by = c('OTU','core.id.hor.incub'))
 df.survivors <- merge(df.exp1, df.ratio, by = "OTU") %>%
   # Pull out positive responders
   subset(mu.burn.trtmt > 0) %>%
-  #subset(mu.burn.trtmt > mean(mu.burn.trtmt)-1*sd(mu.burn.trtmt)) %>%
   # Remove taxa with an RNA:DNA ratio before [cutoff]
-  subset(max.RNA.DNA.ratio > 0) %>%
+  subset(max.RNA.DNA.ratio > 1) %>%
   # Calculate max mu for each OTU
-  group_by(OTU, horizon) %>%
+  group_by(OTU) %>%
   mutate(mu.survival.max = max(mu.burn.trtmt),
          mu.fast.max = NA,
          mu.affinity.max = NA) %>%
-  subset(select = c(OTU, comparison, experiment, horizon,
-                    Domain, Phylum, Class, Order, Family, Genus, Species, 
-                    mu.survival.max, mu.fast.max, mu.affinity.max,max.RNA.DNA.ratio)) %>% 
[…]

### 2023-03-16 corncob-experiment2-TempCutoff.R

@@ -48,37 +48,59 @@ ps.norm.prune <- prune_taxa(taxa_sums(ps.norm.prune)>0, ps.norm.prune)
 
 
 # Create phylum dataset:
-#ps.raw.phylum <- tax_glom(ps.raw.full, taxrank = 'Phylum')
-#ps.raw.phylum
+#ps.raw.phylum <- tax_glom(ps.raw.prune, taxrank = 'Phylum')
+#ps.raw.prune <- ps.raw.phylum
 
 
-# EXPERIMENT 2 - pb Dry vs. 5-week dry -----
+### Step 2: Create phyloseq objects with Temp cutoff for three comparison -----
 
+## PB DRY vs. 5-WEEK DRY: ##
+# Subset phyloseq object
 ps.DvD <- ps.raw.prune %>%
   phyloseq::subset_samples(burn.trtmt %in% c('dry')) 
 
-# Set burn temp cutoff:
-df.dry <- data.frame(sample_data(ps.DvD))
-
-df.dry <- df.dry %>%
+# Create burn temp cutoff:
+df.dry <- data.frame(sample_data(ps.DvD)) %>%
   group_by(site) %>%
-  mutate(Dry.burn.max = max(Thermo.low.max)) 
+  mutate(Dry.burn.max = max(Thermo.mid.max)) 
 
+# Recombine sample data with phyloseq object
 ps.df <- sample_data(df.dry)
 
+# Fix phyloseq names
 sample_names(ps.df) = df.dry$Full.id
-
 sample_data(ps.DvD) <- ps.df
 
 
-# 1.1. Set up corncob O horizon, dry burn, Max temp > 50 -----
+
+## PB WET vs. 5-WEEK WET ##
+# Subset phyloseq object
+ps.WvW <- ps.raw.prune %>%
+  phyloseq::subset_samples(burn.trtmt %in% c('wet')) 
+
+# Create burn temp cutoff:
+df.wet <- data.frame(sample_data(ps.WvW)) %>%
+  group_by(site) %>%
+  mutate(Wet.burn.max = max(Thermo.mid.max)) 
+
+# Recombine sample data with phyloseq object
+ps.df <- sample_data(df.wet)
+
+# Fix phyloseq names
+sample_names(ps.df) = df.wet$Full.id
+sample_data(ps.WvW) <- ps.df
+
+
+
+### Step 3:  Set up and run corncob analyzes -----
[…]

### 2023-03-16 decay-model-two-pool.R

@@ -63,6 +63,7 @@ coefs.df <- data.frame("core.id.incub" = "sample", "k1" = 0, "k2" = 0, "M1" = 0,
 output.fit.df <- data.frame("core.id" = "sample", 
                             "core.id.incub" = "sample", 
                             'r.squared' = 0,
+                            'pvalue' = 0,
                             "site" = 0,
                             "burn.trtmt" = "trtmt",
                             "t" = 0, 
@@ -101,6 +102,8 @@ for (i in seq_along(names.vec)) {
   
   df.lm <- lm(Mt ~ Mt.fit, data = df.x)
   df.x$r.squared <- summary(df.lm)$r.squared
+  df.x$pvalue <- summary(df.lm)$coef[2,4]
+  
 
   ## summary information on parameter estimates
   coefs <- summary(TwoPool.nls.fit) 
@@ -108,6 +111,7 @@ for (i in seq_along(names.vec)) {
   k2 <- coefs$coefficients[[2]]
   M1 <- coefs$coefficients[[3]]
   M2 <- df.x$Mt[1] - M1
+  pvalue <- df.x$pvalue
   
   coefs.df <- coefs.df %>%
     add_row("core.id.incub" = names.vec[[i]], "k1" = k1, "k2" = k2, "M1" = M1, "M2" = M2)
@@ -151,9 +155,10 @@ names.vec = as.vector(names.vec$core.id.incub)
 # Create an output df to populate with coefficients later
 coefs.df <- data.frame("core.id.incub" = "sample", "k1" = 0, "k2" = 0, "M1" = 0, "M2" = 0)
 
-output.fit.df <- data.frame("core.id" = "sample",
-                            "core.id.incub" = "sample",
-                            "r.squared" = 0,
+output.fit.df <- data.frame("core.id" = "sample", 
+                            "core.id.incub" = "sample", 
+                            'r.squared' = 0,
+                            'pvalue' = 0,
                             "site" = 0,
                             "burn.trtmt" = "trtmt",
                             "t" = 0, 
@@ -182,6 +187,8 @@ for (i in seq_along(names.vec)) {
   
   df.lm <- lm(Mt ~ Mt.fit, data = df.x)
   df.x$r.squared <- summary(df.lm)$r.squared
+  df.x$pvalue <- summary(df.lm)$coef[2,4]
+  
   
   ## summary information on parameter estimates
   coefs <- summary(TwoPool.nls.fit) 
[…]

### 2023-03-16 compile_thermocouple_data_all_burns.R
Remove unneeded scripts

@@ -1,54 +1,0 @@
-# --------------------
-# 
-# Title: compile_thermocouple_data_all_burns
-# Author: Dana Johnson
-# Date: 2020-Feb-03
-#
-# Purpose: This is code to compile all thermocouple data from simulated burns at FPL
-# into a single data file "Temp-all-burns"
-#
-# --------------------
-
-setwd("C:/Users/danab/Box Sync/WhitmanLab/Projects/WoodBuffalo/FireSim2019/data/FireSim2019_Temp/")
-
-# Import packages
-# library(dplyr)
-# library(ggplot2)
-
-# library(plyr)
-# library(readr)
-
-library(tidyverse)
-library(stringr)
-
-## Import all .csv files from location (mydir) 
-myfiles = list.files(pattern="*.csv", full.names=TRUE)
-
-
-# Combine all the raw temp .csv files into one (df) and add column with site ID
-df <- myfiles %>%
-  setNames(nm = .) %>%
-  map_df(~read_csv(.x,col_types = cols(), col_names = FALSE), .id = "File_name")
-
-# Rename colums
-col.names <- c('Site_ID','time_s','Thermo_mid','Thermo_low')
-names(df) <- col.names
-
-class(df$time_s)
-
-# Removing rows in column time_s 
-df <- subset(df, time_s != 'time_s')
-
-df$time_s = as.numeric(df$time_s)
-
-# Use only first couple hours of burn time
-df <- subset(df, time_s < 18000)
-
-# Get rid of lower temperatures
-df <- subset(df, Thermo_mid >20 | Thermo_low >20)
-
-# export new .csv file with compiled temp data
-write.csv(df,"C:/Users/danab/Box Sync/WhitmanLab/Projects/WoodBuffalo/WB2019/data/FireSim2019_Temp\\Temp-all-burns.csv")
-
-
-

### 2023-03-16 corncob-experiment2-pHclasses.R
Remove unnecessary corncob scripts

@@ -1,1188 +1,0 @@
-# --------------------
-# Title: FireSim2019 Experiment 2: sliding pH categories x 3
-# Author: Dana Johnson
-# Date: 2021-Oct-13
-#
-# set-up -----
-
-library(corncob)
-library(phyloseq)
-library(magrittr)
-library(dplyr)
-
-#setwd("C:/Users/danab/Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019/")
-
-### CORNCOB TAKES RAW SEQ DATA AS INPUT ###
-
-### Step 1. Import relevant phyloseq data ----
-# Raw seqs
-ps.raw.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.raw.full')
-ps.raw.full
-
-ps.norm.full <- readRDS('data/sequence-data/LibCombined/phyloseq-objects/ps.norm.full')
-ps.norm.full
-
-# Remove duplicate samples:
-ps.raw.full <- prune_samples(sample_data(ps.raw.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
-                               sample_data(ps.raw.full)$Full.id != '19UW-WB-08-10-O-SI', ps.raw.full)
-
-
-ps.norm.full <- prune_samples(sample_data(ps.norm.full)$Full.id != '19UW-WB-06-08-A-SI-duplicate' &
-                               sample_data(ps.norm.full)$Full.id != '19UW-WB-07-02-O-SI-duplicate' &
-                              sample_data(ps.norm.full)$Full.id != '19UW-WB-11-03-O-SI-duplicate'&
-                             sample_data(ps.norm.full)$Full.id != '19UW-WB-19-07-A-SI-duplicate' &
-                            sample_data(ps.norm.full)$Full.id != '19UW-WB-08-10-O-SI', ps.norm.full)
-
-# Remove taxa with 0 abundance and filter for only genomic DNA:
-ps.raw.prune <-  prune_samples(sample_data(ps.raw.full)$incub.trtmt %in% c('pb','SI') &
[…]

### 2023-03-16 decay-model-two-pool.R
Adding code for analyzing respiration data

@@ -312,106 +312,3 @@ df.rsquared <- df.rsquared %>%
   separate(core.id.incub, c("Year", "Project", "Site", "Core", "incub.trtmt"), sep = "-", remove = FALSE) 
 
 #write.csv(df.rsquared,'../data/2-pool-decay-model-output.csv')
-setwd('../Box/WhitmanLab/Projects/WoodBuffalo/FireSim2019')
-
-df.rsquared <- read.csv('data/2-pool-decay-model-output.csv')
-
-df.coefs <- df.rsquared %>%
-  subset(t == 3) %>%
-  subset(select = c(core.id,incub.trtmt,r.squared,Burn.trtmt,
-                    k1,k2,M1,M2))
-df.fit <- df.rsquared %>%
-  subset(select = c(core.id.incub,Site,Core,incub.trtmt,r.squared,
-                    Burn.trtmt,Mt,Mt.fit))
-  
-# Look at the coefficient dataframe
-hist(df.rsquared$k1,breaks=20)
-hist(df.rsquared$k2,breaks=20)
-hist(df.rsquared$M1,breaks=20)
-hist(df.rsquared$M2,breaks=20)
-
-# Separate incubation treatments
-liwa.inc <- subset(df.rsquared, incub.trtmt == "LIwA")
-lin.inc <- subset(df.rsquared, incub.trtmt == "LIn")
-st.inc <- subset(df.rsquared, incub.trtmt == "SI")
-
-
-#PLOT: Fractional C remaining at one site (13).
-colnames(df.rsquared)
-head(df.rsquared)
-
-
-
-p = ggplot(df.site, aes(x = t, y = Mt, 
-                     color = Burn.trtmt,
-                     shape = incub.trtmt)) + 
-  geom_point() +
-  geom_line(aes(x=t, y = Mt.fit)) +
-  facet_wrap(~Site) +
-  labs(x = "Day", 
-       y = "C remaining as fraction of initial total C",
-       title = "Fractional C remaining during short-term incubation treatments")
-p
-
-
-
-palette = c("black","orange","red3")
-#PLOT: Fractional C remaining during short-term incubation treatments across all sites
-p = ggplot(st.inc, aes(x = t, y = Mt, 
-                       color = Burn.trtmt)) + 
-  geom_point() +
-  scale_color_manual(values = palette,
-                     limits = c('control','wet burn','dry burn'),
[…]

### 2023-03-16 README.rmd
Update README file

@@
 
-corncob-experiment2-pHclasses.R: tests for differentially abundant OTUs in unburned/burned soils after a 24 hr vs. 5 week incubation using corncob
+corncob-experiment2-TempCutoff.R: tests for differentially abundant OTUs in unburned/burned soils after a 24 hr vs. 5 week incubation using corncob
 
@@
 
+creating_burn_temp_profiles.R: plot the temperature profiles during simulated burns.
+
 decay-model-two-pool.R: Fits two pool decay model to CO2 respiration data
+
+incubations_microbial_respiration.R: calculate C remaining during laboratory incubations as a fraction of initial total C
 
@@
 
+Merged_paper_figures_Revision_Github.R: Combine lab and field OTU datasets to run ordinations and quantify relative abundance of laboratory-identified trait taxa in field data
+
 OTU-trait-list.R - compiles list of OTUs identified as differentially enriched from each experiment
 
+Qiime-pipeline-for-FireSim2019-LibCombined.ipynb: steps for sequence processing and taxonomic assignments
+
 rrndb-SI.R: Assigns mean predicted 16S copy numbers to OTUs based on taxonomy

### 2023-03-16 Manuscript-figures.Rmd

@@
 
-#library(knitr)
 library(ggplot2)
-#library(plyr)
 library(dplyr)
 library(tidyr)
-#library(car) # For Levene's Test
 library(phyloseq)
-#library(scatterplot3d)
-#library(ggtree)
-library(cowplot) # add-on to ggplot to assist in publication-quality figs
-#library(qwraps2)
+library(cowplot) 
 library(vegan)
 library(tidyverse)
-#library(psych) # scatterplot matrix (pairs, or pairs.panels)
-library(ggtern) # for ternary plots
-#library(devtools)
-#library(DivNet)
-#library(breakaway) # for richness estimates
 
@@
 ```{r, message = FALSE}
-#df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
-#df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
-#df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
-#df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')
-
 # Starting phyloseq:
@@
 
-#ps.raw.pb <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb', ps.raw.full)
-#ps.norm.pb <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb', ps.norm.full)
-
-# ps.norm.pb
-#ps.norm.pb.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb',ps.norm.gDNA)
-#ps.norm.pb.cDNA <- prune_samples(sample_data(ps.norm.cDNA)$incub.trtmt == 'pb',ps.norm.cDNA)
-# ps.norm.SI
-#ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI',ps.norm.gDNA)
-# ps.norm.LIwA
-#ps.norm.LIwA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIwA',ps.norm.gDNA)
-#ps.norm.LIn <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIn',ps.norm.gDNA)
-#ps.norm.LI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.norm.gDNA)
-#ps.raw.LI <- prune_samples(sample_data(ps.raw.gDNA)$incub.trtmt %in% c('LIn', 'LIwA'),ps.raw.gDNA)
-
-#ps.norm.SI<- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
 ```
 
-# Figure 2 (burn temperature, pH and C:N change, respiration coefficients):
+# Figure 2A-C (burn temperature, pH and C:N change, respiration coefficients):
 ```{r}
-# Temperatures ----
+# Temperature, Fig. 2A ----
 df.Temp <-read.csv('../../data/burn-thermocouple-temp-logs/Temp-all-burns-clean.csv')
@@
 
-# pH and C:N change ----
+# pH and C:N change, Fig. 2B ----
 pChange_pH <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
@@
 
-# Respiration coefficients ----
+# Respiration coefficients, Fig. 2C ----
 #   Decay model coefficients at end of 5 week incubation (Days=34)
@@
 
-# Figure 3: RNA and DNA concentration (ng/g soil)
+# Figure 2D: RNA and DNA concentration (ng/g soil)
 ```{r}
@@
 
-Bray-Curtis dissimilarity?
-```{r, message = FALSE}
-# This is a possibly convoluted piece of code to first create a Bray-Curtis
-#     dissimilarity matrix and then pull out the dissimilarities between dry/wet
-#     burns and corresponding control cores.
-
-# First: Calculate Bray-curtis dissimilarity matrix ----
-ps.cDNA.raw <- prune_samples(sample_data(ps.raw.full)$DNA.type == 'cDNA', ps.raw.full)
-ps.cDNA.raw <- prune_taxa(taxa_sums(ps.cDNA.raw) > 0, ps.cDNA.raw)
-
-dist.bray.full <- as.matrix(distance(ps.raw.full, method = 'bray', type = 'samples'))
-
-# Look at some figures
-hist(dist.bray.full)
-heatmap(dist.bray.full)
-
-# Convert distance matrix into dataframe
-df <- data.frame(dist.bray.full)
-
-# Bring in meta data and subset for specific analysis
-df.meta.sub <- subset(df.meta, select = c(Full.id, burn.trtmt,site, DNA.type,
-                                          incub.trtmt,core, horizon,
-                                          pH, change.pH))
-
-# Create a dataframe with the colnames and Full.ID
-x <- data.frame(str_split(colnames(df)[1:460], 'X', simplify = TRUE)[,2])
-
-# Rename columes:
-colnames(x)[1] <- 'ID.bray'
-
-# Clean up x. 
-x <- x %>%
-  mutate(Full.id = ID.bray)
-
-x$Full.id <- str_replace_all(x$Full.id, "\\.", "-")
-
-x$X <- 'X'
-
-x <- x %>%
-  unite(Bray.ID, c('X',"ID.bray"), sep = '', remove = TRUE)
-
-# Next, pull out the control cores from the meta data and assign them to "Control.id"
-df.meta.control <- df.meta %>%
-  subset(burn.trtmt == 'control') %>%
-  mutate(Control.id = Full.id) %>%
-  subset(select = c(Control.id, site, horizon, incub.trtmt, DNA.type))
-
-# Combine list of control cores with full df.meta
-df.meta.list <- merge(subset(df.meta.sub, select = c(Full.id, site, horizon, 
-                                                     DNA.type,burn.trtmt, incub.trtmt, 
-                                                     pH, change.pH)), 
-                      df.meta.control, by = c('site', 'horizon', 'incub.trtmt', 'DNA.type'))
-
-# ANd then combine the Full.id list with the control core meta data I just created.
-#     df.list now contains Full.id with the corresponding control sample for each 
-#     dry/wet burn and a colume ("Bray.ID") that has the sample ID formatted to 
-#     match the distance matrix names.
-df.list <- x %>%
-  merge(df.meta.list, by = 'Full.id') %>%
-  subset(burn.trtmt != 'control')
-
-df.list$burn.trtmt <- as.character(df.list$burn.trtmt)
-df.list$horizon <- as.character(df.list$horizon)
-df.list$incub.trtmt <- as.character(df.list$incub.trtmt)
-
-# Create and empty data frame to store distances
-df.distances <- data.frame("Full.id" = df.list$Full.id, 
-                           'control.core' = 'core',
-                           #'burn.trtmt' = 'burn', 'horizon' = 'H',
-                           #'DNA.type' = 'DNA.type',
-                           'BC.distance.btw.burned.and.control' = 'distance'
-                           #'incub.trtmt' = 'incub', 'pH' = 0
-                           ) %>%
-  unique()
-
-# Now run a convoluted loop:
-for (i in 1:nrow(df.list)) { # For each sample (row in df.list)
-  for (j in 1:nrow(df)) { # For each row in the dissimilarity matrix
-    for (k in 1:ncol(df)){ # And for each colume in the dissimilarity matrix
-      if(colnames(df)[k] == df.list$Bray.ID[i] &  # If the distance matrix colume ID matches the sample ID in the list
-         rownames(df)[j] == df.list$Control.id[i]) { # And the rowname ID matches the corresponding control core, then...
-        df.distances$BC.distance.btw.burned.and.control[i] = df[j,k] # Pull out the distance and store it in new dataframe
-        #df.distances$burn.trtmt[i] = df.list$burn.trtmt[i]
-        df.distances$control.core[i] = df.list$Control.id[i]
-        #df.distances$horizon[i] = df.list$horizon[i]
-        #df.distances$incub.trtmt[i] = df.list$incub.trtmt[i]
-        #df.distances$DNA.type[i] = df.list$DNA.type[i]
-        #df.distances$pH[i] = df.list$pH[i]
-        #df.distances$change.pH[i] = df.list$change.pH[i]
-      }
-    } 
-  } 
-}
-
-df.distances$BC.distance.btw.burned.and.control <- as.numeric(df.distances$BC.distance.btw.burned.and.control)
-
-# Save backup dataframe.
-df.final <- df.distances
-
-# -----
-df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')
-
-df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))                            
-dim(df.distances)
-
-# Plots ----
-p=ggplot(subset(df.distances, DNA.type == 'cDNA')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.burned.and.control, fill = horizon),
-               alpha = 0.7) +
-  theme_bw() +
-  facet_wrap(~incub.trtmt, ncol=4,
-             labeller = labeller(incub.trtmt = IncubLabels)) + 
-  labs(x='Burn treatment',
-       y = 'Bray-Curtis dissimilarity \ncompared to control', 
+# Lab and field ordination, Figure 3 -----
+See "Merged_paper_figures_Revision_Github.R" script
+
+# Trait abundance in field data, Figure 4: ----
+See "Merged_paper_figures_Revision_GitHub.R" script
+
+# Rel abundance adjusted by copy num, Figure 5 -----
+See "Merged_paper_figures_Revision_GitHub.R" script
+
+# Total trait abun by BC dissimilarity, Figure 6 -----
+See "Merged_paper_figures_Revision_GitHub.R" script
+
+# Supplementary
+```{r}
+# Carbon and nitrogen loss, Figure S2 -----
+pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
+  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
+    theme_bw()+
+  labs(x= 'Burn treatment',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Total C (%)',
        fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey40'),
+  scale_fill_manual(values = c('black','grey90'),
                      limits = c('O','A'),
                      labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('wet','dry'),
-                   labels = c('Moist soil \nburn','Dry soil \nburn')) +
-  theme(axis.title = element_text(size=18),
-        axis.text = element_text(size=18),
-        legend.title = element_text(size=18),
-        legend.text = element_text(size=18),
-        strip.text = element_text(size=18)) + 
-  ylim(0,1)
-
-test <- aov(BC.distance.btw.burned.and.control~burn.trtmt*horizon, data = subset(df.distances, DNA.type == 'cDNA'))
+  scale_x_discrete(limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+pChange_N <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
+  geom_boxplot(aes(x=burn.trtmt, y = percent.total.N, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
+    theme_bw()+
+  labs(x= 'Burn treatment',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Total N (%)',
+       fill = 'Soil horizon') + 
+  scale_fill_manual(values = c('black','grey90'),
+                     limits = c('O','A'),
+                     labels = c('Organic','Mineral')) +
+  scale_x_discrete(limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+cowplot::plot_grid(pChange_C, pChange_N, ncol=2)
+
+test <- aov(percent.total.N ~ burn.trtmt, data = subset(df.meta, incub.trtmt == 'SI' & horizon == 'O'))
 summary(test)
@@
 
-```
-
-Richness estimates?
-
-If the community composition data of a single sample includes few singletons, we assume that sequencing captured most of the taxa present in the sample.
-If the data includes many singletons, we assume that sequencing missed many rare taxa.
-We can use breakaway to estiamte how many taxa were missed and use this to estimate richness.
-```{r}
-
-# Load data and calculate richness ----
-df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
-df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
-df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
-df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')
-
-head(df.pb.cDNA.OTU)
-
-df.counts.pb.cDNA <- df.pb.cDNA.OTU %>%
-  group_by(Full.id) %>%
-  mutate(counts = length(unique(OTU))) %>%
-  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
-  unique()
-
-df.counts.pb.gDNA <- df.pb.gDNA.OTU %>%
-  group_by(Full.id) %>%
-  mutate(counts = length(unique(OTU))) %>%
-  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
-  unique()
-
-df.counts.SI <- df.SI.OTU %>%
-  group_by(Full.id) %>%
-  mutate(counts = length(unique(OTU))) %>%
-  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
-  unique()
-
-df.counts.LI <- df.LI.norm %>%
-  group_by(Full.id) %>%
-  mutate(counts = length(unique(OTU))) %>%
-  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
-  unique()
-
-df.counts <- rbind(df.counts.pb.cDNA, df.counts.pb.gDNA,
-                   df.counts.SI, df.counts.LI)
-
-df.counts$burn.trtmt <-  factor(df.counts$burn.trtmt, levels = c('control','wet','dry'))
-df.counts$horizon <-  factor(df.counts$horizon, levels = c('O', 'A'))
-
-df.counts.pb <- subset(df.counts, incub.trtmt == 'pb')
-
-# Plots ----
-p = ggplot(df.counts.pb, aes(x=burn.trtmt, y=counts)) +
-  geom_boxplot(aes(fill = burn.trtmt), alpha = 0.7) + 
-  geom_point(color = 'black', alpha = 0.4) + 
-  theme_bw() + 
-  facet_grid(horizon~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels,
-                                                               horizon = HorizonLabels, 
-                                                               DNA.type = DNALabels)) + 
-  labs(y = 'unique non-zero OTU count')
-
-test <- aov(counts ~ burn.trtmt, data = subset(df.counts.pb.gDNA, horizon =='O'))
-summary(test)
-TukeyHSD(test)
-
-# Plot richness using "plot_richness" function in phyloseq: ----
-ps <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb',
-                    ps.raw.full)
-
-sample_data(ps)$burn.trtmt <- factor(sample_data(ps)$burn.trtmt, levels = c('control','wet','dry'))
-sample_data(ps)$horizon <- factor(sample_data(ps)$horizon, levels = c('O','A'))
-
-p = plot_richness(ps, x = "burn.trtmt", measures = 'Shannon') +
-  theme_bw() + 
-  geom_boxplot(aes(fill = horizon), alpha = 0.6) + 
-  facet_grid(horizon~DNA.type+incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels,
+# C remaining as fraction of total, Figure S3, S4 -----
+#   See incubations_microbial_respiration.R
+# Full ordination, Fig. S6 ----
+ps.full.dataset <-readRDS('../../../CombinedFireSim1519/ps.1519FireSim.merged')
+tree <- ape::read.tree('../../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')
+
+tree <- phy_tree(tree)
+tax <- tax_table(ps.full.dataset)
+otu <- otu_table(ps.full.dataset)
+sam <- sample_data(ps.full.dataset)
+
+ps.full.dataset = phyloseq::phyloseq(otu,tax, sam,tree)
+ps.full.dataset
+
+# Setting some plot parameters
+year.labs = c("One year post-fire","Five years post-fire")
+names(year.labs) = c(1,5)
+horizon.labs = c("Mineral","Organic")
+
+# Playing with new datasets
+ps = ps.full.dataset
+
+# Add column with pairs info
+sample_data(ps)$Pairs = paste(sample_data(ps)$Site_ID,sample_data(ps)$Org_or_Min,sep="_")
+head(sample_data(ps)$Pairs)
+
+# Normalize sample counts
+ps.norm = transform_sample_counts(ps,function(x) x/sum(x))
+sample_data(ps.norm)$Study = sample_data(ps.norm)$Years_Since_Fire
+sample_data(ps.norm)$Study[is.na(sample_data(ps.norm)$Study)]="Lab"
+
+ord.nmds = ordinate(ps.norm,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)
+
+plot_ordination(ps.norm,ord.pcoa,color="burn.trtmt",shape="incub.trtmt")
+plot_ordination(ps.norm,ord.nmds,color="pH",shape="Study")
+# Neat, they all fall out on top of each other. That's nice.
+colnames(sample_data(ps.norm))
+
+ps.norm.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('pb','SI','LIwA'), ps.norm.gDNA)
+ps.norm.gDNA <- prune_taxa(taxa_sums(ps.norm.gDNA)>0,ps.norm.gDNA)
+
+MyNMDS.full.gDNA <- ordinate(ps.norm.gDNA, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)
+
+# Ordination plot with horizons and deg.hrs
+p1 = plot_ordination(ps.norm.gDNA, MyNMDS.full.gDNA, axes = c(1,2), 
+                      color = "burn.trtmt",
+                      shape = 'incub.trtmt') + 
+  facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels,
                                                    DNA.type = DNALabels,
-                                                      horizon = HorizonLabels))
-```
-
-RNA:DNA ratios?
-```{r}
-df.norm.ratios <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/RNA_DNA_norm_ratios.csv')
-# RNA:DNA ratios were calculated by (RNA rel. abundance)/(DNA rel. abundance)
-#     In instances of DNA rel. abundance = 0, I set DNA abundance = 0.0000038, which
-#     is equal to the lowest measured rel. abundance of DNA across the dataset.
-#     In instances of RNA re. abundance = 0, I set ratio = 0.
-
-df.norm.ratios$horizon <- factor(df.norm.ratios$horizon, levels = c('O','A'))
-df.norm.ratios$burn.trtmt <- factor(df.norm.ratios$burn.trtmt, levels = c('control','wet','dry'))
-
-# Plot 
-p = ggplot(data = subset(df.norm.ratios, DNA.abundance > 0.001), aes(x=burn.trtmt, y = RNA.DNA.ratio, fill = horizon)) + 
-  geom_boxplot()+ 
-  #stat_smooth(method=lm,se = FALSE,color='black') +
-  #facet_wrap(~horizon, ncol=1,scale = 'free')+
-  theme_bw() + 
-  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')
-
-# What fraction of total reads for each sample fall below 0.001 relative abundance threshold? -----
-df.DNA.tally <- df.norm.ratios %>%
-  subset(RNA.abundance + DNA.abundance > 0) %>%
-  #subset(DNA.abundance > 0) %>%
-  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
-  mutate(counts = length(OTU)) %>%
-  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
-  tally(DNA.abundance > 0.001) %>%
-  #mutate(DNA.fraction.above.cutoff = n/counts)
-  mutate(non.zero.DNA.fraction = n/counts)
-head(df.DNA.tally)
-
-df.RNA.tally <- df.norm.ratios %>%
-  subset(RNA.abundance + DNA.abundance > 0) %>%
-  #subset(RNA.abundance > 0) %>%
-  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
-  mutate(counts = length(OTU)) %>%
-  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
-  tally(RNA.abundance > 0.001)%>%
-  mutate(non.zero.RNA.fraction = n/counts)
-  #mutate(RNA.fraction.above.cutoff = n/counts)
-head(df.RNA.tally)
-
-df.DNA.tally$burn.trtmt <- factor(df.DNA.tally$burn.trtmt, levels = c('control','wet','dry'))
-df.RNA.tally$burn.trtmt <- factor(df.RNA.tally$burn.trtmt, levels = c('control','wet','dry'))
-
-p = ggplot(df.DNA.tally, aes(x=burn.trtmt, y =DNA.fraction.above.cutoff, fill = horizon)) + 
-  geom_boxplot() + theme_bw()
-
-test <- aov(DNA.fraction.above.cutoff ~ burn.trtmt*horizon, data = df.DNA.tally)
-summary(test)
-TukeyHSD(test)
-
-test <- aov(non.zero.RNA.fraction ~ burn.trtmt*horizon, data = df.RNA.tally)
-summary(test)
-TukeyHSD(test)
-
-# Re-calculate ratio including only taxa present in both burned and unburned cores: ----
-df.burned <- subset(df.norm.ratios, burn.trtmt == 'dry') %>%
-  subset(DNA.abundance > 0) %>%
-  mutate(burned.DNA.abundance = DNA.abundance) %>%
-  subset(select = c(site, horizon, OTU, burned.DNA.abundance))
-
-df.control <- subset(df.norm.ratios, burn.trtmt == 'control') %>%
-  subset(DNA.abundance > 0) %>%
-  mutate(unburned.DNA.abundance = DNA.abundance) %>%
-  subset(select = c(site, horizon, OTU, unburned.DNA.abundance))
-
-df.shared.OTUs <- merge(df.burned, df.control)
-
-df.common.taxa <- subset(df.norm.ratios, burn.trtmt != 'wet') %>%
-  merge(df.shared.OTUs) %>%
-  mutate(ratio = RNA.abundance/DNA.abundance) %>%
-  group_by(core.id.hor.incub) %>%
-  mutate(mean.ratio = mean(ratio))
-
-df.counts <- df.common.taxa %>%
-  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
-  tally(DNA.abundance > 0)
-
-dim(df.common.taxa)
-
-# Plot 
-p = ggplot(data = df.common.taxa, aes(x=burn.trtmt, y = ratio, fill = horizon)) + 
-  geom_boxplot()+ 
-  #stat_smooth(method=lm,se = FALSE,color='black') +
-  #facet_wrap(~horizon, ncol=1,scale = 'free')+
-  theme_bw() + 
-  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')
-
-test <- aov(ratio ~ burn.trtmt*horizon, data = df.common.taxa)
-summary(test)
-TukeyHSD(test)
-
-# Recalculating ratios using raw reads: -----
-ps.raw.gDNA <- prune_samples(sample_data(ps.raw.pb)$DNA.type == 'gDNA', ps.raw.pb)
-ps.raw.gDNA
-ps.raw.gDNA <- prune_taxa(taxa_sums(ps.raw.gDNA)>0, ps.raw.gDNA)
-ps.raw.gDNA
-
-ps.raw.cDNA <- prune_taxa(taxa_sums(ps.raw.cDNA)>0, ps.raw.cDNA)
-
-df.raw.pb.cDNA <- psmelt(ps.raw.cDNA)
-df.raw.pb.gDNA <- psmelt(ps.raw.gDNA)
-
-df.RNA <- df.raw.pb.cDNA %>%
-  mutate(RNA.abundance = Abundance) %>%
-  subset(select = c(core.id.hor.incub, OTU, RNA.abundance))
-
-df.DNA <- df.raw.pb.gDNA %>%
-  mutate(DNA.abundance = Abundance) %>%
-  subset(select = c(core.id.hor.incub, OTU, DNA.abundance, horizon, site, pH, hrzn.degree.hrs,burn.trtmt))
-
-rownames(df.RNA) <- NULL
-rownames(df.DNA) <- NULL
-
-df.merge <- merge(df.RNA, df.DNA, by = c("core.id.hor.incub", "OTU"), all = TRUE)
-
-df.pb <- df.merge %>%
-  group_by(site, OTU) %>%
-  mutate(min = min(DNA.abundance)) %>%
-  subset(min > 0)
-
-df.pb[is.na(df.pb$RNA.abundance),3] <- 0
-
-df.pb <- df.pb %>%
-  mutate(ratio = RNA.abundance/DNA.abundance)
-
-# Plot
-df.pb$burn.trtmt <- factor(df.pb$burn.trtmt, levels = c('control','wet','dry'))
-
-p = ggplot(data = subset(df.pb,horizon =='O'), aes(x=burn.trtmt, y = (ratio), color = burn.trtmt)) + 
-  geom_boxplot()+ 
-  #stat_smooth(method=lm,se = FALSE,color='black') +
-  facet_wrap(~horizon, ncol=1,scale = 'free')+
-  theme_bw() + 
-  labs(title = 'RNA:DNA \nonly taxa present across all trtmts')
-
-test <- aov((ratio) ~ burn.trtmt, data = subset(df.pb, horizon == 'O'))
-summary(test)
-TukeyHSD(test)
-
-# Alternative calculations for RNA:DNA ratios: ----
-
-### Set ratio = 100 if DNA rel. abundance = 0 (Bowsher et al. 2019)
-for (i in 1:nrow(df.norm.ratios)) {
-  if(df.norm.ratios$DNA.abundance[i] == 0) {
-    df.norm.ratios$RNA.DNA.ratio[i] = 100
-  } else {
-    df.norm.ratios$RNA.DNA.ratio[i] = df.norm.ratios$RNA.DNA.ratio[i]
-  }
-}
-
-### If DNA abundance = 0, change it to 1.  (Bowsher et al. 2019)
-#     But this would only work for raw count data.
-for (i in 1:nrow(df.norm.ratios)) {
-  if(df.norm.ratios$DNA.abundance[i] == 0) {
-    df.norm.ratios$DNA.abundance[i] = 0.000038
-  } else {
-    df.norm.ratios$DNA.abundance[i] = df.norm.ratios$DNA.abundance[i]
-  }
-}
-df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance
-
-### Add 1 to all DNA and RNA abundances (Bowsher et al. 2019)
-df.norm.ratios$DNA.abundance = df.norm.ratios$DNA.abundance + 0.000038
-
-#df.norm.ratios$RNA.abundance = df.norm.ratios$RNA.abundance + 0.000038
-
-df.norm.ratios <- subset(df.norm.ratios, DNA.abundance > 0.0001 || RNA.abundance >0.0001 )
-
-df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance
-```
-
-# Figure 4 - weighted mean gene copy number
-Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
-```{r}
-df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
-df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
-df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')
-
-df.WMCN.SI <- subset(df.WMCN.SI, core.id != '19UW-WB-11-02' & 
-                    Full.id != '19UW-WB-06-08-A-SI-duplicate' &
-                    Full.id != '19UW-WB-07-02-O-SI-duplicate' &
-                    Full.id != '19UW-WB-11-03-O-SI-duplicate'&
-                    Full.id != '19UW-WB-19-07-A-SI-duplicate' &
-                    Full.id != '19UW-WB-08-10-O-SI' )
-
-summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
-sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
-summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)
-sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)
-
-test = aov(WtMeanCopyNum~ burn.trtmt*horizon, data = df.WMCN.SI)
-summary(test)
-TukeyHSD(test)
-
-df.WMCN <- rbind(df.WMCN.SI, df.WMCN.LIwA, df.WMCN.pb)
-
-df.WMCN <- df.WMCN %>%
-  unite(core.id.hor, c(core.id, horizon), sep = '-', remove=FALSE)
-
-df.WMCN <- merge(df.WMCN, df.meta)
-
-# CHeck for normality:
-p.QQ = qqplot(df.WMCN$hrzn.degree.hrs, df.WMCN$WtMeanCopyNum)
-
-# Plot ----
-df.WMCN$burn.trtmt <- factor(df.WMCN$burn.trtmt, levels = c('control','wet','dry'))
-df.WMCN$horizon <- factor(df.WMCN$horizon, levels = c('O','A'))
-df.WMCN$incub.trtmt <- factor(df.WMCN$incub.trtmt, levels = c('pb','SI','LIwA'))
-
-p1 = ggplot(data = subset(df.WMCN, incub.trtmt != 'LIwA')) + 
-  geom_boxplot(aes(x=burn.trtmt, y=WtMeanCopyNum, fill=horizon),alpha=0.7)+
-  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels))+
-  theme_bw() + 
-  scale_fill_manual(values = c("darkgreen","grey70"),
-                     labels = c('Organic','Mineral'),
-                     limits = c('O','A'))+
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
-  labs(x='Burn treatment',
-       y='Weighted mean predicted \n16S rRNA gene copy number',
-       fill = 'Soil horizon') +
-  theme(axis.text.y = element_text(size = 12),
-        axis.text.x = element_text(size = 12),
-        legend.text = element_text(size = 14),
-        legend.title = element_text(size = 14),
-        strip.text = element_text(size=14),
-        legend.position = 'right',
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10))) +
-  ylim(1,NA)
-
-# Stats
-df.WMCN.O <- subset(df.WMCN, horizon == 'O')
-df.WMCN.A <- subset(df.WMCN, horizon == 'A')
-
-fit.df.WMCN.O <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.O)
-fit.df.WMCN.A <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.A)
-
-summary(fit.df.WMCN.O)
-# p = 2*10^-16, R^2 adj = 0.6081
-summary(fit.df.WMCN.A)
-# p = 2*10^-16, R^2 adj = 0.7883
-
-# Weighted mean copy number STATS:
-test <- aov(WtMeanCopyNum ~ burn.trtmt*horizon, data = subset(df.WMCN, incub.trtmt == 'SI'))
-summary(test)
-TukeyHSD(test)
-
-test.sum <- df.WMCN %>%
-  group_by(burn.trtmt, horizon) %>%
-  summarize(mean.WMCN = mean(WtMeanCopyNum))
-
-# Calculate WMCN change from pb to SI: ----
-df.WMCN.initial <- subset(df.WMCN, incub.trtmt == 'pb') %>%
-  mutate(WMCN.pb = WtMeanCopyNum) %>%
-  subset(select = c(core.id, horizon, burn.trtmt, WMCN.pb))
-
-df.WMCN.SI <- df.WMCN.SI %>%
-  merge(df.WMCN.initial, all = TRUE) %>%
-  mutate(change.WMCN = WtMeanCopyNum - WMCN.pb)
-
-df.WMCN.SI$burn.trtmt <- factor(df.WMCN.SI$burn.trtmt, levels = c('control','wet','dry'))
-
-p = ggplot(df.WMCN.SI, aes(x=burn.trtmt, y = change.WMCN, fill = horizon)) + 
-  geom_boxplot() + 
-  geom_hline(yintercept = 0)+
-  theme_bw() + 
-  labs(x = 'Comparison between samples 24 h and 5 wk post-burn',
-       y = 'Change in predicted wt. mean gene copy number')
-
-test <- aov(change.WMCN ~ burn.trtmt*horizon, data = df.WMCN.SI)
-summary(test)
-TukeyHSD(test)
-
-# Compare copy number of positive/negative responders: ----
-df.full.OTU <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
-RDP <- read.csv('../../data/All-OTUs-CopyNum.csv')
-
-df.fast <- subset(df.full.OTU, experiment == 'fast growth' &
-                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
-  mutate(fast.est = Estimate)%>%
-  dplyr::group_by(OTU) %>%
-  dplyr::mutate(max.Estimate = max(Estimate)) %>%
-  subset(Estimate == max.Estimate) %>%
-  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
-                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
-                    Species, DNA.type, fast.est)) %>%
-  unique()
-
-ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI', ps.norm.full)
-ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
-
-df.not.responders <- data.frame(taxa_names(ps.norm.SI))
-
-df.not.responders <- subset(df.not.responders, !(taxa_names.ps.norm.SI. %in% df.responders$OTU))
-
-df.not.responders$Responders = 'no'
-df.responders <- subset(df.fast, select = c(OTU)) %>%
-  mutate(Responders = 'yes')
-colnames(df.not.responders)[1] = 'OTU'
-
-df.responders <- rbind(df.responders, df.not.responders) %>%
-  merge(RDP)
-
-p = ggplot(df.responders, aes(x=Responders, y = CopyNum)) + 
-  geom_boxplot() + 
+                                                   incub.trtmt = IncubLabels))+
+  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
+  geom_point(size=3, alpha=0.8) +
+  #geom_line(aes(group = core.id.hor)) +
+  labs(color = 'Burn treatment',
+       #color = expression("Degree ("*degree*C*") hours"), 
+       shape = 'experiment') +
+  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
+  scale_color_manual(values = c('black','orange','red'),
+                     labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
+                     breaks = c('control','wet','dry'))+
+  scale_shape_manual(values = c('circle','square','triangle'),
+                     labels = c('Fire survival', 'Fast growth','Post-fire envir. affinity'),
+                     breaks = c('pb','SI','LIwA')) +
+  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
+  #scale_shape_manual(values = c('circle','triangle'),
+   #                  labels = c('O horizon','Mineral'),
+    #                 breaks = c('O','A')) + 
+  theme(legend.text = element_text(face = 'italic',size = 16),
+        axis.title = element_text(size=16),
+        axis.text = element_text(size=16),
+        legend.title = element_text(size=16)) + 
   theme_bw()
 
-df.SI.responders <- df.full.OTU %>%
-  subset(experiment == 'fast growth') %>%
-  merge(RDP)
-
-dim(df.SI.responders)
-
-df.SI.positive = subset(df.SI.responders, Estimate > 0 ) %>%
-  group_by(OTU) %>%
-  mutate(Estimate = max(Estimate)) %>%
-  mutate(Response = 'positive') %>%
-  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
-                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
-  unique()
-
-df.SI.negative = subset(df.SI.responders, Estimate < 0 ) %>%
-  group_by(OTU) %>%
-  mutate(Estimate = min(Estimate)) %>%
-  mutate(Response = 'negative') %>%
-  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
-                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
-  unique()
-
-df.SI.responders <- rbind(df.SI.positive, df.SI.negative)
-
-p = ggplot(df.SI.responders, aes(x=Estimate, y = Class, color = Phylum)) + 
-  geom_point() + 
-  theme_bw() + 
-  facet_wrap(~Comparison) +
-  geom_vline(xintercept = 0)
-
-df.SI.dry.responders <- subset(df.SI.responders, Comparison == 'pb.dry.v.SI.dry') %>%
-  subset(!(OTU %in% subset(df.SI.responders, Comparison %in% c('pb.wet.v.SI.wet', 'pb.control.v.SI.control')))) %>%
-  subset(select = c(OTU, CopyNum, Response, horizon,Estimate)) %>%
-  unique()
-
-p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Response, y = CopyNum, fill = horizon)) + 
-  geom_boxplot() + 
-  theme_bw() + 
-  facet_wrap(~horizon)
-
-test = aov(CopyNum ~ Response+horizon, data = df.SI.dry.responders)
-summary(test)
-TukeyHSD(test)
-
-p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Estimate, y = CopyNum)) + 
-  geom_point()+
-  facet_grid(Response~horizon) + 
-  stat_smooth(method=lm,se = FALSE,color='black') +
-  theme_bw() 
-```
-
-# Figure 5 - Calculate bray-curtis dissimilarity for autoclaving
-```{r, message = FALSE}
+p1
+
+# BC dissimilarity and pH change, Figure S7-----
 df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')
@@
 
-test = lm(BC.distance.btw.burned.and.control~change.pH, data=subset(df.distances, incub.trtmt == 'LIwA' & horizon == 'A' & burn.trtmt == 'dry'))
-
-test
-summary(test)
-
-# Hrzn.degree.hrs vs. Bray-Curtis dissimilarities for -pb RNA and DNA -----
-p = ggplot(subset(df.meta.combined, burn.trtmt =='dry' & 
-                    incub.trtmt == 'pb'),
-           aes(x=hrzn.degree.hrs, y = BC.distance.btw.burned.and.control,fill = horizon)) +
-  geom_point(shape='circle filled',
-             stroke=1,
-             alpha = 0.8,
-             size=3) +
-  theme_bw() +
-  facet_grid(DNA.type~horizon, scales = 'free',
-             labeller = labeller(incub.trtmt = IncubLabels,
-                                 burn.trtmt = BurnLabels, 
-                                 DNA.type = DNALabels)) + 
-  labs(y = 'Bray-Curtis dissimilarity compared to control', 
-       title = 'Bray-Curtis dissimilarities') + 
-  scale_fill_manual(values = c('black','grey70'),
-                     limits = c('O','A'),
-                     labels = c('Organic','Mineral')) +
-  theme(axis.title = element_text(size=12),
-        axis.text = element_text(size=12),
-        legend.title = element_text(size=12),
-        legend.text = element_text(size=12)) + 
-    stat_smooth(method=lm,se = FALSE,color='black')
-
-# Stats -----
-test <- aov(BC.distance.btw.burned.and.control ~ hrzn.degree.hrs, 
-            data = subset(df.meta.combined,incub.trtmt == 'pb' & DNA.type == 'cDNA' &burn.trtmt == 'wet'))
-summary(test) 
-```
-
-# Responders as fraction of total reads
-```{r}
+# Respiration rate figures, S8, S9, S10-----
+#   See "incubations_microbial_respiration.R" script
+
+# Traits as fraction of total reads in lab data, Figure S11-----
 df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
@@
 
-# Table summarize composition of responders by phylum:
-df.phylum <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Phylum)) %>% unique()
-
-df.phylum %>% mutate(Phylum = as.factor(Phylum)) %>% subset(mu.affinity.max>0) %>%subset(select = c(Phylum)) %>% View()
-
-df.Class <- subset(df, select = c(mu.survival.max, mu.fast.max, mu.affinity.max, Class)) %>% unique()
-
-df.Class %>% mutate(Class = as.factor(Class)) %>% subset(mu.fast.max>0) %>%subset(select = c(Class)) %>% summary()
-
-# Count number of taxa by sample:
-# Create a factor corresponding to the Genera
-genfac = factor(tax_table(ps.norm.cDNA)[, "Genus"])
-# Tabulate the counts for each genera in each sample
-gentab = apply(otu_table(ps.norm.cDNA), MARGIN = 2, function(x) {
-    tapply(x, INDEX = genfac, FUN = sum, na.rm = TRUE, simplify = TRUE)
-})
-head(gentab)[, 1:10]
-
-x <- as.data.frame(gentab)
 ```
 
-# New figures: 
-```{r}
-### BC dissim of burned vs. unburned on the x axis with a respiration metric on the y axis
-
-# Import BC dissimilarity data
-df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')
-
-# Combine this with metadata
-df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))
-
-# Organize
-df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
-df.distances$horizon <- factor(df.distances$horizon, levels = c('O','A'))
-
-# Import respiration data:
-df.resp <- read.csv("../../data/fractional-c-remaining.csv")
-
-df.merge <- merge(df.distances, df.resp, by = c('core.id','incub.trtmt')) %>%
-  subset(incub.trtmt == 'SI') %>%
-  subset(DayFactor == 34) %>%
-  mutate(mass.C.respired = mass.C.remaining.g * (1-fractional.C.remaining))
-
-pBC = ggplot(df.merge, aes(x=BC.distance.btw.burned.and.control, y=k1, color = horizon)) + 
-  geom_point() + 
-  scale_color_manual(values = c('darkgreen','grey70'))+
-  stat_smooth(method=lm,se = FALSE,color='black') +
-  theme_bw() + 
-  #facet_wrap(~horizon, ncol=2,scales = 'fixed',
-   #          labeller = labeller(horizon = HorizonLabels))+
-  labs(y = 'Decay rate constant for \nfast C pool (k1)',
-       x = 'Bray-Curtis dissimilarity \ncompared to unburned control')
-
-summary(lm(data=df.merge,k1~BC.distance.btw.burned.and.control))
-
-### Ordination colored by respiration metric:
-# Full ordination
-ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt =='SI', ps.norm.full)
-ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
-
-ord.nmds = ordinate(ps.norm.SI,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)
-
-# quick look at results:
-plot_ordination(ps.norm.SI,ord.nmds,color="burn.trtmt",shape="incub.trtmt")
-colnames(sample_data(ps.norm))
-
-# Ordination plot with horizons and deg.hrs
-p1 = plot_ordination(ps.norm.SI, ord.nmds, axes = c(1,2), color = "",
-                      shape = 'burn.trtmt') + 
-  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
-  geom_point(size=3, alpha=0.8) +
-  # scale_color_gradientn(colours = c('gold2','red','red4','black')) +
-  # scale_color_manual(values = c('black','orange','red'),
-  #                    labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
-  #                    breaks = c('control','wet','dry'))+
-  scale_shape_manual(values = c('circle','square','triangle'),
-                     labels = c('Unburned control', 'Moist soil','Dry soil'),
-                     breaks = c('control','wet','dry')) +
-  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
-  #scale_shape_manual(values = c('circle','triangle'),
-   #                  labels = c('O horizon','Mineral'),
-    #                 breaks = c('O','A')) + 
-  theme(legend.text = element_text(size = 12),
-        axis.title = element_text(size=12),
-        axis.text = element_text(size=12),
-        legend.title = element_text(size=12)) + 
-  labs(shape = 'Burn treatment',
-       color = 'Fractional size\nof fast C pool') +
-  theme_bw()
-
-p1
-
-## What fraction of total reads in dry soil burns 24 hr post burn were bacillus?
-#  Bacillus fire surviving taxa = 8f0e2646c1389192d5a822f62bd295cf, 8adb5559e135233565acfea1287280bf
-df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
-
-df.bac <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv') %>%
-  subset(mu.survival.max>0) %>%
-  subset(Genus=='Bacillus')
-
-ps.norm.bac <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'pb', ps.norm.gDNA) 
-ps.norm.bac <- prune_taxa(taxa_names(ps.norm.bac) %in% df.bac$OTU, ps.norm.bac)
-
-bac <- psmelt(ps.norm.bac)
-# Answer 9% (8f0e2646c1389192d5a822f62bd295cf) and 4% (8adb5559e135233565acfea1287280bf) of total reads in dry soil burns
-
-### What percentage of all OTUs were identified as fast growers?
-df.fast <- df %>%
-  subset(mu.fast.max>0)
-
-ps.norm.SI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'SI', ps.norm.gDNA) 
-ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
-ps.norm.SI
-# Answer: IN the 5 week incubation, 0.4%
-
-### Max relative abundance of responding taxa in lab samples?
-ps.responders <- prune_taxa(taxa_names(ps.norm.gDNA) %in% df$OTU, ps.norm.gDNA)
-df.responders <- psmelt(ps.responders)
-
-df.responders <- df.responders %>%
-  subset(select = c(Sample, Abundance, Full.id,burn.trtmt))
-
-Num.responders <- df.responders %>% group_by(Full.id) %>% mutate(abun = sum(Abundance))
-max(Num.responders$abun) # = 0.604
-
-Num.responders.in.dry <- df.responders %>%
-  subset(burn.trtmt == 'dry') %>% 
-  group_by(Full.id) %>% 
-  mutate(combined.abun = sum(Abundance))
-
-mean(Num.responders.in.dry$combined.abun) # = 15
-sd(Num.responders.in.dry$combined.abun) # =
-
-```
-
-# Figure 6: Trade offs
-```{r}
-
-df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/all-responders.csv')
-df.L2FC <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Full_L2FC.csv')
-
-# Checking to make sure that L2FC calculations didn't drop any OTUs. 
-df.survival <- df %>%
-  subset(experiment == 'survival'&
-           T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C') & 
-           intercept > 0) %>%
-  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
-  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
-  unique()
-
-df.survival.L2FC <- df.L2FC %>%
-  subset(experiment == 'survival'  &
-           T.cutoff %in% c('low thermo > 50C','Mid thermo > 50C') &
-           mu > 0) %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  subset(select = c(OTU)) %>%
-  unique()
-
-df.survival.merge <- merge(df.survival, df.survival.L2FC)
-#write.csv(df.survival,'../tables/survivors.csv', row.names=FALSE)
-
-dim(df.survival)
-dim(df.survival.L2FC)
-
-df.fast <- df %>%
-  subset(experiment == 'fast growth'&
-           intercept > 0) %>%
-  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
-  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
-  unique()
-dim(df.fast)
-
-df.fast.L2FC  <- df.L2FC %>%
-  subset(experiment == 'fast growth'  &
-           mu > 0) %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  subset(select = c(OTU)) %>%
-  unique() 
-dim(df.fast.L2FC)
-df.fast.merge <- merge(df.fast.L2FC, df.fast)
-
-df.affinity <- df %>%
-  subset(experiment == 'affinity'&
-           T.cutoff %in% c('Low thermo > 50','Mid thermo > 50') &
-           intercept > 0) %>%
-  subset(intercept > (mean(intercept)-1*sd(intercept)) ) %>% 
-  subset(select = c(OTU,Phylum, Class, Order, Family, Genus, Species)) %>%
-  unique()
-dim(df.affinity)
-
-df.affinity.L2FC  <- df.L2FC %>%
-  subset(experiment == 'affinity'  &
-           T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C') &
-           mu > 0) %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  subset(select = c(OTU)) %>%
-  unique() 
-dim(df.affinity.L2FC)
-
-df.affinity.merge <- merge(df.affinity.L2FC, df.affinity)
-
-df.full <- df.L2FC
-
-# Filter u ----
-# First pull out enriched taxa:
-df <-  subset(df.full, mu > 0)
-
-# Create a dataframe for survivors filtering by temperature cutof and 1 sd from 
-#   the mean of the intercept. Remove duplicate taxa. 
-df.survival <- subset(df, experiment == 'survival' &
-                        T.cutoff %in% c('low thermo > 50 C','mid thermo > 50 C')) %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  mutate(survival.L2FC = L2FC) %>%
-  dplyr::group_by(OTU) %>%
-  dplyr::mutate(max.mu = max(mu)) %>%
-  subset(mu == max.mu) %>%
-  subset(select = c(OTU, survival.L2FC)) %>%
-  unique()%>%
-  mutate(survivor = 'yes')
-
-# Create dataframe for fast growers filtering for 1 sd from the mean: -----
-df.fast <- subset(df, experiment == 'fast growth') %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  mutate(fast.L2FC = L2FC)%>%
-  dplyr::group_by(OTU) %>%
-  dplyr::mutate(max.mu = max(mu)) %>%
-  subset(mu == max.mu) %>%
-  subset(select = c(OTU, fast.L2FC)) %>%
-  unique() %>%
-  mutate(fast = 'yes')
-
-# Create data frame for affinity taxa filtering for temperature cutoff and 1
-#   sd from the mean:
-df.affinity <- subset(df, experiment == 'affinity' &
-                        T.cutoff %in% c('Low thermo > 50C','Mid thermo > 50C')) %>%
-  subset(mu > (mean(mu)-1*sd(mu))) %>%
-  mutate(affinity.L2FC = L2FC)%>%
-  dplyr::group_by(OTU) %>%
-  dplyr::mutate(max.mu = max(mu)) %>%
-  subset(mu == max.mu) %>%
-  subset(select = c(OTU, affinity.L2FC)) %>%
-  unique()%>%
-  mutate(affinity = 'yes')
-
-# Combine the three dataframes:
-df.index <- merge(df.survival, df.fast, all = TRUE) %>%
-  merge(df.affinity, all = TRUE) %>%
-  subset(select = c(OTU, survivor, fast, affinity))
-
-df.ids <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv') %>%
-  subset(select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
-  unique()
-df.ids <- merge(df.index,df.ids, all = FALSE)
-write.csv(df.ids, '../tables/all-responding-otus.csv', row.names = FALSE)
-
-# Next take the full responder dataset and filter out any duplicate taxa
-
-x.1 <- df.full %>%
-  subset(experiment == 'survival') %>%
-  subset(select = c(OTU, mu, experiment,horizon,
-                    fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, experiment) %>%
-  dplyr::mutate(max.mu = max(abs(mu))) %>%
-  subset(max.mu == abs(mu)) %>%
-  dplyr::mutate(survival.L2FC = L2FC) %>%
-  subset(select = c(OTU, survival.L2FC)) %>%
-  unique()
-
-x.2 <- df.full %>%
-  subset(experiment == 'fast growth') %>%
-  subset(select = c(OTU, mu, experiment,horizon,
-                    fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, experiment) %>%
-  dplyr::mutate(max.mu = max(abs(mu))) %>%
-  subset(max.mu == abs(mu)) %>%
-  dplyr::mutate(fast.L2FC = L2FC) %>%
-  subset(select = c(OTU, fast.L2FC)) %>%
-  unique()
-
-x.3 <- df.full %>%
-  subset(experiment == 'affinity') %>%
-  subset(select = c(OTU, mu, experiment,horizon,
-                    fold.change, L2FC)) %>%
-  dplyr::group_by(OTU, experiment) %>%
-  dplyr::mutate(max.mu = max(abs(mu))) %>%
-  subset(max.mu == abs(mu)) %>%
-  dplyr::mutate(affinity.L2FC = L2FC) %>%
-  subset(select = c(OTU, affinity.L2FC)) %>%
-  unique()
-
-x <- merge(x.1, x.2, all = TRUE) %>%
-  merge(x.3, all = TRUE)
-
-# Create list of responding taxa:
-responding.OTU.list = unique(df.index$OTU)
-
-# Then filter this to include only taxa identified as responders (i.e. meeting
-#   the respective cutoffs for at least one of the three trait experiments)
-df.traits <- filter(x, OTU %in% responding.OTU.list) %>% 
-  unique()
-
-df.traits <- merge(df.index, df.traits)
-
-#df.traits <- test %>%
-#  merge(unique(subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species))))
-
-df.traits$trait = 'null'
-
-for (i in 1:nrow(df.traits)) {
-  if (df.traits$survivor[i] == 'yes' &
-      df.traits$survival.L2FC[i] > 0 &
-      is.na(df.traits$fast[i]) == TRUE &
-      is.na(df.traits$affinity[i]) == TRUE) {
-    df.traits$trait[i] = 'survival'
-      } else if (df.traits$fast[i] == 'yes' &
-                 df.traits$fast.L2FC[i] > 0 &
-                 is.na(df.traits$survivor[i]) == TRUE &
-                 is.na(df.traits$affinity[i]) == TRUE) {
-        df.traits$trait[i] = 'fast growth'
-      } else if (df.traits$affinity[i] == 'yes' &
-                 df.traits$affinity.L2FC[i] > 0 &
-                 is.na(df.traits$survivor[i]) == TRUE &
-                 is.na(df.traits$fast[i]) == TRUE) {
-        df.traits$trait[i] = 'affinity'
-      } else if (df.traits$survivor[i] == 'yes' &
-                 df.traits$survival.L2FC[i] > 0 &
-                 df.traits$fast[i] == 'yes' &
-                 df.traits$fast.L2FC[i] > 0 &
-                 is.na(df.traits$affinity[i]) == TRUE) {
-        df.traits$trait[i] = 'survival and fast growth'
-      } else if (df.traits$fast[i] == 'yes' &
-                 df.traits$fast.L2FC[i] > 0 &
-                 df.traits$affinity[i] == 'yes' &
-                 df.traits$affinity.L2FC[i] > 0 &
-                 is.na(df.traits$survivor[i]) == TRUE) {
-        df.traits$trait[i] = 'fast growth and affinity'
-      } else if (df.traits$survivor[i] == 'yes' &
-                 df.traits$survival.L2FC[i] > 0 &
-                 df.traits$affinity[i] == 'yes' &
-                 df.traits$affinity.L2FC[i] > 0 &
-                 is.na(df.traits$fast[i]) == TRUE) {
-        df.traits$trait[i] = 'survival and affinity'
-      } else if (df.traits$survivor[i] == 'yes' &
-                 df.traits$survival.L2FC[i] > 0 &
-                 df.traits$fast[i] == 'yes' &
-                 df.traits$fast.L2FC[i] > 0 &
-                 df.traits$affinity[i] == 'yes' &
-                 df.traits$affinity.L2FC[i] > 0) {
-        df.traits$trait[i] = 'survival, fast growth, \nand affinity'
-      } else {
-        df.traits$trait[i] = 'none'
-      } 
-}
-
-unique(df.traits$trait)
-
-head(df.traits)
-
-library(RColorBrewer)
-old.trait.colors = c('gold','green','royalblue3','purple','darkred','orange','black')
-trait.colors = c(brewer.pal(n=10, name = 'Spectral'), 'black')
-
-trait.colors = c('#E6AB02','#33A02C','#386CB0','#762A83','#D73027','#F46D43','black')
-
-# Finally build trait trade-off plots:
-p1 = ggplot(df.traits) + 
-  geom_hline(yintercept = 0) + 
-  geom_vline(xintercept = 0)+ 
-  geom_point(aes(x=survival.L2FC, y=fast.L2FC, color = trait, fill = trait), shape = 21,size=4, alpha=1) + 
-  theme_bw() +
-  labs(x= expression(Survival~(log[2]-fold~change)),
-       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = expression(Fast~growth~(log[2]-fold~change))) + 
-  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=10),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=10),
-        legend.position = 'none',
-        # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")+
-  stat_smooth(aes(x=survival.L2FC, y=fast.L2FC),method=lm, se=FALSE, color = 'grey40',
-              geom = 'smooth')
-
-p2 = ggplot(df.traits) + 
-  geom_hline(yintercept = 0) + 
-  geom_vline(xintercept = 0)+ 
-  geom_point(aes(x=fast.L2FC, y=affinity.L2FC, color = trait, fill=trait), shape = 21,  size=4,alpha=1) + 
-  theme_bw() +
-  labs(x= expression(Fast~growth~(log[2]-fold~change)),
-       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = expression(Post~fire~envir.~affinity~(log[2]-fold~change))) + 
-  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=10),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=10),
-        legend.position = 'none',
-        # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-p3 = ggplot(df.traits) + 
-  geom_hline(yintercept = 0) + 
-  geom_vline(xintercept = 0)+ 
-  geom_point(aes(x=affinity.L2FC, y=survival.L2FC, color = trait, fill = trait), 
-             shape = 21,size=4,alpha=1) + 
-  theme_bw() +
-  labs(x=expression(Post~fire~envir.~affinity~(log[2]-fold~change)),
-       #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = expression(Survival~(log[2]-fold~change)),
-       color = 'Bacterial strategy:',
-       fill = 'Bacterial strategy:') + 
-  scale_color_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  scale_fill_manual(limits = c('survival','survival and fast growth','fast growth','fast growth and affinity',
-                                'affinity','affinity and survival','survival, fast growth, \nand affinity'),
-                     values = trait.colors) + 
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = 'none',
-        # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-cowplot::plot_grid(p1, p2,p3, ncol=3)
-
-test <- lm(fast.L2FC ~ affinity.L2FC, data = df.traits)
-summary(test)
-test
-#
-
-x <- grDevices::rainbow(n=6)
-
-df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
-df <- subset(df, select = c(OTU, Domain, Phylum, Class, Order, Family, Genus, Species)) %>%
-  unique()
-
-df.traits <- merge(df.traits,df)
-dim(df.traits)
-```
-
-```{r}
-# How much of total community do affinity taxa account for?
-ps.norm.LI <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt == 'LIwA', ps.norm.gDNA)
-ps.norm.LI <- prune_taxa(taxa_names(ps.norm.LI) %in% df.affinity.L2FC$OTU, ps.norm.LI)
-
-df.norm.LI <- psmelt(ps.norm.LI)
-df.norm.LI$burn.trtmt = factor(df.norm.LI$burn.trtmt, levels = c('control','wet','dry'))
-
-df.norm.LI <- df.norm.LI %>%
-  group_by(core.id.hor.incub, horizon, burn.trtmt) %>%
-  summarize(sum.Abundance = sum(Abundance))
-
-p = ggplot(df.norm.LI, aes(x=burn.trtmt, y = sum.Abundance, color = horizon)) + 
-  geom_point() + 
-  facet_grid(~horizon) + 
-  theme_bw()
-```
-
-# PERMANOVAs:
+# PERMANOVAs, Supplementary:
 ```{r}
@@
 
-# Figure 7:
-Ordinations
-```{r}
-# Full ordination
-ps.full.dataset <- readRDS('../../CombinedFireSim1519/ps.1519FireSim.merged')
-tree <- ape::read.tree('../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')
-
-tree <- phy_tree(tree)
-tax <- tax_table(ps.full.dataset)
-otu <- otu_table(ps.full.dataset)
-sam <- sample_data(ps.full.dataset)
-
-ps.full.dataset = phyloseq::phyloseq(otu,tax, sam,tree)
-ps.full.dataset
-
-# Setting some plot parameters
-year.labs = c("One year post-fire","Five years post-fire")
-names(year.labs) = c(1,5)
-horizon.labs = c("Mineral","Organic")
-
-# Playing with new datasets
-ps = ps.full.dataset
-
-# Add column with pairs info
-sample_data(ps)$Pairs = paste(sample_data(ps)$Site_ID,sample_data(ps)$Org_or_Min,sep="_")
-head(sample_data(ps)$Pairs)
-
-# Normalize sample counts
-ps.norm = transform_sample_counts(ps,function(x) x/sum(x))
-sample_data(ps.norm)$Study = sample_data(ps.norm)$Years_Since_Fire
-sample_data(ps.norm)$Study[is.na(sample_data(ps.norm)$Study)]="Lab"
-
-ord.nmds = ordinate(ps.norm,method = "NMDS",ddistance="wunifrac",k=3, weighted=TRUE)
-
-plot_ordination(ps.norm,ord.pcoa,color="burn.trtmt",shape="incub.trtmt")
-plot_ordination(ps.norm,ord.nmds,color="pH",shape="Study")
-# Neat, they all fall out on top of each other. That's nice.
-colnames(sample_data(ps.norm))
-
-ps.norm.gDNA <- prune_samples(sample_data(ps.norm.gDNA)$incub.trtmt %in% c('pb','SI','LIwA'), ps.norm.gDNA)
-ps.norm.gDNA <- prune_taxa(taxa_sums(ps.norm.gDNA)>0,ps.norm.gDNA)
-
-MyNMDS.full.gDNA <- ordinate(ps.norm.gDNA, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)
-
-# Ordination plot with horizons and deg.hrs
-p1 = plot_ordination(ps.norm.gDNA, MyNMDS.full.gDNA, axes = c(1,2), 
-                      color = "burn.trtmt",
-                      shape = 'incub.trtmt') + 
-  facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels,
-                                                   DNA.type = DNALabels,
-                                                   incub.trtmt = IncubLabels))+
-  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
-  geom_point(size=3, alpha=0.8) +
-  #geom_line(aes(group = core.id.hor)) +
-  labs(color = 'Burn treatment',
-       #color = expression("Degree ("*degree*C*") hours"), 
-       shape = 'experiment') +
-  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
-  scale_color_manual(values = c('black','orange','red'),
-                     labels = c('Unburned control', 'Wet soil burn','Wry soil burn'),
-                     breaks = c('control','wet','dry'))+
-  scale_shape_manual(values = c('circle','square','triangle'),
-                     labels = c('Fire survival', 'Fast growth','Post-fire envir. affinity'),
-                     breaks = c('pb','SI','LIwA')) +
-  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
-  #scale_shape_manual(values = c('circle','triangle'),
-   #                  labels = c('O horizon','Mineral'),
-    #                 breaks = c('O','A')) + 
-  theme(legend.text = element_text(face = 'italic',size = 16),
-        axis.title = element_text(size=16),
-        axis.text = element_text(size=16),
-        legend.title = element_text(size=16)) + 
-  theme_bw()
-
-p1
-```
-
-# Supplementary
-```{r}
-# Carbon and nitrogen loss
-pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = percent.total.C, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
-    theme_bw()+
-  labs(x= 'Burn treatment',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Total C (%)',
-       fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey90'),
-                     limits = c('O','A'),
-                     labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-pChange_N <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = percent.total.N, fill = horizon), alpha = 0.7, varwidth = FALSE) + 
-    theme_bw()+
-  labs(x= 'Burn treatment',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Total N (%)',
-       fill = 'Soil horizon') + 
-  scale_fill_manual(values = c('black','grey90'),
-                     limits = c('O','A'),
-                     labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Wet soil\nburn','Dry soil\nburn')) +
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-cowplot::plot_grid(pChange_C, pChange_N, ncol=2)
-
-test <- aov(percent.total.N ~ burn.trtmt, data = subset(df.meta, incub.trtmt == 'SI' & horizon == 'O'))
-summary(test)
-TukeyHSD(test)
-
-# Traits
-df.resp.taxa <- merge(df.survival.L2FC, df.fast.L2FC, all = TRUE) %>% merge(df.affinity.L2FC, all = TRUE)
-
-ps.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.resp.taxa$OTU, ps.norm.full)
-ps.taxa
-df.taxa <- psmelt(ps.taxa)
-
-# survival
-ps.survival.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.survival.L2FC$OTU, ps.norm.full)
-ps.survival.taxa
-
-df.survival.taxa <- psmelt(ps.survival.taxa)
-
-df.survival.taxa$burn.trtmt <- factor(df.survival.taxa$burn.trtmt, levels = c('control','wet','dry'))
-
-p = ggplot(subset(df.survival.taxa, incub.trtmt == 'pb' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
-  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
-  theme_bw()+
-  facet_wrap(~horizon,ncol=1) + 
-  scale_fill_manual(values = c('black','slategray3','tan3'),
-                     limits = c('control','wet','dry'),
-                     labels = c('control','wet soil','dry soil'))+
-  labs(fill = 'Burn treatment',
-       x = 'site',
-       y='Total abundance (%)') + 
- theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-# fast
-ps.fast.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.fast.L2FC$OTU, ps.norm.full)
-ps.fast.taxa
-
-df.fast.taxa <- psmelt(ps.fast.taxa)
-
-p = ggplot(subset(df.survival.taxa, incub.trtmt == 'SI' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
-  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
-  theme_bw()+
-  facet_wrap(~horizon,ncol=1) + 
-  scale_fill_manual(values = c('black','slategray3','tan3'),
-                     limits = c('control','wet','dry'),
-                     labels = c('control','wet soil','dry soil'))+
-  labs(fill = 'Burn treatment',
-       x = 'site',
-       y='Total abundance (%)') + 
- theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-# affinity
-ps.affinity.taxa <- prune_taxa(taxa_names(ps.norm.full) %in% df.affinity.L2FC$OTU, ps.norm.full)
-ps.affinity.taxa
-
-df.affinity.taxa <- psmelt(ps.affinity.taxa)
-
-p = ggplot(subset(df.survival.taxa, incub.trtmt == 'LIwA' & DNA.type == 'gDNA'), aes(x=site, y = Abundance)) + 
-  geom_bar(aes(fill = burn.trtmt),stat = 'identity',position = 'dodge') + 
-  theme_bw()+
-  facet_wrap(~horizon,ncol=1) + 
-  scale_fill_manual(values = c('black','slategray3','tan3'),
-                     limits = c('control','wet','dry'),
-                     labels = c('control','wet soil','dry soil'))+
-  labs(fill = 'Burn treatment',
-       x = 'site',
-       y='Total abundance (%)') + 
- theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = 'right',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-```
-
-FIN --------------------------------
-
-EXTRAS:
-
-# SI: plot responders as fraction of total comm. vs. total C mineralized over 5 week incub.
-```{r}
-### Goal plot with fraction of total comm by trait category vs. total C-CO2 respired after 5 weeks
-
-# 1. import trait data
-df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
-head(df)
-
-df$trait = 'TBD'
-
-# assign traits:
-for (i in 1:nrow(df)) {
-  if (is.na(df$mu.fast.max[i]) & is.na(df$mu.affinity.max[i])) {
-    df$trait[i] = 'Survivor' 
-  } else if (is.na(df$mu.survival.max[i]) & is.na(df$mu.affinity.max[i])) {
-    df$trait[i] = 'Fast grower' 
-  } else if (is.na(df$mu.survival.max[i]) & is.na(df$mu.fast.max[i])) {
-    df$trait[i] = 'Affinity taxa' 
-  } else if (is.na(df$mu.survival.max[i])) {
-    df$trait[i] = 'Fast grower and affinity taxa'
-  } else if (is.na(df$mu.affinity.max[i])) {
-    df$trait[i] = 'Survivor and fast grower'
-  } else if (is.na(df$mu.fast.max[i])) {
-    df$trait[i] = 'Survivor and affinity taxa' 
-  } else {
-    df$trait[i] = 'ALL'
-  }
-}
-
-# 2. import full comm data at end of SI incubation
-ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI', ps.norm.full)
-
-# 3. Assign traits to OTUs in the SI comm data
-ps.norm.SI <- prune_taxa(taxa_names(ps.norm.SI) %in% df$OTU, ps.norm.SI)
-ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
-
-df.norm.SI <- psmelt(ps.norm.SI)
-
-df.norm.SI <- merge(df.norm.SI, subset(df, select = c(OTU, trait)))
-
-p = ggplot(df.norm.SI, aes(x=burn.trtmt, y=Abundance)) + 
-  geom_bar(aes(fill=trait), stat='identity', position='stack')
-
-# 4. Import respiration data
-#df.resp <- read.csv("../../data/fractional-c-remaining.csv")
-# df.resp <- df (imported from "incubations_microbial_respiration_TLWcheck.R")
-
-# 5. sum total respiration at end of 5 weeks
-df.resp.SI <- subset(df.resp, Incubation.trtmt == 'SI')
-
-# 6. merge trait and respiration dataframes
-df.sum <- df.norm.SI %>%
-  group_by(Full.id, trait) %>%
-  mutate(trait.abun = sum(Abundance)) %>%
-  subset(select = c(core.id,trait,trait.abun)) %>%
-  unique() %>%
-  merge(df.resp.SI, by = 'core.id')
-
-# 7. plot fraction of total comm vs. total C-CO2 respired
-p = ggplot(subset(df.sum, Day==34), aes(x=trait.abun, y = C.CO2.absorbed.per.g.C)) + 
-  geom_point(aes(color=trait)) + 
-  facet_wrap(~burn.trtmt)+
-  theme_bw()
-
-p = ggplot(df.sum, aes(x=(1-fractional.C.remaining),y=trait.abun)) + 
-  geom_bar(aes(fill=trait), stat='identity', position='stack') + 
-  theme_bw()
-
-# Initial mineralization after 2-7 days
-
-```
-
-# figuring out corncob + trait assignments
-```{r}
-df <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
-
-unique(subset(df, select = c(experiment, DNA.type, Comparison, pH.cutoff, Temp.cutoff)))
-
-df.LI <- read.csv('../data/sequence-data/LibCombined/corncob-output/Ex3 Affinity/all-responders.csv')
-
-df$horizon <- factor(df$horizon, levels = c('O','A'))
-df$experiment <- factor(df$experiment, levels = c('survival','fast growth','affinity'))
-
-for (i in 1:nrow(df)) {
-  if (abs(df$intercept[i]) > 2) {
-    df$trimmed.intercept[i] = df$intercept[i]
-  } else {
-    df$trimmed.intercept[i] = NA
-  }
-}
-
-p = ggplot(df) + 
-  geom_histogram(aes(intercept),fill = 'red', binwidth=1) + 
-  #geom_histogram(aes(trimmed.intercept), fill = 'blue', binwidth=1) + 
-  theme_bw() + 
-  facet_grid(experiment+DNA.type~horizon, scales = 'free')
-
-length(unique(subset(df, Temp.cutoff == 'Low thermo greater than 50 C' &
-                       experiment == 'survival')$OTU))
-
-p1 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
-  geom_histogram() + 
-  theme_bw() + 
-  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')
-
-p2 = ggplot(subset(df, experiment == 'fast growth'), aes(intercept)) +
-  geom_histogram() + 
-  theme_bw() + 
-  facet_grid(horizon+Comparison~pH.cutoff, scales = 'free')
-
-p3 = ggplot(subset(df, experiment == 'survival'), aes(intercept)) +
-  geom_histogram() + 
-  theme_bw() + 
-  facet_grid(horizon+Comparison~Temp.cutoff, scales = 'free')
-
-length(unique(subset(df, intercept > 0 & experiment == 'affinity')$OTU))
-length(unique(subset(df, intercept < 0 & experiment == 'affinity')$OTU))
-length(unique(subset(df, intercept > 1 & experiment == 'affinity')$OTU))
-length(unique(subset(df, intercept < -1 & experiment == 'affinity')$OTU))
-
-dim(subset(df, experiment == 'fast growth' &
-             horizon == 'O' &
-             Comparison == 'pb.dry.v.SI.dry' &
-             pH.cutoff != 'null'))
-             #Temp.cutoff != 'null'))
-
-```
-
-# PLotting rel. abundance of responders:
-Reallying interesting data. We're seeing interesting trends with positive responders.
-The relative abundance of positive responders increases across the dry soil post-burn
-pH range, but decreases across the control soil pH range. 
-```{r}
-df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-resopnders.csv')
-df.full3 <- read.csv('../data/sequence-data/LibCombined/corncob-output/Ex3 Affinity/all-responders.csv')
-df.LI.norm$burn.trtmt <- factor(df.LI.norm$burn.trtmt, levels = c('control','wet','dry'))
-
-for (i in 1:nrow(df.full3)) {
-  if (df.full3$Estimate[i] > 0) {
-    df.full3$Response[i] = 'positive'
-  } else if (df.full3$Estimate[i] < 0) {
-    df.full3$Response[i] = 'negative'
-  }
-}
-
-df.full3.LIn <-  subset(df.full3, Comparison %in% c('LIn.dry.v.LIn.control'))$OTU
-df.full3.LIwA <- subset(df.full3, Comparison %in% c('LIwA.dry.v.LIwA.control'))$OTU
-
-df.count <- df.full3 %>%
-  group_by(Comparison, Controlling.for) %>%
-  count(Response)
-
-# PUll out a subset of the corncob analyses:
-df.affinity <- subset(df.full3, Comparison %in% c('LIwA.dry.v.LIwA.control') &
-                        Controlling.for == 'pH category: low, mid, high' ) %>%
-  subset(select = c(OTU, horizon, Response))
-
-# OR just pull out positive responding OTUs:
-df.affinity <- df.full3 %>%
-  subset(Estimate > 0) %>%
-  subset(Comparison %in% c('LIwA.dry.v.LIwA.control') & Controlling.for =='control pH') %>%
-  subset(select = c(OTU, horizon, Response))
-
-# Create a list of positive/negative responding OTUs
-df.affinity.positive = subset(df.affinity, Response == 'positive')
-df.affinity.negative = subset(df.affinity, Response == 'negative')
-
-# Match these lists to the full community data.
-df.LI.positive.responders <- subset(df.LI.norm, OTU %in% df.affinity.positive$OTU)
-df.LI.negative.responders <- subset(df.LI.norm, OTU %in% df.affinity.negative$OTU)
-df.LI.not.responders <- subset(df.LI.norm, !OTU %in% df.affinity$OTU)
-
-# Create response categories to use in ggplot
-df.LI.positive.responders$Response = 'positive'
-df.LI.negative.responders$Response = 'negative'
-df.LI.not.responders$Response = 'none'
-
-# Combine the dataframe
-df.LI.responders <- rbind(df.LI.positive.responders,df.LI.negative.responders,df.LI.not.responders)
-
-# Convert pH to a character for the purpose of plotting
-df.LI.responders$pH <- as.character(df.LI.responders$pH)
-df.LI.responders$cntl.pH <- as.character(df.LI.responders$cntl.pH)
-
-p1 = ggplot(subset(df.LI.responders, horizon == 'O' & site != 19), aes(x=cntl.pH, y=Abundance, fill=Response))+
-  geom_bar(stat = 'identity') +
-  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
-             labeller = labeller(incub.trtmt = IncubLabels, 
-                                 horizon = HorizonLabels,
-                                 burn.trtmt = BurnLabels)) +
-  scale_fill_manual(values = c('forestgreen','grey50','red'),
-                     limits = c('positive','none', 'negative'),
-                     labels = c('Positive','No Response', 'Negative')) +
-  labs(title = 'experiment3: Both LIn and LIwA data: controlling for pre-burn pH',
-       y = 'Relative abundance') + 
-  theme(legend.position = 'bottom',
-        axis.text.x = element_text(size=8), 
-        legend.text = element_text(size=8))
-
-df.LI.sum <- df.LI.responders %>%
-  group_by(Full.id, Response) %>%
-  mutate(sum.abun = sum(Abundance)) %>%
-  subset(select = c(Full.id, pH, cntl.pH, horizon, burn.trtmt, incub.trtmt, Response,site, sum.abun)) %>%
-  unique()
-
-df.LI.sum$burn.trtmt <- factor(df.LI.sum$burn.trtmt, levels = c('control','wet','dry'))
-df.LI.sum$site <- as.character(df.LI.sum$site)
-
-p2 = ggplot(subset(df.LI.sum, horizon == 'O' & Response != 'none' & burn.trtmt == 'dry'), aes(x=pH, y=(sum.abun), color = site))+
-  geom_point(size=3) +
-  facet_grid(incub.trtmt~burn.trtmt, scales = 'free', 
-             labeller = labeller(incub.trtmt = IncubLabels, 
-                                 horizon = HorizonLabels,
-                                 burn.trtmt = BurnLabels)) +
-        stat_smooth(method=lm,se = FALSE,color='black') +
-  #scale_color_manual(values = c('forestgreen','grey50','red'),
-   #                  limits = c('positive','none', 'negative'),
-    #                 labels = c('Positive','No Response', 'Negative')) +
-  labs(title = 'experiment3: Responders identified LIwA.dry.vs.control \ncontrolling for pre-burn pH',
-       y = 'Relative abundance',
-       x = 'post-burn pH') + 
-  theme(legend.position = 'bottom',
-        axis.text.x = element_text(size=8), 
-        legend.text = element_text(size=8))+
-  ylim(0,0.2)
-
-```
-
-# Mapping relative abundance of responding taxa across experiments:
-```{r}
-df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-resopnders.csv')
-
-df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
-df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
-df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')
-
-p = ggplot(data = df.pb.gDNA.OTU, aes(x=site, y = Abundance, fill = Phylum)) + 
-  geom_bar(stat = 'identity') + 
-  facet_grid(burn.trtmt~horizon) + 
-  theme_bw()
-
-df <- df.full.OTU %>%
-  subset(Estimate > 0) %>%
-  group_by(OTU) %>%
-  mutate(max.Estimate = max(Estimate)) %>%
-  subset(abs(Estimate) > 1) %>%
-  merge(df.LI.norm) %>%
-  subset(incub.trtmt == 'LIwA')
-
-df$site <- as.character(df$site)
-df$change.pH <- as.character(df$change.pH)
-df$burn.trtmt <- factor(df$burn.trtmt, levels = c('control','wet','dry'))
-
-p <- ggplot(data = subset(df, burn.trtmt == 'dry' & horizon == 'O'), 
-            aes(x=site, y = Abundance, Fill = experiment)) + 
-  theme_bw()+
-  #geom_point()+
-  geom_bar(stat = 'identity') +
-  facet_wrap(~experiment, scale = 'free') + 
-  #stat_smooth(method=lm,se = FALSE,color='black') +
-  theme(axis.text.x = element_text(angle = 90))
-```
-
-# Exploring composition data for 24-hours post-burn:
-```{r}
-#df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
-#df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
-
-p = ggplot(data = df.pb.gDNA.OTU, aes(x=site, y = Abundance, fill = Phylum)) + 
-  geom_bar(stat='identity')+
-  facet_grid(horizon~burn.trtmt, labeller = labeller(horizon = HorizonLabels,
-                                                     burn.trtmt = BurnLabels)) + 
-  theme_bw() +
-  theme(legend.position = 'bottom')
-
-# Most abundant taxa; most abundant responders:
-df <- df.pb.gDNA.OTU %>%
-  group_by(Family) %>%
-  mutate(sum.Abundance = sum(Abundance))
-
-p = ggplot(data = subset(df, sum.Abundance > 2.08), aes(x=site, y = Abundance, fill = Class)) + 
-  geom_bar(stat='identity')+
-  facet_grid(horizon~burn.trtmt, labeller = labeller(horizon = HorizonLabels,
-                                                     burn.trtmt = BurnLabels)) + 
-  theme_bw() +
-  theme(legend.position = 'bottom')
-
-```
-
-# Calculate bray-curtis dissimilarity for LIwA vs. SI
+Bray-Curtis dissimilarity? 
 ```{r, message = FALSE}
 # This is a possibly convoluted piece of code to first create a Bray-Curtis
-#     dissimilarity matrix and then pull out the dissimilarities between SI and
-#     LIwA cores.
-ps.bray <- prune_samples(sample_data(ps.raw.gDNA)$DNA.type == 'gDNA' &
-                           sample_data(ps.raw.gDNA)$incub.trtmt %in% c('SI','LIwA')&
-                           sample_data(ps.raw.gDNA)$Full.id %in% df.meta$Full.id, ps.raw.gDNA)
-
-ps.bray <- prune_taxa(taxa_sums(ps.bray) > 0, ps.bray)
-
-dist.bray.SIvLIwA <- as.matrix(distance(ps.bray, method = 'bray', type = 'samples'))
+#     dissimilarity matrix and then pull out the dissimilarities between dry/wet
+#     burns and corresponding control cores.
+
+# First: Calculate Bray-curtis dissimilarity matrix ----
+ps.cDNA.raw <- prune_samples(sample_data(ps.raw.full)$DNA.type == 'cDNA', ps.raw.full)
+ps.cDNA.raw <- prune_taxa(taxa_sums(ps.cDNA.raw) > 0, ps.cDNA.raw)
+
+dist.bray.full <- as.matrix(distance(ps.raw.full, method = 'bray', type = 'samples'))
+
+# Look at some figures
+hist(dist.bray.full)
+heatmap(dist.bray.full)
 
 # Convert distance matrix into dataframe
-df <- data.frame(dist.bray.SIvLIwA)
+df <- data.frame(dist.bray.full)
 
 # Bring in meta data and subset for specific analysis
-df.meta.sub <- subset(df.meta, select = c(Full.id, burn.trtmt,site, core.id.hor,
-                                          incub.trtmt,core, horizon)) %>%
-  subset(incub.trtmt %in% c('SI','LIwA')) %>%
-  unique()
-
-# Combine metadata and distances so we can use burn treatment to sort
-#df <- merge(df, df.meta.pb.cDNA)
+df.meta.sub <- subset(df.meta, select = c(Full.id, burn.trtmt,site, DNA.type,
+                                          incub.trtmt,core, horizon,
+                                          pH, change.pH))
 
 # Create a dataframe with the colnames and Full.ID
-x <- data.frame(str_split(colnames(df)[1:276], 'X', simplify = TRUE)[,2])
+x <- data.frame(str_split(colnames(df)[1:460], 'X', simplify = TRUE)[,2])
 
@@
 x <- x %>%
-  unite(Bray.ID, c('X',"ID.bray"), sep = '', remove = TRUE) %>%
-  unique()
-
-# Create row with LIwA id, SI id, and core.id.hor:
-df.LIwA <- subset(df.meta, incub.trtmt == 'LIwA') %>%
-  mutate(LIwA.full.id = Full.id) %>%
-  subset(select = c(core.id.hor, LIwA.full.id))
-
-df.SI <- subset(df.meta, incub.trtmt == 'SI') %>%
-  mutate(SI.full.id = Full.id) %>%
-  subset(select = c(core.id.hor, SI.full.id)) %>%
-  unique()
-
-#df.list <- merge(df.LIwA, df.SI, by = 'core.id.hor')
+  unite(Bray.ID, c('X',"ID.bray"), sep = '', remove = TRUE)
+
+# Next, pull out the control cores from the meta data and assign them to "Control.id"
+df.meta.control <- df.meta %>%
+  subset(burn.trtmt == 'control') %>%
+  mutate(Control.id = Full.id) %>%
+  subset(select = c(Control.id, site, horizon, incub.trtmt, DNA.type))
+
+# Combine list of control cores with full df.meta
+df.meta.list <- merge(subset(df.meta.sub, select = c(Full.id, site, horizon, 
+                                                     DNA.type,burn.trtmt, incub.trtmt, 
+                                                     pH, change.pH)), 
+                      df.meta.control, by = c('site', 'horizon', 'incub.trtmt', 'DNA.type'))
 
@@
 #     df.list now contains Full.id with the corresponding control sample for each 
-#     dry/wet burn and a column ("Bray.ID") that has the sample ID formatted to 
+#     dry/wet burn and a colume ("Bray.ID") that has the sample ID formatted to 
 #     match the distance matrix names.
-df.list <- df.SI %>%
-  merge(df.meta.sub, by = 'core.id.hor') %>%
-  merge(x, by = 'Full.id') %>%
-  subset(incub.trtmt == 'LIwA') %>%
-  unique()
+df.list <- x %>%
+  merge(df.meta.list, by = 'Full.id') %>%
+  subset(burn.trtmt != 'control')
 
@@
 
-head(df.meta.sub)
 # Create and empty data frame to store distances
-df.distances <- data.frame("Full.id" = df.list$Full.id, 'core.id.hor' = 'core.id.hor',
-                           'burn.trtmt' = 'burn', 'SI.full.id' = 'SI.full.id',
-                           'horizon' = 'H',
-                           'BC.distance.btw.SI.and.LIwA' = 'distance',
-                           'incub.trtmt' = 'incub') %>%
+df.distances <- data.frame("Full.id" = df.list$Full.id, 
+                           'control.core' = 'core',
+                           #'burn.trtmt' = 'burn', 'horizon' = 'H',
+                           #'DNA.type' = 'DNA.type',
+                           'BC.distance.btw.burned.and.control' = 'distance'
+                           #'incub.trtmt' = 'incub', 'pH' = 0
+                           ) %>%
   unique()
@@
       if(colnames(df)[k] == df.list$Bray.ID[i] &  # If the distance matrix colume ID matches the sample ID in the list
-         rownames(df)[j] == df.list$SI.full.id[i]) { # And the rowname ID matches the corresponding control core, then...
-        df.distances$BC.distance.btw.SI.and.LIwA[i] = df[j,k] # Pull out the distance and store it in new dataframe
-        df.distances$burn.trtmt[i] = df.list$burn.trtmt[i]
-        df.distances$horizon[i] = df.list$horizon[i]
-        df.distances$incub.trtmt[i] = df.list$incub.trtmt[i]
-        df.distances$SI.full.id[i] = df.list$SI.full.id[i]
+         rownames(df)[j] == df.list$Control.id[i]) { # And the rowname ID matches the corresponding control core, then...
+        df.distances$BC.distance.btw.burned.and.control[i] = df[j,k] # Pull out the distance and store it in new dataframe
+        #df.distances$burn.trtmt[i] = df.list$burn.trtmt[i]
+        df.distances$control.core[i] = df.list$Control.id[i]
+        #df.distances$horizon[i] = df.list$horizon[i]
+        #df.distances$incub.trtmt[i] = df.list$incub.trtmt[i]
+        #df.distances$DNA.type[i] = df.list$DNA.type[i]
+        #df.distances$pH[i] = df.list$pH[i]
+        #df.distances$change.pH[i] = df.list$change.pH[i]
       }
@@
 
-# Remove any samples that didn't have duplicates between LIwA and SI
-df.distances <- subset(df.distances, horizon != 'H')
-
-df.distances$BC.distance.btw.SI.and.LIwA <- as.numeric(df.distances$BC.distance.btw.SI.and.LIwA)
-
-df.distances$incub.trtmt <- factor(df.distances$incub.trtmt, levels = c('pb','SI','LIwA','LIn'))
-
-p=ggplot(subset(df.distances,horizon=='O')) + 
-  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.SI.and.LIwA, fill = horizon),
-               alpha = 0.5) +
+df.distances$BC.distance.btw.burned.and.control <- as.numeric(df.distances$BC.distance.btw.burned.and.control)
+
+# Save backup dataframe.
+df.final <- df.distances
+
+# -----
+df.distances <- read.csv('../data/bray-curtis-dissimilarites.csv')
+
+df.distances <- merge(df.distances, subset(df.meta, burn.trtmt != 'control'))                            
+dim(df.distances)
+
+# Plots ----
+p=ggplot(subset(df.distances, DNA.type == 'cDNA')) + 
+  geom_boxplot(aes(x=burn.trtmt, y = BC.distance.btw.burned.and.control, fill = horizon),
+               alpha = 0.7) +
   theme_bw() +
-  facet_wrap(~horizon, ncol=3,
-             labeller = labeller(horizon = HorizonLabels)) + 
+  facet_wrap(~incub.trtmt, ncol=4,
+             labeller = labeller(incub.trtmt = IncubLabels)) + 
   labs(x='Burn treatment',
-       #y = 'Bray-Curtis dissimilarity between \nsoil 5 weeks post-burn vs. inoculated soil 6 months post-burn',
-       y='Bray-Curtis dissimilarity',
-       fill = 'Soil horizon',
-       title = 'Bray-Curtis dissimilarities for gDNA') + 
-  scale_fill_manual(values = c('black','grey80'),
+       y = 'Bray-Curtis dissimilarity \ncompared to control', 
+       fill = 'Soil horizon') + 
+  scale_fill_manual(values = c('black','grey40'),
                      limits = c('O','A'),
                      labels = c('Organic','Mineral')) +
-  scale_x_discrete(limits = c('control','wet','dry'),
-                   labels = c('Unburned \ncontrol', 'Wet soil \nburn','Dry soil \nburn')) +
+  scale_x_discrete(limits = c('wet','dry'),
+                   labels = c('Moist soil \nburn','Dry soil \nburn')) +
   theme(axis.title = element_text(size=18),
@@
         legend.text = element_text(size=18),
-        strip.text = element_text(size=18))+
+        strip.text = element_text(size=18)) + 
   ylim(0,1)
 
-test <- aov(BC.distance.btw.SI.and.LIwA~burn.trtmt, data = subset(df.distances,horizon=='O'))
+test <- aov(BC.distance.btw.burned.and.control~burn.trtmt*horizon, data = subset(df.distances, DNA.type == 'cDNA'))
 summary(test)
@@
 
-df.meta.combined <- merge(df.meta, df.distances, by = c('Full.id', 'burn.trtmt', 'horizon', 'incub.trtmt'))
-
-p = ggplot(subset(df.meta.combined, horizon == 'A'),aes(x=Thermo.mid.max, y = BC.distance.btw.burned.and.control, fill = horizon)) +
-  geom_point(shape='circle filled',
-             stroke=1,
-             alpha = 0.8,
-             size=3) +
+```
+
+Richness estimates?
+
+If the community composition data of a single sample includes few singletons, we assume that sequencing captured most of the taxa present in the sample.
+If the data includes many singletons, we assume that sequencing missed many rare taxa.
+We can use breakaway to estiamte how many taxa were missed and use this to estimate richness.
+```{r}
+
+# Load data and calculate richness ----
+df.pb.gDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.gDNA.norm.csv')
+df.pb.cDNA.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.pb.cDNA.norm.csv')
+df.SI.OTU <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.SI.norm.csv')
+df.LI.norm <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/df.LI.norm.csv')
+
+head(df.pb.cDNA.OTU)
+
+df.counts.pb.cDNA <- df.pb.cDNA.OTU %>%
+  group_by(Full.id) %>%
+  mutate(counts = length(unique(OTU))) %>%
+  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
+  unique()
+
+df.counts.pb.gDNA <- df.pb.gDNA.OTU %>%
+  group_by(Full.id) %>%
+  mutate(counts = length(unique(OTU))) %>%
+  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
+  unique()
+
+df.counts.SI <- df.SI.OTU %>%
+  group_by(Full.id) %>%
+  mutate(counts = length(unique(OTU))) %>%
+  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
+  unique()
+
+df.counts.LI <- df.LI.norm %>%
+  group_by(Full.id) %>%
+  mutate(counts = length(unique(OTU))) %>%
+  subset(select = c(Full.id, burn.trtmt, horizon, DNA.type, incub.trtmt, counts)) %>%
+  unique()
+
+df.counts <- rbind(df.counts.pb.cDNA, df.counts.pb.gDNA,
+                   df.counts.SI, df.counts.LI)
+
+df.counts$burn.trtmt <-  factor(df.counts$burn.trtmt, levels = c('control','wet','dry'))
+df.counts$horizon <-  factor(df.counts$horizon, levels = c('O', 'A'))
+
+df.counts.pb <- subset(df.counts, incub.trtmt == 'pb')
+
+# Plots ----
+p = ggplot(df.counts.pb, aes(x=burn.trtmt, y=counts)) +
+  geom_boxplot(aes(fill = burn.trtmt), alpha = 0.7) + 
+  geom_point(color = 'black', alpha = 0.4) + 
   theme_bw() + 
-  facet_wrap(burn.trtmt~incub.trtmt, scales = 'free',
-             labeller = labeller(incub.trtmt = IncubLabels,
-                                 burn.trtmt = BurnLabels)) + 
-  labs(x='Max temp, mid-point',
-       y = 'Bray-Curtis dissimilarity compared to control; A horizon', 
-       fill = 'Soil horizon',
-       title = 'Bray-Curtis dissimilarities for gDNA') + 
-  scale_fill_manual(values = c('black','grey40'),
-                     limits = c('O','A'),
-                     labels = c('Organic','Mineral')) +
-  theme(axis.title = element_text(size=12),
-        axis.text = element_text(size=12),
-        legend.title = element_text(size=12),
-        legend.text = element_text(size=12)) + 
-    stat_smooth(method=lm,se = FALSE,color='black')
-
+  facet_grid(horizon~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels,
+                                                               horizon = HorizonLabels, 
+                                                               DNA.type = DNALabels)) + 
+  labs(y = 'unique non-zero OTU count')
+
+test <- aov(counts ~ burn.trtmt, data = subset(df.counts.pb.gDNA, horizon =='O'))
+summary(test)
+TukeyHSD(test)
+
+# Plot richness using "plot_richness" function in phyloseq: ----
+ps <- prune_samples(sample_data(ps.raw.full)$incub.trtmt == 'pb',
+                    ps.raw.full)
+
+sample_data(ps)$burn.trtmt <- factor(sample_data(ps)$burn.trtmt, levels = c('control','wet','dry'))
+sample_data(ps)$horizon <- factor(sample_data(ps)$horizon, levels = c('O','A'))
+
+p = plot_richness(ps, x = "burn.trtmt", measures = 'Shannon') +
+  theme_bw() + 
+  geom_boxplot(aes(fill = horizon), alpha = 0.6) + 
+  facet_grid(horizon~DNA.type+incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels,
+                                                   DNA.type = DNALabels,
+                                                      horizon = HorizonLabels))
 ```
 
-# Control pH vs. Delta pH:
+RNA:DNA ratios?
 ```{r}
-pChange_pH <- ggplot(subset(df.meta, burn.trtmt != 'control'),aes(x=cntl.pH, y = change.pH, color = Thermo.mid.max)) + 
-  geom_point(aes(x=cntl.pH, y = change.pH, color = Thermo.mid.max), alpha = 0.4,size=3)  + 
-      stat_smooth(method=lm,se = FALSE,color='black')+ 
-    theme_bw()+
-  labs(x= 'pre-burn (control) pH',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Change in post-burn pH') + 
-  facet_grid(burn.trtmt~horizon, scales = 'free_y',
-             labeller = labeller(horizon = HorizonLabels,
-                                                     burn.trtmt = BurnLabels))+
-  #scale_color_manual(values = c('black','slategray','tan3'),
-   #                  limits = c('control','wet','dry'),
-    #                 labels = c('control','wet soil','dry soil')) +
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(face="italic",size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+df.norm.ratios <- read.csv('../data/sequence-data/LibCombined/phyloseq-objects/RNA_DNA_norm_ratios.csv')
+# RNA:DNA ratios were calculated by (RNA rel. abundance)/(DNA rel. abundance)
+#     In instances of DNA rel. abundance = 0, I set DNA abundance = 0.0000038, which
+#     is equal to the lowest measured rel. abundance of DNA across the dataset.
+#     In instances of RNA re. abundance = 0, I set ratio = 0.
+
+df.norm.ratios$horizon <- factor(df.norm.ratios$horizon, levels = c('O','A'))
+df.norm.ratios$burn.trtmt <- factor(df.norm.ratios$burn.trtmt, levels = c('control','wet','dry'))
+
+# Plot 
+p = ggplot(data = subset(df.norm.ratios, DNA.abundance > 0.001), aes(x=burn.trtmt, y = RNA.DNA.ratio, fill = horizon)) + 
+  geom_boxplot()+ 
+  #stat_smooth(method=lm,se = FALSE,color='black') +
+  #facet_wrap(~horizon, ncol=1,scale = 'free')+
+  theme_bw() + 
+  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')
+
+# What fraction of total reads for each sample fall below 0.001 relative abundance threshold? -----
+df.DNA.tally <- df.norm.ratios %>%
+  subset(RNA.abundance + DNA.abundance > 0) %>%
+  #subset(DNA.abundance > 0) %>%
+  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
+  mutate(counts = length(OTU)) %>%
+  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
+  tally(DNA.abundance > 0.001) %>%
+  #mutate(DNA.fraction.above.cutoff = n/counts)
+  mutate(non.zero.DNA.fraction = n/counts)
+head(df.DNA.tally)
+
+df.RNA.tally <- df.norm.ratios %>%
+  subset(RNA.abundance + DNA.abundance > 0) %>%
+  #subset(RNA.abundance > 0) %>%
+  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
+  mutate(counts = length(OTU)) %>%
+  group_by(core.id.hor.incub, burn.trtmt, horizon,counts) %>%
+  tally(RNA.abundance > 0.001)%>%
+  mutate(non.zero.RNA.fraction = n/counts)
+  #mutate(RNA.fraction.above.cutoff = n/counts)
+head(df.RNA.tally)
+
+df.DNA.tally$burn.trtmt <- factor(df.DNA.tally$burn.trtmt, levels = c('control','wet','dry'))
+df.RNA.tally$burn.trtmt <- factor(df.RNA.tally$burn.trtmt, levels = c('control','wet','dry'))
+
+p = ggplot(df.DNA.tally, aes(x=burn.trtmt, y =DNA.fraction.above.cutoff, fill = horizon)) + 
+  geom_boxplot() + theme_bw()
+
+test <- aov(DNA.fraction.above.cutoff ~ burn.trtmt*horizon, data = df.DNA.tally)
+summary(test)
+TukeyHSD(test)
+
+test <- aov(non.zero.RNA.fraction ~ burn.trtmt*horizon, data = df.RNA.tally)
+summary(test)
+TukeyHSD(test)
+
+# Re-calculate ratio including only taxa present in both burned and unburned cores: ----
+df.burned <- subset(df.norm.ratios, burn.trtmt == 'dry') %>%
+  subset(DNA.abundance > 0) %>%
+  mutate(burned.DNA.abundance = DNA.abundance) %>%
+  subset(select = c(site, horizon, OTU, burned.DNA.abundance))
+
+df.control <- subset(df.norm.ratios, burn.trtmt == 'control') %>%
+  subset(DNA.abundance > 0) %>%
+  mutate(unburned.DNA.abundance = DNA.abundance) %>%
+  subset(select = c(site, horizon, OTU, unburned.DNA.abundance))
+
+df.shared.OTUs <- merge(df.burned, df.control)
+
+df.common.taxa <- subset(df.norm.ratios, burn.trtmt != 'wet') %>%
+  merge(df.shared.OTUs) %>%
+  mutate(ratio = RNA.abundance/DNA.abundance) %>%
+  group_by(core.id.hor.incub) %>%
+  mutate(mean.ratio = mean(ratio))
+
+df.counts <- df.common.taxa %>%
+  group_by(core.id.hor.incub, burn.trtmt, horizon) %>%
+  tally(DNA.abundance > 0)
+
+dim(df.common.taxa)
+
+# Plot 
+p = ggplot(data = df.common.taxa, aes(x=burn.trtmt, y = ratio, fill = horizon)) + 
+  geom_boxplot()+ 
+  #stat_smooth(method=lm,se = FALSE,color='black') +
+  #facet_wrap(~horizon, ncol=1,scale = 'free')+
+  theme_bw() + 
+  labs(title = 'RNA:DNA \n*only taxa present in paired burned/unburned trtmts')
+
+test <- aov(ratio ~ burn.trtmt*horizon, data = df.common.taxa)
+summary(test)
+TukeyHSD(test)
+
+# Recalculating ratios using raw reads: -----
+ps.raw.gDNA <- prune_samples(sample_data(ps.raw.pb)$DNA.type == 'gDNA', ps.raw.pb)
+ps.raw.gDNA
+ps.raw.gDNA <- prune_taxa(taxa_sums(ps.raw.gDNA)>0, ps.raw.gDNA)
+ps.raw.gDNA
+
+ps.raw.cDNA <- prune_taxa(taxa_sums(ps.raw.cDNA)>0, ps.raw.cDNA)
+
+df.raw.pb.cDNA <- psmelt(ps.raw.cDNA)
+df.raw.pb.gDNA <- psmelt(ps.raw.gDNA)
+
+df.RNA <- df.raw.pb.cDNA %>%
+  mutate(RNA.abundance = Abundance) %>%
+  subset(select = c(core.id.hor.incub, OTU, RNA.abundance))
+
+df.DNA <- df.raw.pb.gDNA %>%
+  mutate(DNA.abundance = Abundance) %>%
+  subset(select = c(core.id.hor.incub, OTU, DNA.abundance, horizon, site, pH, hrzn.degree.hrs,burn.trtmt))
+
+rownames(df.RNA) <- NULL
+rownames(df.DNA) <- NULL
+
+df.merge <- merge(df.RNA, df.DNA, by = c("core.id.hor.incub", "OTU"), all = TRUE)
+
+df.pb <- df.merge %>%
+  group_by(site, OTU) %>%
+  mutate(min = min(DNA.abundance)) %>%
+  subset(min > 0)
+
+df.pb[is.na(df.pb$RNA.abundance),3] <- 0
+
+df.pb <- df.pb %>%
+  mutate(ratio = RNA.abundance/DNA.abundance)
+
+# Plot
+df.pb$burn.trtmt <- factor(df.pb$burn.trtmt, levels = c('control','wet','dry'))
+
+p = ggplot(data = subset(df.pb,horizon =='O'), aes(x=burn.trtmt, y = (ratio), color = burn.trtmt)) + 
+  geom_boxplot()+ 
+  #stat_smooth(method=lm,se = FALSE,color='black') +
+  facet_wrap(~horizon, ncol=1,scale = 'free')+
+  theme_bw() + 
+  labs(title = 'RNA:DNA \nonly taxa present across all trtmts')
+
+test <- aov((ratio) ~ burn.trtmt, data = subset(df.pb, horizon == 'O'))
+summary(test)
+TukeyHSD(test)
+
+# Alternative calculations for RNA:DNA ratios: ----
+
+### Set ratio = 100 if DNA rel. abundance = 0 (Bowsher et al. 2019)
+for (i in 1:nrow(df.norm.ratios)) {
+  if(df.norm.ratios$DNA.abundance[i] == 0) {
+    df.norm.ratios$RNA.DNA.ratio[i] = 100
+  } else {
+    df.norm.ratios$RNA.DNA.ratio[i] = df.norm.ratios$RNA.DNA.ratio[i]
+  }
+}
+
+### If DNA abundance = 0, change it to 1.  (Bowsher et al. 2019)
+#     But this would only work for raw count data.
+for (i in 1:nrow(df.norm.ratios)) {
+  if(df.norm.ratios$DNA.abundance[i] == 0) {
+    df.norm.ratios$DNA.abundance[i] = 0.000038
+  } else {
+    df.norm.ratios$DNA.abundance[i] = df.norm.ratios$DNA.abundance[i]
+  }
+}
+df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance
+
+### Add 1 to all DNA and RNA abundances (Bowsher et al. 2019)
+df.norm.ratios$DNA.abundance = df.norm.ratios$DNA.abundance + 0.000038
+
+#df.norm.ratios$RNA.abundance = df.norm.ratios$RNA.abundance + 0.000038
+
+df.norm.ratios <- subset(df.norm.ratios, DNA.abundance > 0.0001 || RNA.abundance >0.0001 )
+
+df.norm.ratios$RNA.DNA.ratio = df.norm.ratios$RNA.abundance/df.norm.ratios$DNA.abundance
+```
+
+# Weighted mean gene copy number
+Which bacteria are fast-growing following burn treatments of varying severity and under a range of moisture conditions?
+```{r}
+df.WMCN.pb <- read.csv('../../data/WtMeanCopyNum_pb_gDNA.csv')
+df.WMCN.SI <- read.csv('../../data/WtMeanCopyNum_SI.csv')
+df.WMCN.LIwA <- read.csv('../../data/WtMeanCopyNum_LIwA.csv')
+
+df.WMCN.SI <- subset(df.WMCN.SI, core.id != '19UW-WB-11-02' & 
+                    Full.id != '19UW-WB-06-08-A-SI-duplicate' &
+                    Full.id != '19UW-WB-07-02-O-SI-duplicate' &
+                    Full.id != '19UW-WB-11-03-O-SI-duplicate'&
+                    Full.id != '19UW-WB-19-07-A-SI-duplicate' &
+                    Full.id != '19UW-WB-08-10-O-SI' )
+
+summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
+sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'O')$WtMeanCopyNum)
+summary(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)
+sd(subset(df.WMCN.SI, burn.trtmt == 'control' &horizon == 'A')$WtMeanCopyNum)
+
+test = aov(WtMeanCopyNum~ burn.trtmt*horizon, data = df.WMCN.SI)
+summary(test)
+TukeyHSD(test)
+
+df.WMCN <- rbind(df.WMCN.SI, df.WMCN.LIwA, df.WMCN.pb)
+
+df.WMCN <- df.WMCN %>%
+  unite(core.id.hor, c(core.id, horizon), sep = '-', remove=FALSE)
+
+df.WMCN <- merge(df.WMCN, df.meta)
+
+# CHeck for normality:
+p.QQ = qqplot(df.WMCN$hrzn.degree.hrs, df.WMCN$WtMeanCopyNum)
+
+# Plot ----
+df.WMCN$burn.trtmt <- factor(df.WMCN$burn.trtmt, levels = c('control','wet','dry'))
+df.WMCN$horizon <- factor(df.WMCN$horizon, levels = c('O','A'))
+df.WMCN$incub.trtmt <- factor(df.WMCN$incub.trtmt, levels = c('pb','SI','LIwA'))
+
+p1 = ggplot(data = subset(df.WMCN, incub.trtmt != 'LIwA')) + 
+  geom_boxplot(aes(x=burn.trtmt, y=WtMeanCopyNum, fill=horizon),alpha=0.7)+
+  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt = IncubLabels))+
+  theme_bw() + 
+  scale_fill_manual(values = c("darkgreen","grey70"),
+                     labels = c('Organic','Mineral'),
+                     limits = c('O','A'))+
+  scale_x_discrete(limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  labs(x='Burn treatment',
+       y='Weighted mean predicted \n16S rRNA gene copy number',
+       fill = 'Soil horizon') +
+  theme(axis.text.y = element_text(size = 12),
+        axis.text.x = element_text(size = 12),
+        legend.text = element_text(size = 14),
+        legend.title = element_text(size = 14),
+        strip.text = element_text(size=14),
+        legend.position = 'right',
         axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = 'right',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-pChange_pH
-
-df.meta.dry.O <- subset(df.meta, burn.trtmt == 'dry' & horizon == 'A')
-
-model <- lm(change.pH~cntl.pH, data = df.meta.dry.O)
-model
-summary(model)
-
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10))) +
+  ylim(1,NA)
+
+# Stats
+df.WMCN.O <- subset(df.WMCN, horizon == 'O')
+df.WMCN.A <- subset(df.WMCN, horizon == 'A')
+
+fit.df.WMCN.O <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.O)
+fit.df.WMCN.A <- lm(WtMeanCopyNum~hrzn.degree.hrs, data=df.WMCN.A)
+
+summary(fit.df.WMCN.O)
+# p = 2*10^-16, R^2 adj = 0.6081
+summary(fit.df.WMCN.A)
+# p = 2*10^-16, R^2 adj = 0.7883
+
+# Weighted mean copy number STATS:
+test <- aov(WtMeanCopyNum ~ burn.trtmt*horizon, data = subset(df.WMCN, incub.trtmt == 'SI'))
+summary(test)
+TukeyHSD(test)
+
+test.sum <- df.WMCN %>%
+  group_by(burn.trtmt, horizon) %>%
+  summarize(mean.WMCN = mean(WtMeanCopyNum))
+
+# Calculate WMCN change from pb to SI: ----
+df.WMCN.initial <- subset(df.WMCN, incub.trtmt == 'pb') %>%
+  mutate(WMCN.pb = WtMeanCopyNum) %>%
+  subset(select = c(core.id, horizon, burn.trtmt, WMCN.pb))
+
+df.WMCN.SI <- df.WMCN.SI %>%
+  merge(df.WMCN.initial, all = TRUE) %>%
+  mutate(change.WMCN = WtMeanCopyNum - WMCN.pb)
+
+df.WMCN.SI$burn.trtmt <- factor(df.WMCN.SI$burn.trtmt, levels = c('control','wet','dry'))
+
+p = ggplot(df.WMCN.SI, aes(x=burn.trtmt, y = change.WMCN, fill = horizon)) + 
+  geom_boxplot() + 
+  geom_hline(yintercept = 0)+
+  theme_bw() + 
+  labs(x = 'Comparison between samples 24 h and 5 wk post-burn',
+       y = 'Change in predicted wt. mean gene copy number')
+
+test <- aov(change.WMCN ~ burn.trtmt*horizon, data = df.WMCN.SI)
+summary(test)
+TukeyHSD(test)
+
+# Compare copy number of positive/negative responders: ----
+df.full.OTU <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+RDP <- read.csv('../../data/All-OTUs-CopyNum.csv')
+
+df.fast <- subset(df.full.OTU, experiment == 'fast growth' &
+                        Estimate > (mean(Estimate)-1*sd(Estimate))) %>%
+  mutate(fast.est = Estimate)%>%
+  dplyr::group_by(OTU) %>%
+  dplyr::mutate(max.Estimate = max(Estimate)) %>%
+  subset(Estimate == max.Estimate) %>%
+  subset(select = c(OTU, Estimate, SE, t, p, p_fdr,Comparison, experiment,
+                    horizon, Domain, Phylum, Class, Order, Family, Genus, 
+                    Species, DNA.type, fast.est)) %>%
+  unique()
+
+ps.norm.SI <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'SI', ps.norm.full)
+ps.norm.SI <- prune_taxa(taxa_sums(ps.norm.SI)>0, ps.norm.SI)
+
+df.not.responders <- data.frame(taxa_names(ps.norm.SI))
+
+df.not.responders <- subset(df.not.responders, !(taxa_names.ps.norm.SI. %in% df.responders$OTU))
+
+df.not.responders$Responders = 'no'
+df.responders <- subset(df.fast, select = c(OTU)) %>%
+  mutate(Responders = 'yes')
+colnames(df.not.responders)[1] = 'OTU'
+
+df.responders <- rbind(df.responders, df.not.responders) %>%
+  merge(RDP)
+
+p = ggplot(df.responders, aes(x=Responders, y = CopyNum)) + 
+  geom_boxplot() + 
+  theme_bw()
+
+df.SI.responders <- df.full.OTU %>%
+  subset(experiment == 'fast growth') %>%
+  merge(RDP)
+
+dim(df.SI.responders)
+
+df.SI.positive = subset(df.SI.responders, Estimate > 0 ) %>%
+  group_by(OTU) %>%
+  mutate(Estimate = max(Estimate)) %>%
+  mutate(Response = 'positive') %>%
+  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
+                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
+  unique()
+
+df.SI.negative = subset(df.SI.responders, Estimate < 0 ) %>%
+  group_by(OTU) %>%
+  mutate(Estimate = min(Estimate)) %>%
+  mutate(Response = 'negative') %>%
+  subset(select = c(OTU, Estimate, Comparison, horizon, Domain, Phylum, Class, Order, 
+                    Family, Genus, Species, GenusRDP, CopyNum, Response)) %>%
+  unique()
+
+df.SI.responders <- rbind(df.SI.positive, df.SI.negative)
+
+p = ggplot(df.SI.responders, aes(x=Estimate, y = Class, color = Phylum)) + 
+  geom_point() + 
+  theme_bw() + 
+  facet_wrap(~Comparison) +
+  geom_vline(xintercept = 0)
+
+df.SI.dry.responders <- subset(df.SI.responders, Comparison == 'pb.dry.v.SI.dry') %>%
+  subset(!(OTU %in% subset(df.SI.responders, Comparison %in% c('pb.wet.v.SI.wet', 'pb.control.v.SI.control')))) %>%
+  subset(select = c(OTU, CopyNum, Response, horizon,Estimate)) %>%
+  unique()
+
+p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Response, y = CopyNum, fill = horizon)) + 
+  geom_boxplot() + 
+  theme_bw() + 
+  facet_wrap(~horizon)
+
+test = aov(CopyNum ~ Response+horizon, data = df.SI.dry.responders)
+summary(test)
+TukeyHSD(test)
+
+p = ggplot(subset(df.SI.dry.responders, is.na(CopyNum) == FALSE), aes(x=Estimate, y = CopyNum)) + 
+  geom_point()+
+  facet_grid(Response~horizon) + 
+  stat_smooth(method=lm,se = FALSE,color='black') +
+  theme_bw() 
 ```
-
-# Scatterplot matrices to explore "severity"
-```{r}
-colnames(df.meta)
-
-my_colors <- c('red','orange','black')
-
-df1 <- df.meta %>%
-  subset(DNA.type =='gDNA' & incub.trtmt == 'pb') %>%
-  mutate(Frac.O.loss = (PRE.O.hor.thickness.cm - POST.O.hor.thickness.cm)/PRE.O.hor.thickness.cm) %>%
-  subset(select = c(burn.trtmt, 
-                    PRE.O.hor.thickness.cm,
-                    avg.sand,
-                    Thermo.mid.max,
-                    Thermo.low.max, 
-                    change.pH, 
-                    change.C.N.ratio,
-                    Mid.degree.C.hours,
-                    Low.degree.C.hours,
-                    Frac.core.dry.mass.loss,
-                    Frac.core.wet.mass.loss,
-                    hrzn.degree.hrs,
-                    Frac.O.loss))
-
-pairs.panels(df1[,c(2:3,8:10)], 
-      method = 'pearson',
-      hist.col = 'blue',
-      density = TRUE,
-      ellipses = TRUE,
-      col = my_colors[df1$burn.trtmt],
-      pch=19)
-
-pairs.panels(df1[,c(10,11,8,9)], 
-      method = 'pearson',
-      hist.col = 'blue',
-      density = TRUE,
-      ellipses = TRUE,
-      col = my_colors[df1$burn.trtmt],
-      pch=19)
-
-pairs(df1[,c(2,3,4,6,7,8,12,13)],
-      method = 'pearson',
-      col = my_colors[df1$burn.trtmt],
-      pch=19)
-
-df.meta <- df.meta %>%
-  mutate(Frac.O.loss = (PRE.O.hor.thickness.cm - POST.O.hor.thickness.cm)/PRE.O.hor.thickness.cm)
-
-p3 = ggplot(df.meta, aes(x=hrzn.degree.hrs,y=Frac.O.loss, color=burn.trtmt)) +
-  theme_bw()+
-  geom_point(size=3) + 
-  stat_smooth(method=lm,color='black') +
-  facet_grid(~Veg.type)
-
-```
-
-# Comparing autoclave v. not decay model data:
-```{r}
-df.coefs <- subset(df.meta, incub.trtmt != 'SI' &
-                     incub.trtmt != 'pb')
-
-p1 = ggplot(df.coefs, aes(x=burn.trtmt)) + 
-  geom_boxplot(aes(y=(M1), fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
-  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
-  theme_bw()+
-  labs(x= 'Dominant vegetation',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Fractional size of fast C pool \n(M1)',
-       fill = 'Burn treatment',
-       color = 'Burn treatment') + 
-  facet_wrap(~Veg.type) +
-  theme(axis.text.y = element_text(size = 16),
-        legend.title = element_text(size=16),
-        axis.text.x = element_text(size = 16),
-        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=16),
-        legend.text = element_text(size=16),
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-p1
-
-df.rsquared.5weeks <- read.csv('../data/2-pool-decay-model-output-5-weeks.csv')
-df.5weeks <- subset(df.rsquared.5weeks, t == 3)
-
-df.5weeks$incub.trtmt <- factor(df.5weeks$incub.trtmt, levels = c('SI','LIwA','LIn'))
-df.5weeks$burn.trtmt <- factor(df.5weeks$burn.trtmt, levels = c('control','wet','dry'))
-
-p1 = ggplot(df.5weeks, aes(x=burn.trtmt)) + 
-  geom_boxplot(aes(y=(M1), fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
-  #geom_boxplot(aes(y=log(M2), fill=burn.trtmt))+
-  theme_bw()+
-  labs(y = 'Fractional size of fast C pool \n(M1)',
-       fill = 'Burn treatment',
-       color = 'Burn treatment') + 
-  theme(axis.text.y = element_text(size = 16),
-        legend.title = element_text(size=16),
-        axis.text.x = element_text(size = 16),
-        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=16),
-        legend.text = element_text(size=16),
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-p1
-
-# Look at fractional C remaining at end of incubation:
-df.fracC <- read.csv("../data/fractional-c-remaining.csv", row.names = 1)
-
-df.veg <- subset(df.meta, select = c(site, Veg.type)) %>%
-  unique()
-
-df.fracC <- subset(df.fracC, DayFactor == 34) %>%
-  merge(df.veg, all = TRUE)
-
-df.fracC$incub.trtmt <- factor(df.fracC$incub.trtmt, levels = c('SI','LIwA','LIn'))
-df.fracC$burn.trtmt <- factor(df.fracC$burn.trtmt, levels = c('control','wet','dry'))
-
-p = ggplot(df.fracC, aes(x = burn.trtmt)) + 
-    geom_boxplot(aes(y=fractional.C.remaining, fill=incub.trtmt, color=incub.trtmt), alpha = 0.5, varwidth = FALSE)+
-  theme_bw()+
-  facet_wrap(~Veg.type)+
-  labs(fill = 'Burn treatment',
-       color = 'Burn treatment') + 
-  theme(axis.text.y = element_text(size = 16),
-        legend.title = element_text(size=16),
-        axis.text.x = element_text(size = 16),
-        axis.title.x = element_text(size = 16, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 16, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=16),
-        legend.text = element_text(size=16),
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-```
-
-# ORDINATIONS - Comparing to unburned
-```{r}
-MyNMDS.pb.gDNA <- ordinate(ps.norm.pb.gDNA, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-MyNMDS.pb.cDNA <- ordinate(ps.norm.pb.cDNA, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-MyNMDS.SI <- ordinate(ps.norm.SI, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-
-MyNMDS.LI <- ordinate(ps.norm.LI, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-MyNMDS.LI
-
-ps.norm.LI.control <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('control'),ps.norm.LI)
-ps.norm.LI.control<- prune_taxa(taxa_sums(ps.norm.LI.control)>0, ps.norm.LI.control)
-
-ps.norm.LI.wet <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('wet'),ps.norm.LI)
-ps.norm.LI.wet<- prune_taxa(taxa_sums(ps.norm.LI.wet)>0, ps.norm.LI.wet)
-
-ps.norm.LI.dry <- prune_samples(sample_data(ps.norm.LI)$burn.trtmt %in% c('dry'),ps.norm.LI)
-ps.norm.LI.dry<- prune_taxa(taxa_sums(ps.norm.LI.dry)>0, ps.norm.LI.dry)
-
-MyNMDS.LI.control <- ordinate(ps.norm.LI.control, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-MyNMDS.LI.wet <- ordinate(ps.norm.LI.wet, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-MyNMDS.LI.dry <- ordinate(ps.norm.LI.dry, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-
-MyNMDS.LI.control
-MyNMDS.LI.wet
-MyNMDS.LI.dry
-
-p.LI.control = plot_ordination(ps.norm.LI.control, MyNMDS.LI.control,
-                               axes=c(1,3),shape = "incub.trtmt", color = 'horizon') +
-  geom_line(aes(group = core.id.hor)) +
-  theme_bw() +
-  geom_point(size=3)
-
-p.LI.wet = plot_ordination(ps.norm.LI.wet, MyNMDS.LI.wet, 
-                           axes = c(1,3),shape = "incub.trtmt", color = 'horizon') +  
-  geom_line(aes(group = core.id.hor)) +
-
-  theme_bw() +
-  geom_point(size=3)
-
-p.LI.dry = plot_ordination(ps.norm.LI.dry, MyNMDS.LI.dry, 
-                           axes=c(1,3),shape = "incub.trtmt", color = 'horizon') +
-    geom_line(aes(group = core.id.hor)) +
-  theme_bw() +
-  geom_point(size=3)
-
-cowplot::plot_grid(p.LI.control,p.LI.wet,p.LI.dry, ncol=3, labels = c('Control','Wet','Dry'))
-
-p.LI.axis1.2 = plot_ordination(ps.norm.LI, MyNMDS.LI, 
-                           axes=c(1,2),shape = "horizon", color = 'burn.trtmt') +
-    geom_line(aes(group = core.id.hor)) +
-  theme_bw() +
-  geom_point(size=3)
-p.LI.axis1.3 = plot_ordination(ps.norm.LI, MyNMDS.LI, 
-                           axes=c(1,3),shape = "horizon", color = 'burn.trtmt') +
-    geom_line(aes(group = core.id.hor)) +
-  theme_bw() +
-  geom_point(size=3)
-cowplot::plot_grid(p.LI.axis1.2,p.LI.axis1.3, ncol=2)
-
-p1 = plot_ordination(ps.norm.pb.gDNA, MyNMDS.pb.gDNA, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-p2 = plot_ordination(ps.norm.pb.gDNA, MyNMDS.pb.gDNA, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-p3 = plot_ordination(ps.norm.SI, MyNMDS.SI, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-p4 = plot_ordination(ps.norm.SI, MyNMDS.SI, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-p5 = plot_ordination(ps.norm.LIwA, MyNMDS.LIwA, axes = c(1,2),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-p6 = plot_ordination(ps.norm.LIwA, MyNMDS.LIwA, axes=c(1,3),shape = "burn.trtmt", color = 'burn.trtmt') +
-  facet_wrap(~incub.trtmt) + theme_bw() +
-  geom_point(size=3)
-
-# using cowplot to combine multiple figures.
-plot_grid(p1,p2,p3,p4,p5,p6,ncol=2)
-
-# Full ordination
-MyNMDS.full <- ordinate(ps.norm.gDNA, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)
-
-ps.norm.pb <- prune_samples(sample_data(ps.norm.full)$incub.trtmt == 'pb', ps.norm.full)
-ps.norm.pb <- prune_taxa(taxa_sums(ps.norm.pb)>0, ps.norm.pb)
-MyNMDS.pb <- ordinate(ps.norm.pb, method = 'NMDS', k=3, ddistance="wunifrac", weighted=TRUE)
-
-sample_data(ps.norm.pb)$horizon = factor(sample_data(ps.norm.pb)$horizon, levels = c('O','A'))
-
-# Ordination plot with horizons and deg.hrs
-p1 = plot_ordination(ps.norm.pb, MyNMDS.pb, axes = c(1,2), 
-                      color = "burn.trtmt",
-                      shape = 'burn.trtmt') + 
-  facet_grid(horizon~DNA.type, labeller = labeller(horizon = HorizonLabels,
-                                                   DNA.type = DNALabels,
-                                                   incub.trtmt = IncubLabels))+
-  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
-  geom_point(size=3, alpha=0.8) +
-  labs(color = 'Burn treatment',
-       #color = expression("Degree ("*degree*C*") hours"), 
-       shape = 'Burn treatment') +
-  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
-  scale_color_manual(values = c('black','orange','red'),
-                     labels = c('control', 'wet soil burn','dry soil burn'),
-                     breaks = c('control','wet','dry'))+
-  scale_shape_manual(values = c('circle','square','triangle'),
-                     labels = c('control', 'wet soil burn','dry soil burn'),
-                     breaks = c('control','wet','dry')) +
-  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
-  #scale_shape_manual(values = c('circle','triangle'),
-   #                  labels = c('O horizon','Mineral'),
-    #                 breaks = c('O','A')) + 
-  theme(legend.text = element_text(face = 'italic',size = 16),
-        axis.title = element_text(size=16),
-        axis.text = element_text(size=16),
-        legend.title = element_text(size=16)) + 
-  theme_bw()
-
-p1
-
-p2 = plot_ordination(ps.norm.gDNA, MyNMDS.full, axes = c(2,3), 
-                      color = "pH",
-                      shape = 'burn.trtmt') + 
-  facet_grid(horizon~incub.trtmt, labeller = labeller(horizon = HorizonLabels))+
-  #facet_grid(~horizon, labeller = labeller(horizon = HorizonLabels))+
-  geom_point(size=3, alpha=0.8) +
-  labs(color = 'post-burn pH',
-       #color = expression("Degree ("*degree*C*") hours"), 
-       shape = 'Burn treatment',
-       title = "Ch 4, p2: NMDS ordination on weighted unifrac dissimilarities \n All DNA samples; all timepoints") +
-  #scale_color_gradientn(colours = c('gold2','red','red4','black')) +
-  #scale_shape_manual(values = c('circle','square','triangle'),
-   #                  labels = c('control', 'wet soil burn','dry soil burn'),
-    #                 breaks = c('control','wet','dry')) +
-  #scale_shape_discrete(labels = c('Picea' = 'Picea spp.', 'Populus_tremuloides' = 'Populus tremuloides','Pinus_banksiana' = 'Pinus banksiana')) +
-  #scale_shape_manual(values = c('circle','triangle'),
-   #                  labels = c('O horizon','Mineral'),
-    #                 breaks = c('O','A')) + 
-  theme(legend.text = element_text(face = 'italic',size = 16),
-        axis.title = element_text(size=16),
-        axis.text = element_text(size=16),
-        legend.title = element_text(size=16)) + 
-  theme_bw()
-
-p2
-```
-
-# ORDINATIONS - Comparing SI to LIwA - inoculated burned soils look more like uninoculated burned 5-week samples
-```{r}
-ps.norm.SI.v.LIwA <- prune_samples(sample_data(ps.norm.full)$incub.trtmt %in% c('SI','LIwA'), ps.norm.full)
-
-ps.subset <- prune_samples(sample_data(ps.norm.SI.v.LIwA)$horizon == 'O' &
-                             sample_data(ps.norm.SI.v.LIwA)$burn.trtmt != 'wet',ps.norm.SI.v.LIwA)
-
-MyNMDS.inoculation <- ordinate(ps.subset, method = 'NMDS', k=3, ddistance="unifrac", weighted=TRUE)
-
-IncubLabels = c('5 weeks post-burn', 'Inoculated soils \n6 months post-burn')
-names(IncubLabels) = c('SI', 'LIwA')
-
-p.inoc = plot_ordination(ps.subset, MyNMDS.inoculation,
-                               axes=c(1,2),shape = "burn.trtmt", color='burn.trtmt') +
-  geom_point(size=2)+
-  geom_line(aes(group = site), color = 'grey60') +
-  facet_wrap(~incub.trtmt, labeller = labeller(incub.trtmt=IncubLabels))+
-  scale_color_manual(values = c('black','tan3'),
-                     limits = c('control','dry'),
-                     labels = c('Unburned \ncontrol','Dry soil')) +
-  scale_shape_manual(values = c('circle','triangle'),
-                     limits = c('control','dry'),
-                     labels = c('Unburned \ncontrol','Dry soil')) +
-  labs(shape = 'Burn treatment',
-       color = 'Burn treatment')+
-  theme_bw() +
-  geom_point(size=3)
-
-p.inoc
-```
-
-# Phylogenetic tree:
-```{r, message = FALSE}
-ps.traits <- phyloseq::prune_taxa(df.trait$OTU, ps.raw.full)
-
-AbunTaxa = taxa_names(filter_taxa(ps.norm.gDNA, function(x) mean(x) > 0.001, TRUE))
-
-length(AbunTaxa)
-ps.prune = prune_taxa(AbunTaxa, ps.raw.full)
-ps.prune
-
-ps.prune <- ps.raw.full %>%
-  subset_samples(burn.trtmt %in% c('dry'))
-
-ps.prune <- prune_taxa(AbunTaxa, ps.prune)
-
-p = ggtree(ps.prune, aes(color=Phylum), 
-           branch.length = 'none',
-           layout = 'circular') + 
-  geom_treescale() + 
-  geom_tiplab2(size=2, aes(angle=angle))
-
-tree <- read.tree(file = '../../CombinedFireSim1519/tree/merged-exported-tree/tree.nwk')
-tree <- phy_tree(ps.prune)
-
-plot(tree, type = 'cladogram')
-
-# using cowplot to combine multiple figures.
-cowplot::plot_grid(p,p1, ncol=2, labels = c('A','B'))
-
-```
-
-# Number of responding OTUs for each experiment:
-```{r}
-df.full.OTU <- read.csv('../data/sequence-data/LibCombined/corncob-output/all-responders.csv')
-head(df.full.OTU)
-
-# Filter responders:
-df.full <- df.full.OTU %>%
-  subset(abs(Estimate) > 1) # removes 1500 non-unique OTUs
-dim(df.full)
-
-df.PB.pos.rspd <- subset(df.full, experiment == 'survival' & Estimate > 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU,horizon) %>%
-  mutate(max.Estimate = max(Estimate)) %>%
-  subset(max.Estimate == Estimate) %>%  
-  mutate(Response = 'positive') %>%
-  unique()
-
-df.PB.neg.rspd <- subset(df.full, experiment == 'survival' & Estimate < 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU, horizon) %>%
-  mutate(min.Estimate = min(Estimate)) %>%
-  subset(min.Estimate == Estimate) %>%
-  mutate(Response = 'negative') %>%
-  unique()
-
-summary(df.PB.pos.rspd$Estimate)
-length(unique(df.PB.pos.rspd$OTU))
-length(unique(df.PB.neg.rspd$OTU))
-
-df.SI.cntl.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
-  subset(Comparison == 'pb.control.v.SI.control') %>%
-  group_by(OTU, horizon) %>%
-  mutate(max.Estimate = max(Estimate)) %>%
-  subset(max.Estimate == Estimate) %>%
-  unique()
-df.SI.cntl.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
-  subset(Comparison == 'pb.control.v.SI.control') %>%
-  group_by(OTU, horizon) %>%
-  mutate(min.Estimate = min(Estimate)) %>%
-  subset(min.Estimate == Estimate) %>%
-  unique()
-
-df.SI.pos.rspd <- subset(df.full, experiment == 'fast growth' & Estimate > 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU, horizon) %>%
-  mutate(max.Estimate = max(Estimate)) %>%
-  subset(max.Estimate == Estimate) %>%
-  mutate(Response = 'positive') %>%
-  unique() %>% 
-  subset(!(OTU %in% df.SI.cntl.pos.rspd$OTU))
-length(unique(df.SI.pos.rspd$OTU))
-
-df.SI.neg.rspd <- subset(df.full, experiment == 'fast growth' & Estimate < 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU, horizon) %>%
-  mutate(min.Estimate = min(Estimate)) %>%
-  subset(min.Estimate == Estimate) %>%
-  unique() %>%
-  mutate(Response = 'negative') %>%
-  subset(!(OTU %in% df.SI.cntl.neg.rspd$OTU))
-
-length(unique(df.SI.neg.rspd$OTU))
-
-# LIwA:
-df.LIwA <- subset(df.full, experiment == 'affinity')
-
-df.LIwA.pos.rspd <- subset(df.full, experiment == 'affinity' & Estimate > 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU, horizon) %>%
-  mutate(max.Estimate = max(Estimate)) %>%
-  subset(max.Estimate == Estimate) %>%
-  mutate(Response = 'positive') %>%
-  unique() 
-length(unique(df.LIwA.pos.rspd$OTU))
-
-df.LIwA.neg.rspd <- subset(df.full, experiment == 'affinity' & Estimate < 0) %>%
-  subset(Temp.cutoff %in% c('Low thermo greater than 50 C',
-                            'Mid thermo greater than 50 C')) %>%
-  group_by(OTU,horizon) %>%
-  mutate(min.Estimate = min(Estimate)) %>%
-  subset(min.Estimate == Estimate) %>%
-  mutate(Response = 'negative') %>%
-  unique() 
-length(unique(df.LIwA.neg.rspd$OTU))
-
-df.responders <- rbind(df.PB.pos.rspd, df.PB.neg.rspd,
-                       df.SI.pos.rspd, df.SI.neg.rspd,
-                       df.LIwA.pos.rspd, df.LIwA.neg.rspd)
-head(df.responders)
-
-p = ggplot(subset(df.responders, Phylum == 'Firmicutes'), aes(x=Estimate, y = Genus, color = experiment)) + 
-  geom_point(size=2) + 
-  theme_bw() + 
-  facet_grid(horizon~experiment) + 
-  geom_vline(xintercept = 0)
-
-# Are fire survivors likely to be fast growing?
-length(df.PB.pos.rspd$OTU)
-dim(subset(df.PB.pos.rspd, OTU %in% df.SI.pos.rspd$OTU))
-# --> No not really. Of 19 fire survivors, only 2 are fast growing.
-
-# Are fast growing taxa also survivors?
-length(unique(df.SI.pos.rspd$OTU))
-dim(subset(df.SI.pos.rspd, OTU %in% df.PB.pos.rspd$OTU)) 
-# --> No, of 98 OTUs identified as fast growing, only 2 were also identified as fire surviving.
-
-# Do fast growing taxa show post-fire affinity?
-length(unique(df.SI.pos.rspd$OTU))
-length(unique(subset(df.SI.pos.rspd, OTU %in% df.LIwA.pos.rspd$OTU))$OTU)
-length(unique(subset(df.SI.pos.rspd, OTU %in% df.LIwA.neg.rspd$OTU))$OTU)
-# --> 8 of 98 are positive+positive, 
-# --> 5 of 98 are positive+negative
-
-# Are positive affinity taxa also fire susceptible?
-length(df.LIwA.pos.rspd$OTU)
-dim(subset(df.LIwA.pos.rspd, OTU %in% df.PB.neg.rspd$OTU))
-# --> Nope. Only 1 of the positive affinity taxa was identified as fire susceptible.
-
-# Are positive affinity taxa also fast growers?
-length(df.LIwA.pos.rspd$OTU)
-dim(subset(df.LIwA.pos.rspd, OTU %in% df.SI.pos.rspd$OTU))
-# --> Not really, 7 of 53 positive affinity taxa identified as fast growing.
-
-# Are negative affinity taxa the same as slow growing taxa?
-length(df.LIwA.neg.rspd$OTU) 
-dim(subset(df.LIwA.neg.rspd, OTU %in% df.SI.neg.rspd$OTU))
-# Not really, 12 of 199 (10%) of negative affinity taxa were identified as slow growing.
-
-# DO fire survivors appear to have an affinity for post-fire environment?
-length(df.PB.pos.rspd$OTU)
-dim(subset(df.PB.pos.rspd, OTU %in% df.LIwA.pos.rspd$OTU))
-# --> Nope. 1 of 19
-
-# What about an anti-affinity?
-dim(subset(df.PB.pos.rspd, OTU %in% df.LIwA.neg.rspd$OTU))
-# --> Nop3. 2 of 19.
-```
-
-# Attempt at 3D plot
-```{r}
-# GRoup by Order
-ps.norm.gDNA <- ps.norm.gDNA %>%
-  tax_glom('Phylum')
-
-df.norm.gDNA.Phylum <- psmelt(ps.norm.gDNA)
-
-df.Phylum.pb <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'pb') %>%
-  group_by(Phylum, core.id.hor) %>%
-  mutate(mean.Abun.pb = mean(Abundance)) %>%
-  subset(select = c(Domain, Phylum, mean.Abun.pb, core.id.hor, burn.trtmt))
-
-df.Phylum.SI <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'SI') %>%
-  group_by(Phylum, core.id.hor) %>%
-  mutate(mean.Abun.SI = mean(Abundance)) %>%
-  subset(select = c(Domain, Phylum, mean.Abun.SI, core.id.hor, burn.trtmt))
-
-df.Phylum.LIn <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'LIn') %>%
-  group_by(Phylum, core.id.hor) %>%
-  mutate(mean.Abun.LIn = mean(Abundance)) %>%
-  subset(select = c(Domain, Phylum, mean.Abun.LIn, core.id.hor, burn.trtmt))
-
-df.Phylum.LIwA <- subset(df.norm.gDNA.Phylum, incub.trtmt == 'LIwA') %>%
-  group_by(Phylum, core.id.hor) %>%
-  mutate(mean.Abun.LIwA = mean(Abundance)) %>%
-  subset(select = c(Domain, Phylum, mean.Abun.LIwA, core.id.hor, burn.trtmt))
-
-df <- merge(df.Phylum.pb, df.Phylum.SI) %>%
-  merge(df.Phylum.LIn) %>%
-  merge(df.Phylum.LIwA) %>%
-  subset(mean.Abun.pb > 0.1 |
-           mean.Abun.SI > 0.1 |
-           mean.Abun.LIn > 0.1)
-
-# Plot
-p = ggplot(df, aes(x=mean.Abun.pb, 
-                   y=mean.Abun.SI, 
-                   color=Phylum, 
-                   shape = burn.trtmt,
-                   size = mean.Abun.LIn))+
-  geom_point() + 
-  #facet_wrap(~Phylum, scales = 'fixed') + 
-  ylim(0,1) + 
-  xlim(0,1)
-p
-
-cols <- c('red','orange','yellow','green','blue','purple','pink','black','grey10','grey20', 'forestgreen')
-
-df$color <- mycolors[as.numeric(df$Phylum)]
-
-# 3D plot with scatterplot3d - problems with coloring by variable
-with(df,
-     scatterplot3d(x = mean.Abun.pb, 
-                  y = mean.Abun.SI,
-                  z = mean.Abun.LIn))
-
-# 3D plot with rgl
-plot3d(
-  x=df$mean.Abun.pb, y=df$mean.Abun.SI, z=df$mean.Abun.LIn,
-  type = 's',
-  raidus = 0.1)
-```

### 2023-03-16 README.rmd

@@
 rrndb-SI.R: Assigns mean predicted 16S copy numbers to OTUs based on taxonomy
+
+Combined_Lab_Field_OTU_table.csv: R dataframe of OTUs in the combined lab experiment/field datasets
+
+Combined_Lab_Field_sample_data.csv: R dataframe of sample names and metadata for the combined lab experiment/field datasets
+
+Combined_Lab_Field_tax_table.csv: R dataframe of taxonomy table for combined lab experiment/field datasets
+
+lab_OTU_table.csv: R dataframe of OTUs in the lab experiment datasets
+
+lab_sample_data.csv: R dataframe of sample names and metadata for the lab experiment datasets
+
+lab_taxonomy_table.csv: R dataframe of taxonomy for lab experiment datasets

### 2023-05-26 Merged_paper_figures_Revision_Github.R
Remove treed wetland sites from field data

@@ -26,8 +26,19 @@ ps.norm = transform_sample_counts(ps,function(x) x/sum(x))
 sample_data(ps.norm)$Study = sample_data(ps.norm)$Years_Since_Fire
 sample_data(ps.norm)$Study[is.na(sample_data(ps.norm)$Study)]="Lab"
 
+# Drop non-autoclaved lab samples, cDNA, and treed wetland field samples for ordination
+sample_data(ps.norm)$incub.trtmt = ifelse(is.na(sample_data(ps.norm)$incub.trtmt), "field",sample_data(ps.norm)$incub.trtmt)
+sample_data(ps.norm)$DNA.type[is.na(sample_data(ps.norm)$DNA.type)]="gDNA"
+sample_data(ps.norm)$Veg.type = ifelse(is.na(sample_data(ps.norm)$Veg.type), paste(sample_data(ps.norm)$Veg_Comm),sample_data(ps.norm)$Veg.type)
+
+ps.norm = subset_samples(ps.norm,sample_data(ps.norm)$incub.trtmt %in% c("field","SI","LIwA","pb"))
+ps.norm = subset_samples(ps.norm,sample_data(ps.norm)$DNA.type == "gDNA")
+ps.norm = subset_samples(ps.norm,sample_data(ps.norm)$Veg.type != "Treed Wetland")
+ps.norm
+
 # Ordinate plots
 ord.nmds = ordinate(ps.norm,method = "NMDS",distance="bray",k=3, trymax=200)
+ord.nmds
 
 # Making figure for paper
 # Get ordination data
@@ -54,34 +65,25 @@ full.plot$horizon[full.plot$horizon=="M"]="A"
 full.plot$horizon[full.plot$horizon=="A"]="Mineral"
 full.plot$horizon[full.plot$horizon=="O"]="Organic"
 
-# Make veg comm variable same for both sets
-full.plot$Veg.type
-full.plot$Veg.type = ifelse(is.na(full.plot$Veg.type), paste(full.plot$Veg_Comm),full.plot$Veg.type)
-
 # Make new year-agnostic study variable
 full.plot$StudyShape = full.plot$Study
 full.plot$StudyShape[full.plot$StudyShape %in% c("1","5")]="Field"
 
[…]

### 2023-05-26 Manuscript-figures.Rmd
Editing figure numbers to match manuscript

@@
 
-# Rel abundance adjusted by copy num, Figure 5 -----
+# Total trait abun by BC dissimilarity, Figure 5 -----
 See "Merged_paper_figures_Revision_GitHub.R" script
 
-# Total trait abun by BC dissimilarity, Figure 6 -----
-See "Merged_paper_figures_Revision_GitHub.R" script
-
-# Supplementary
+#### Extended data figures
 ```{r}
-# Carbon and nitrogen loss, Figure S2 -----
+# Carbon and nitrogen loss, Extended data Figure 1 -----
 pChange_C <- ggplot(subset(df.meta, incub.trtmt == 'SI')) + 
@@
 TukeyHSD(test)
-
-# C remaining as fraction of total, Figure S3, S4 -----
-#   See incubations_microbial_respiration.R
-# Full ordination, Fig. S6 ----
+```
+
+# C remaining as fraction of total, Extended data Figure S2, S3 -----
+See incubations_microbial_respiration.R
+
+# Decay model parameters for post-fire environment affinity incubation, Extended Data Figure 4 -----
+
+XXXX
+
+```{r}
+# Full ordination, Extended Data Figure 5 ----
 ps.full.dataset <-readRDS('../../../CombinedFireSim1519/ps.1519FireSim.merged')
@@
 p1
-
-# BC dissimilarity and pH change, Figure S7-----
+```
+
+# Rel abundance adjusted by weighted mean predicted 16S copy num, Extended Data Figure 6 -----
+See "Merged_paper_figures_Revision_GitHub.R" script
+
+# Respiration rate for lab-incubated soils, Extended data Figure 7-----
+See "incubations_microbial_respiration.R" script
+
+```{r}
+# Traits as fraction of total reads in lab data, Extended data Figure 8-----
+df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
+
+ps.responders <- prune_taxa(taxa_names(ps.norm.full) %in% df$OTU, ps.norm.full)
+
+df.melt <- psmelt(ps.responders)
+
+responders <- df.melt %>% group_by(Sample) %>% summarize(Abundance) 
+max(responders$Abundance)
+mean(responders$Abundance)
+
+dry <- subset(df.melt, burn.trtmt == 'dry') %>% subset(select = c(Sample, horizon, burn.trtmt, Abundance, incub.trtmt, Thermo.mid.max)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
+
+summary(dry)
+
+# Total gDNA reads in lab experiments: 39115
+# Total reads in lab experiments: 43450
+# Number responders = 117
+# max abundance in lab data = 60%
+# mean abundance, dry burns = 0.15% +/- 14%
+
+df.frac.of.total <- df.melt %>% subset(select = c(Sample, horizon, burn.trtmt, Veg.type, Abundance, DNA.type, incub.trtmt, Thermo.mid.max, site)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
+
+p_FractionTotal <- ggplot(subset(df.frac.of.total, DNA.type == 'cDNA'), aes(x=site, y=total.Abun, fill=burn.trtmt)) +
+  geom_bar(stat='identity',  position='dodge') + 
+  facet_wrap(~horizon+incub.trtmt, labeller = labeller(horizon = HorizonLabels)) + 
+  theme_bw()+
+  labs(x= 'Sampling site ID',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Fraction of total reads',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+df.frac.of.total$burn.trtmt <- factor(df.frac.of.total$burn.trtmt, levels = c('control','wet','dry'))
+
+p_FractionTotal <- ggplot(subset(df.frac.of.total,incub.trtmt!='LIn'), aes(x=horizon, y=total.Abun, fill=burn.trtmt)) +
+  geom_boxplot()+
+  facet_wrap(~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels, DNA.type = DNALabels)) + 
+  theme_bw()+
+  labs(x= 'Soil horizon',
+     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
+       y = 'Fraction of total reads',
+       fill = 'Burn treatment') + 
+  scale_fill_manual(values = c('grey50','orange','red'),
+                     limits = c('control','wet','dry'),
+                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
+    scale_x_discrete(limits = c('O','A'),
+                     labels = c('Organic','Mineral')) +
+  theme(axis.text.y = element_text(size = 14),
+        legend.title = element_text(size=14),
+        axis.text.x = element_text(size = 14),
+        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
+        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
+        strip.text = element_text(size=14),
+        legend.text = element_text(size=14),
+        legend.position = '',
+       # legend.background = element_rect(fill = "darkgray"),
+        legend.box = "vertical")
+
+```
+
+# Extended Data Figure 9, Respiration rates with/without inocubation
+See "incubations_microbial_respiration.R" script
+
+#### Supplementary Figure 1 
+```{r}
+# BC dissimilarity and pH change, Supplementary Figure 1 -----
 df.distances <- read.csv('../../data/bray-curtis-dissimilarites.csv')
@@
     ylim(0,1)
-
-# Respiration rate figures, S8, S9, S10-----
-#   See "incubations_microbial_respiration.R" script
-
-# Traits as fraction of total reads in lab data, Figure S11-----
-df <- read.csv('../../data/sequence-data/LibCombined/corncob-output/Manuscript/Trait-responder-OTUs.csv')
-
-ps.responders <- prune_taxa(taxa_names(ps.norm.full) %in% df$OTU, ps.norm.full)
-
-df.melt <- psmelt(ps.responders)
-
-responders <- df.melt %>% group_by(Sample) %>% summarize(Abundance) 
-max(responders$Abundance)
-mean(responders$Abundance)
-
-dry <- subset(df.melt, burn.trtmt == 'dry') %>% subset(select = c(Sample, horizon, burn.trtmt, Abundance, incub.trtmt, Thermo.mid.max)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
-
-summary(dry)
-
-# Total gDNA reads in lab experiments: 39115
-# Total reads in lab experiments: 43450
-# Number responders = 117
-# max abundance in lab data = 60%
-# mean abundance, dry burns = 0.15% +/- 14%
-
-df.frac.of.total <- df.melt %>% subset(select = c(Sample, horizon, burn.trtmt, Veg.type, Abundance, DNA.type, incub.trtmt, Thermo.mid.max, site)) %>% group_by(Sample) %>% mutate(total.Abun = sum(Abundance))
-
-p_FractionTotal <- ggplot(subset(df.frac.of.total, DNA.type == 'cDNA'), aes(x=site, y=total.Abun, fill=burn.trtmt)) +
-  geom_bar(stat='identity',  position='dodge') + 
-  facet_wrap(~horizon+incub.trtmt, labeller = labeller(horizon = HorizonLabels)) + 
-  theme_bw()+
-  labs(x= 'Sampling site ID',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Fraction of total reads',
-       fill = 'Burn treatment') + 
-  scale_fill_manual(values = c('grey50','orange','red'),
-                     limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
-df.frac.of.total$burn.trtmt <- factor(df.frac.of.total$burn.trtmt, levels = c('control','wet','dry'))
-
-p_FractionTotal <- ggplot(subset(df.frac.of.total,incub.trtmt!='LIn'), aes(x=horizon, y=total.Abun, fill=burn.trtmt)) +
-  geom_boxplot()+
-  facet_wrap(~incub.trtmt+DNA.type, labeller = labeller(incub.trtmt = IncubLabels, DNA.type = DNALabels)) + 
-  theme_bw()+
-  labs(x= 'Soil horizon',
-     #  y = 'Decay rate constant for fast C pool \nlog(k1)',
-       y = 'Fraction of total reads',
-       fill = 'Burn treatment') + 
-  scale_fill_manual(values = c('grey50','orange','red'),
-                     limits = c('control','wet','dry'),
-                     labels = c('Unburned\ncontrol','Moist soil\nburn','Dry soil\nburn')) +
-    scale_x_discrete(limits = c('O','A'),
-                     labels = c('Organic','Mineral')) +
-  theme(axis.text.y = element_text(size = 14),
-        legend.title = element_text(size=14),
-        axis.text.x = element_text(size = 14),
-        axis.title.x = element_text(size = 14, margin = margin(t=10, b=10)),
-        axis.title.y = element_text(size = 14, margin = margin(r=10, l=10)),
-        strip.text = element_text(size=14),
-        legend.text = element_text(size=14),
-        legend.position = '',
-       # legend.background = element_rect(fill = "darkgray"),
-        legend.box = "vertical")
-
 ```

### 2023-05-26 README.rmd
Update README.rmd

@@
-Scripts for analyzing data associated with "Experimentally-determined traits shape bacterial community composition one and five years following wildfire"
+Scripts for analyzing data associated with "Experimentally determined traits shape bacterial community composition one and five years following wildfire"
 
